---
title: "Balance Tables"
editor: source
toc-title: "**Balance Tables**"
toc-location: "left"
toc-depth: 4
toc_float: 
  collapsed: false
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
# bibliography: "bib/kq6.bib"
# csl: anesthesiology.csl
# link-citations: false
# nocite: '@*'
---

<!-- ## Updates -->
<!-- ::: {.callout-important collapse="true"} -->
<!-- ### `r lubridate::today()` -->

<!-- | Date               | Modification| -->
<!-- |:------------------------|:-----------------------------------------------| -->
<!-- | 2024-04-07 | Updated expanded versus standard preoperative evaluation. | -->

<!-- ::: -->

```{r preliminaries}
#| include: false
## preliminaries -------------------------------------- (2022-11-16 11:49) @----
library(conflicted)
library(janitor)
library(htmltools)
library(gt, quietly = TRUE)
library(gtsummary)
library(gtExtras)
library(glue)
library(tidyverse)
conflicts_prefer(dplyr::filter)
knitr::opts_chunk$set(echo = FALSE)
source("code/functions_2023-04-26.R")

# grade footnote
high  <- "<span><span class='quality-sign'>⨁⨁⨁⨁</span>"
mod   <- "<span><span class='quality-sign'>⨁⨁⨁◯</span>"
low   <- "<span><span class='quality-sign'>⨁⨁◯◯</span>"
vlow  <- "<span><span class='quality-sign'>⨁◯◯◯</span>"
low_very  <- paste(low, vlow, sep = "<br/>")
# grade_foot <- paste0("Very low: ", vlow, "; Low: ", low, "; Moderate: ", mod, "; High: ", high, ".")
grade_foot <- paste0("[", "Very low: ", vlow, "; Low: ", low, "; Moderate: ", mod, "; High: ", high, ".", "]", "(", "soe_gt.html#grade", ")")

# replace in balance table
replace_text <- "see Appendix"
# replace_text <- "Nothing replaced" # for copying to publication
source("code/table_functions.R")
```

## Expanded Preoperative Evaluation

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for expanded versus standard preoperative evaluation. </font>

```{r exp_preop_balance}
#| label: exp_preop_balance
#| 
kq1_balance_main("exclude") |> 
  text_replace(replace_text, paste0("See Table ", table_n + 1), locations = cells_body()) 

```

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for expanded versus standard preoperative evaluation. </font>

```{r exp_preop_complications}
#| label: exp_preop_complications

kq1_complications()
```

## Neuraxial versus General Anesthesia

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for regional versus general anesthesia. </font>

```{r reg_gen_balance}
kq3_balance_main(exclude = "RD/1000") |> 
  text_replace(replace_text, paste0("See Table ", table_n + 1), locations = cells_body()) |> 
  tab_footnote(md("RCT: randomized clinical trial; GRADE: Grades of Recommendation, Assessment, Development, and Evaluation; RR: risk ratio; SMD: standardized mean difference; MD: mean difference."))
```

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for regional versus general anesthesia. </font>

```{r reg_gen_complications}
kq3_complications()
```

## TIVA versus Inhalation Anesthesia

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for TIVA versus inhaled anesthesia. </font>

```{r tiva_inh_balance}
kq4_balance_main("exclude") |> 
  text_replace(replace_text, paste0("See Table ", table_n + 1), locations = cells_body())
```

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for TIVA versus inhaled anesthesia. </font>

```{r tiva_inha_complications}
kq4_complications()
```

## Delirium Prophylaxis 

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for dexmedetomidine versus placebo or no delirium prophylaxis. </font>

```{r}
kq6_balance_dex_main("include") |> 
  text_replace(replace_text, paste0("see Table ", table_n + 1), locations = cells_body()) 
```

<font size = 4> `r table_ref()` Other complications and strength of evidence (GRADE) for dexmedetomidine versus placebo or no delirium prophylaxis. </font>

```{r dex_plac_preop_complications}
#| label: dex_plac_preop_complications

kq6_dex_complications()
```

<!-- ### Ketamine -->

<!-- <font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for ketamine versus placebo. </font> -->

```{r}
#| eval: false

kq6_ketamine()  |> 
  text_replace(replace_text, paste0("see Table ", table_n + 1), locations = cells_body())
```

<!-- ### Melatonin or Ramelteon -->

<!-- <font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for melatonin or ramelteon versus placebo. </font> -->

```{r mel_ram_main}
#| eval: false

kq6_balance_mel_ram_main() |> 
  text_replace(replace_text, paste0("see Table ", table_n + 1), locations = cells_body())
```

<!-- <font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for melatonin or ramelteon versus placebo. </font> -->

```{r mel_ram_plaaled_preop_complications}
#| eval: false

kq6_balance_mel_ram_complications()
```

<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
<br/>
<br/>








