---
title: "[DRAFT]{.underline} Balance Tables"
editor: source
toc-title: "**Balance Tables**"
toc-location: "left"
toc-depth: 4
toc_float: 
  collapsed: false
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
# bibliography: "bib/kq6.bib"
# csl: jama.csl
# link-citations: false
# nocite: '@*'
---

```{=html}
<style type="text/css">
@font-face {
    font-family: "GRADE-quality";
    src: url();
    src: url('https://gradepro.org/fonts/GRADE-quality.eot');
    src: url('https://gradepro.org/fonts/GRADE-quality.eot?#iefix')
        format('embedded-opentype'),
      url('https://gradepro.org/fonts/GRADE-quality.woff') format('woff'),
      url('https://gradepro.org/fonts/GRADE-quality.ttf') format('truetype'),
      url('https://gradepro.org/fonts/GRADE-quality.svg#GRADE-quality')
        format('svg');
    font-weight: normal;
    font-style: normal;
}

.quality-sign {
      font-family: 'GRADE-quality', Cambria, Helvetica, Arial;
      font-size: 10px;
      vertical-align: text-top;
}
</style>
```
```{r preliminaries}
#| include: false
## preliminaries -------------------------------------- (2022-11-16 11:49) @----
library(conflicted)
library(janitor)
library(htmltools)
library(gt, quietly = TRUE)
library(gtsummary)
library(gtExtras)
library(glue)
library(tidyverse)
conflicts_prefer(dplyr::filter)
knitr::opts_chunk$set(echo = FALSE)
source("code/functions_2023-04-26.R")

# grade footnote
high  <- '<span><span class="quality-sign">⨁⨁⨁⨁</span>'
mod   <- '<span><span class="quality-sign">⨁⨁⨁◯</span>'
low   <- '<span><span class="quality-sign">⨁⨁◯◯</span>'
vlow  <- '<span><span class="quality-sign">⨁◯◯◯</span>'
grade_foot <- paste0("Very low: ", vlow, "; Low: ", low, "; Moderate: ", mod, "; High: ", high, ".")
```

## Expanded Preoperative Evaluation

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for expanded versus standard preoperative evaluation. </font>

```{r exp_preop_balance}
#| warning: false
expanded_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "ExpandedPreop", range = "B4:M21") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_exp), paste0(events_exp, " (", n_exp, ")"), NA),
    event_c = ifelse(!is.na(n_std), paste0(events_std, " (", n_std, ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_exp:n_std, grade_2))

expanded_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Preoperative Evaluation", columns = c(event_e, event_c), level = 2) |>
  tab_spanner(label = "Expanded", columns = c(event_e), level = 1) |>
  tab_spanner(label = "Standard", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  # indent row labels
  tab_style(style = cell_text(indent = px(15)),       locations = cells_body(rows = outcome %in% c("Hip fracture", "Other", "Any"), columns = outcome)) |>
  tab_footnote(md("RCT: randomized clinical trial; NRSI: nonrandomized studies of interventions (includes before-after designs);  [GRADE: Grades of Recommendation, Assessment, Development, and Evaluation](soe_gt.html#grade); RR: risk ratio; MD: mean difference.")) |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("Studies reported 0 and 2 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest"), placement = "right") 
  # tab_footnote(md("Per 100 patients for [higher or highest category or categories compared with lower ones.](kq3.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") 

```

<br/>

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for expanded versus standard preoperative evaluation. </font>

```{r exp_preop_complications}
#| warning: false
expanded_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "ExpandedPreop", range = "B31:M42") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_exp), paste0(events_exp, " (", n_exp, ")"), NA),
    event_c = ifelse(!is.na(n_std), paste0(events_std, " (", n_std, ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_exp:n_std, grade_2))

expanded_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Preoperative Evaluation", columns = c(event_e, event_c), level = 2) |>
  tab_spanner(label = "Expanded", columns = c(event_e), level = 1) |>
  tab_spanner(label = "Standard", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote(md("RCT: randomized clinical trial; [GRADE: Grades of Recommendation, Assessment, Development, and Evaluation](soe_gt.html#grade); RR: risk ratio; MD: mean difference.")) |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Complications unspecified (4); cardiac failiure or arrhythmia (1); acute coronary syndrome, heart failure, tachyarrhythmia, or bradyarrhythmia (1); acute MI, cardiac arrest and ventricular fibrillation, cardiac dysrhythmia, and acute heart failiure combined.", locations = cells_body(columns = c(outcome), rows = outcome == "Cardiac complications")) |>
  tab_footnote("Studies reported 0 and 2 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest"), placement = "right") |> 
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq3.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("Complications reported variously across the 17 trials. ", locations = cells_body(columns = c(rct), rows = outcome == "Complications"), placement = "right") |> 
  tab_footnote("One study no events; the other two. ", locations = cells_body(columns = c(est), rows = outcome == "cardiac arrest"), placement = "right") |> 
  tab_footnote("Complications reported included pneumonia, respiratory failure, or un specified.", locations = cells_body(columns = c(outcome), rows = outcome == "Pulmonary Complications")) 
  
```

## Regional versus General Anesthesia

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for regional versus general anesthesia. </font>

```{r reg_gen_balance}
#| warning: false
reg_gen_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "RegionalGeneral", range = "B4:L12") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_reg), paste0(events_reg, " (", n_reg, ")"), NA),
    event_c = ifelse(!is.na(n_gen), paste0(events_gen, " (", n_gen, ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = rct) |> 
  select(-c(events_reg:n_gen, grade_2))

reg_gen_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Regional", columns = c(event_e), level = 1) |>
  tab_spanner(label = "General", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct))) |>
  tab_footnote(md("RCT: randomized clinical trial; [GRADE: Grades of Recommendation, Assessment, Development, and Evaluation](soe_gt.html#grade); RR: risk ratio; MD: mean difference.")) |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  # tab_footnote("Complications include bradycardia, tachycardia, arrhythmia, or unspecified.", locations = cells_body(columns = c(outcome), rows = outcome == "Cardiac complications")) |> 
  tab_footnote("Studies reported 0 and 2 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest"), placement = "right") |> 
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq3.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("Complications reported variously across the 17 trials. ", locations = cells_body(columns = c(rct), rows = outcome == "Complications"), placement = "right") 

```

<br/>

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for regional versus general anesthesia. </font>

```{r reg_gen_complications}
#| warning: false
reg_gen_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "RegionalGeneral", range = "B24:L34") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_reg), paste0(events_reg, " (", n_reg, ")"), NA),
    event_c = ifelse(!is.na(n_gen), paste0(events_gen, " (", n_gen, ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = rct) |> 
  select(-c(events_reg:n_gen, grade_2))

reg_gen_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Regional", columns = c(event_e), level = 1) |>
  tab_spanner(label = "General", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct))) |>
  tab_footnote(md("RCT: randomized clinical trial; [GRADE: Grades of Recommendation, Assessment, Development, and Evaluation](soe_gt.html#grade); RR: risk ratio; MD: mean difference.")) |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Complications as reported included bradycardia (4 studies); unspecified (2 studies); tachycardia (1 study); myocardial infarction, heart failure, or new onset arrhythmia (1 study).", locations = cells_body(columns = c(outcome), rows = outcome == "Cardiac complications")) |> 
  tab_footnote("Studies reported 0 and 2 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest"), placement = "right") |>
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq3.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("Complications reported variously across the 17 trials. ", locations = cells_body(columns = c(rct), rows = outcome == "Complications"), placement = "right") |> 
  tab_footnote("One study no events; the other two. ", locations = cells_body(columns = c(est), rows = outcome == "cardiac arrest"), placement = "right") |> 
  tab_footnote("Complications reported included pneumonia, respiratory failure, or un specified.", locations = cells_body(columns = c(outcome), rows = outcome == "Pulmonary Complications")) 
  

```

## TIVA versus Inhaled Anesthesia

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for TIVA versus inhaled anesthesia. </font>

```{r}
#| warning: false
tiva_inhaled_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "TIVAInhaled", range = "B4:M16") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_tiva), paste0(formattable::comma(events_tiva), " (", formattable::comma(n_tiva), ")"), NA),  
    event_c = ifelse(!is.na(n_inh), paste0(formattable::comma(events_inh), " (", formattable::comma(n_inh), ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_tiva:n_inh, grade_2))

tiva_inhaled_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Regional", columns = c(event_e), level = 1) |>
  tab_spanner(label = "General", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote("RCT: randomized clinical trial; NRSI: nonrandomized studies of interventions; GRADE: Grades of Recommendation, Assessment, Development, and Evaluation; RR: risk ratio; OR: odds ratio; MD: mean difference.") |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Neither study detected a difference.", locations = cells_body(columns = c(est), rows = outcome == "Neurocognitive disorders")) |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("0 events in one study; second did not detect a difference.", locations = cells_body(columns = c(est), rows = outcome == "Pulmonary congestion/edema")) |> 
  tab_footnote("2 versus 0 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest")) |> 
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq4.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") |> 
  tab_footnote("Pending formal inclusion of Ca0 2023.", locations = cells_body(columns = c(grade), rows = outcome == "Delirium" & measure == "RR"))

```

<br/>

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for TIVA versus inhaled anesthesia. </font>

```{r tiva_inhaled_preop_complications}
#| warning: false
tiva_inhaled_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "TIVAInhaled", range = "B29:M37") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_tiva), paste0(formattable::comma(events_tiva), " (", formattable::comma(n_tiva), ")"), NA),  
    event_c = ifelse(!is.na(n_inh), paste0(formattable::comma(events_inh), " (", formattable::comma(n_inh), ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_tiva:n_inh, grade_2))

tiva_inhaled_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(110),
    event_c ~ px(110),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Regional", columns = c(event_e), level = 1) |>
  tab_spanner(label = "General", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote(md("RCT: randomized clinical trial; [GRADE: Grades of Recommendation, Assessment, Development, and Evaluation](soe_gt.html#grade); RR: risk ratio; MD: mean difference.")) |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Complications bradycardia (3 studies); atrial fibrillation (1 study); cardiac dysfunction (1 study).", locations = cells_body(columns = c(outcome), rows = outcome == "Cardiac complications")) |>
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq3.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("Complications reported variously across the 17 trials. ", locations = cells_body(columns = c(rct), rows = outcome == "Complications"), placement = "right") |> 
  tab_footnote("One study no events; the other two. ", locations = cells_body(columns = c(est), rows = outcome == "cardiac arrest"), placement = "right") 
  
```

## Delirium Prophylaxis

### Dexmedetomidine

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for dexmedetomidine versus placebo. </font>

```{r}
#| warning: false
dex_plac_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "DeliriumProph", range = "B4:M10") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_dex), paste0(formattable::comma(events_dex), " (", formattable::comma(n_dex), ")"), NA),  
    event_c = ifelse(!is.na(n_pla), paste0(formattable::comma(events_pla), " (", formattable::comma(n_pla), ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_dex:n_pla, grade_2))

dex_plac_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Dexmedetomidine", columns = c(event_e), level = 1) |>
  tab_spanner(label = "Placebo", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote("RCT: randomized clinical trial; NRSI: nonrandomized studies of interventions; GRADE: Grades of Recommendation, Assessment, Development, and Evaluation; RR: risk ratio; OR: odds ratio; MD: mean difference.") |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Neither study detected a difference.", locations = cells_body(columns = c(est), rows = outcome == "Neurocognitive disorders")) |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("0 events in one study; second did not detect a difference.", locations = cells_body(columns = c(est), rows = outcome == "Pulmonary congestion/edema")) |> 
  tab_footnote("2 versus 0 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest")) |> 
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq4.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") 
  # tab_footnote("Pending formal inclusion of Ca0 2023.", locations = cells_body(columns = c(grade), rows = outcome == "Delirium" & measure == "RR"))

```

<br/>

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for dexmedetomidine versus placebo. </font>

```{r dex_plaaled_preop_complications}
#| warning: false
dex_plac_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "DeliriumProph", range = "B18:M29") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_dex), paste0(formattable::comma(events_dex), " (", formattable::comma(n_dex), ")"), NA),  
    event_c = ifelse(!is.na(n_pla), paste0(formattable::comma(events_pla), " (", formattable::comma(n_pla), ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_dex:n_pla, grade_2))

dex_plac_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(110),
    event_c ~ px(110),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Dexmedetomidine", columns = c(event_e), level = 1) |>
  tab_spanner(label = "Placebo", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote(md("RCT: randomized clinical trial; [GRADE: Grades of Recommendation, Assessment, Development, and Evaluation](soe_gt.html#grade); RR: risk ratio; MD: mean difference.")) |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  # tab_footnote("Complications bradycardia (3 studies); atrial fibrillation (1 study); cardiac dysfunction (1 study).", locations = cells_body(columns = c(outcome), rows = outcome == "Cardiac complications")) |>
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq3.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("Complications reported variously across the 17 trials. ", locations = cells_body(columns = c(rct), rows = outcome == "Complications"), placement = "right") |> 
  tab_footnote("One study no events; the other two. ", locations = cells_body(columns = c(est), rows = outcome == "cardiac arrest"), placement = "right") |> 
  tab_footnote("Complications reported as heart failure (1 study), arrhythmia (1 study), or bradycardia (17 studies).", locations = cells_body(columns = c(outcome), rows = outcome == "Cardiac complications"))
  
```

### Ketamine

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for ketamine versus placebo. </font>

```{r}
#| warning: false
ket_plac_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "DeliriumProph", range = "B41:M49") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_ket), paste0(formattable::comma(events_ket), " (", formattable::comma(n_ket), ")"), NA),  
    event_c = ifelse(!is.na(n_pla), paste0(formattable::comma(events_pla), " (", formattable::comma(n_pla), ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_ket:n_pla, grade_2))

ket_plac_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Dexmedetomidine", columns = c(event_e), level = 1) |>
  tab_spanner(label = "Placebo", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote("RCT: randomized clinical trial; NRSI: nonrandomized studies of interventions; GRADE: Grades of Recommendation, Assessment, Development, and Evaluation; RR: risk ratio; OR: odds ratio; MD: mean difference.") |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Neither study detected a difference.", locations = cells_body(columns = c(est), rows = outcome == "Neurocognitive disorders")) |> 
  # tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("0 events in one study; second did not detect a difference.", locations = cells_body(columns = c(est), rows = outcome == "Pulmonary congestion/edema")) |> 
  tab_footnote("2 versus 0 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest")) |> 
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq4.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") 

```

### Melatonin or Ramelteon

<font size = 4> `r table_ref()` Benefits, harms, and strength of evidence (GRADE) for melatonin or ramelteon versus placebo. </font>

```{r}
#| warning: false
mel_ram_plac_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "DeliriumProph", range = "B56:M62") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_mel_ram), paste0(formattable::comma(events_mel_ram), " (", formattable::comma(n_mel_ram), ")"), NA),  
    event_c = ifelse(!is.na(n_pla), paste0(formattable::comma(events_pla), " (", formattable::comma(n_pla), ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_mel_ram:n_pla, grade_2))

mel_ram_plac_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(100),
    event_c ~ px(100),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Dexmedetomidine", columns = c(event_e), level = 1) |>
  tab_spanner(label = "Placebo", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote("RCT: randomized clinical trial; NRSI: nonrandomized studies of interventions; GRADE: Grades of Recommendation, Assessment, Development, and Evaluation; RR: risk ratio; OR: odds ratio; MD: mean difference.") |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  tab_footnote("Neither study detected a difference.", locations = cells_body(columns = c(est), rows = outcome == "Neurocognitive disorders")) |> 
  # tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("0 events in one study; second did not detect a difference.", locations = cells_body(columns = c(est), rows = outcome == "Pulmonary congestion/edema")) |> 
  tab_footnote("2 versus 0 events.", locations = cells_body(columns = c(est), rows = outcome == "Cardiac arrest")) |> 
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq4.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") 

```

<br/>

<font size = 4> `r table_ref()` Included complications and strength of evidence (GRADE) for melatonin or ramelteon versus placebo. </font>

```{r mel_ram_plaaled_preop_complications}
#| warning: false
mel_ram_plac_dat <- readxl::read_excel("data/balance_tables_2023-09-14_mac_mg.xlsx", sheet = "DeliriumProph", range = "B68:M79") |>
  remove_empty(which = "cols") |>
  clean_names() |>
  rename(est = estimate_95_percent_ci) |>
  filter(!if_all(rct:est, ~ is.na(.x))) |>
  mutate(
    # group = ifelse(outcome == "Patient satisfaction", "Patient-reported", "Clinical"),
    across(everything(), ~ str_remove(.x, "‡|†|\\*")),
    # grade = case_when(
    #   grade == "Very low" ~ vlow,
    #   grade == "Low" ~ low,
    #   grade == "Moderate" ~ mod,
    #   grade == "High" ~ high,
    #   grade == "Low/very low" ~ low_very,
    #   .default = grade
    # ),
    event_e = ifelse(!is.na(n_mel_ram), paste0(formattable::comma(events_mel_ram), " (", formattable::comma(n_mel_ram), ")"), NA),  
    event_c = ifelse(!is.na(n_pla), paste0(formattable::comma(events_pla), " (", formattable::comma(n_pla), ")"), NA),
    across(c(event_e, event_c), ~ str_remove(.x, "NA "))
  ) |> 
  relocate(c(event_e, event_c), .after = nrsi) |> 
  select(-c(events_mel_ram:n_pla, grade_2))

mel_ram_plac_dat |>
  gt(id = "one") |>
  cols_label(
    outcome  = "Outcome",
    rct      = "RCT",
    nrsi     = "NRSI",
    event_e  = "N (Total)",
    event_c  = "N (Total)",
    # n        = "    N",
    grade    = "GRADE",
    measure  = "Effect",
    est      = "Estimate (95% CI)"
  ) |>
  fmt_markdown(columns = c(grade)) |>
  cols_hide(n) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(210),
    rct     ~ px(40),
    nrsi    ~ px(45),
    # n       ~ px(65),
    event_e ~ px(110),
    event_c ~ px(110),
    grade   ~ px(100),
    measure ~ px(45),
    est     ~ px(140)
  ) |> 
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Dexmedetomidine", columns = c(event_e), level = 1) |>
  tab_spanner(label = "Placebo", columns = c(event_c), level = 1) |>
  opt_footnote_marks(marks = "standard") |> 
  tab_style(style = cell_text(align = "center"),        locations = cells_column_labels(columns = c(event_c, event_e))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(n, grade, rct, nrsi))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(est))) |>
  # tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(est))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(grade, measure, rct, nrsi))) |>
  tab_footnote(md("RCT: randomized clinical trial; [GRADE: Grades of Recommendation, Assessment, Development, and Evaluation](soe_gt.html#grade); RR: risk ratio; MD: mean difference.")) |>
  # tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |> 
  # tab_footnote("Complications bradycardia (3 studies); atrial fibrillation (1 study); cardiac dysfunction (1 study).", locations = cells_body(columns = c(outcome), rows = outcome == "Cardiac complications")) |>
  tab_footnote(md("[Comparing higher/highest category or categories compared with lower ones.](kq3.html#patient-satisfaction)"), locations = cells_body(columns = c(est), rows = outcome == "Patient satisfaction"), placement = "right") |> 
  tab_footnote("Cardiovascular, pulmonary, and acute kidney injury.", locations = cells_body(columns = c(outcome), rows = outcome == "Complications")) |> 
  tab_footnote("Complications reported variously across the 17 trials. ", locations = cells_body(columns = c(rct), rows = outcome == "Complications"), placement = "right") |> 
  tab_footnote("One study no events; the other two. ", locations = cells_body(columns = c(est), rows = outcome == "cardiac arrest"), placement = "right") 
  
```
