---
title: "KQ 3 Regional vs. General Anesthesia"
editor: source
toc-title: "Regional vs. General Anesthesia"
toc-location: "left"
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
# bibliography: "bib/kq3.bib"
# csl: jama.csl
# link-citations: yes
# nocite: '@*'
---

## Key Question

Among patients 65 years or older \[geriatric\] undergoing surgery, does regional anesthesia as the primary anesthetic technique improve postoperative outcomes compared with general anesthesia?

<!-- setup -------------------------------------------- (2022-12-24 16:56) @ --->

```{r read_data}
#| include: false
source("code/load_data.R")
settings.meta(CIbracket = "(")
# load("data/geri_data_2023-03-13.Rdata")
study_char_dat <- data_kq(study_char_dat, kq3_refid)
study_arm_dat <- data_kq(study_arm_dat, kq3_refid)
contin_dat <- data_kq(contin_dat, kq3_refid)
dichot_dat <- data_kq(dichot_dat, kq3_refid)
likert_dat <- data_kq(likert_dat, kq3_refid)
```

## Outcome Importance Rankings

<font size = 4> `r table_ref()` Rankings of the 5 most important outcomes (11 respondents). </font>

```{r outcome_priority}
#| include: true
#| eval: true
outcome_dat <- rankings("KQ3")
outcome_tab(outcome_dat, 11)
```

### Reporting Frequency

<font size = 4> `r table_ref()` Dichotomous or count outcomes. </font>

```{r dichot_outcome_freq}
# CODE: reporting frequency tabulation
dichot_freq_fun(dichot_dat, "ADL: activities of daily living; NCR: neurocognitive recovery; NCD: neurocognitive disorder; QoR: quality of recovery; ")
```

<font size = 4> `r table_ref()` Continuous outcomes. </font>

```{r cont_outcome_freq}
contin_freq_fun(contin_dat)
```

<font size = 4> `r table_ref()` Likert or ordinal outcomes. </font>

```{r likert_outcome_freq}
likert_freq_fun(likert_dat, "ADL: activities of daily living; NCR: neurocognitive recovery; NCD: neurocognitive disorder; QoR: quality of recovery; ")
```


## **Included Studies**

<font size = 4> `r table_ref()` Number of studies by design. </font>

<!-- Number of studies by design ----------------------- (2022-12-28 10:44) @ --->

```{r studies_design}
# CODE: study design table — design and number; no duplicate counting
study_char_dat |>
  arrange(year) |> 
  group_by(linked_references_all_refid) |> # count 1 for multiple pubs from single study
  slice(1) |> 
  ungroup() |> 
  # select(refid, study, linked_references_all_refid, design_f_lab) |> # to check studies > 1 report
  select(refid, study, design_f_lab) |>
  group_by(design_f_lab, .drop = TRUE) |>
  summarise(total = n()) |>
  adorn_totals("row") |>
  gt(id = "one") |>
  cols_label(design_f_lab = "Design", total = "Studies") |>
  cols_width(
    # design_f_lab ~ px(200),
    design_f_lab ~ "1.8in",
    total ~ ".5in"
  ) |>
  gt_theme_mg() |> 
  tab_style(
    style = list(
      cell_fill(color = "#E4F3FE"),
      cell_text(weight = "bold"),
      cell_borders(sides = c("top", "bottom"), color = "#9A9EA1", style = "solid", weight = px(1.3))
    ),
    locations = cells_body(
      rows = design_f_lab == "Total"
    )
  ) |> 
  tab_style(
    style = list(
      cell_text(align = "left")),
      locations = cells_body(
        columns = design_f_lab
      )
    ) 
  # tab_footnote("Counted randomized clinical trials with more than 1 publication only once (applied to 2 trials with 2 publications).")
```

### Design, centers, country, and surgery

<font size = 4> `r table_ref()` Study design, enrollment, centers, country, and surgery (see [References](#references) for citations). </font>

<!-- design, enrollment, centers ... ------------------- (2022-12-28 10:44) @ --->

```{r drugs_by_arm}
#| label: design_contry_surg
#| tbl-cap: Study design, enrollment, centers, country, and surgery (see [References](#references) for citations).
#| message: false
# CODE: * drugs & recode drugs/comparators so that usable; "other" category recoded to comparator
# DATA: drugs_dat <- study_arm_dat include drug arm data; adds kq5/6 arms
## drugs; from kq6, add kq5 arm drugs ----------------- (2023-01-16 13:46) @----
# drugs for kq5 studies; needed to fill in "missings" for kq6 arms coded as kq5 arms
kq5_drug_by_arm <- read_csv("data/kq56_drug_by_arm.csv") |>
  rename(drug = drug_f) |> # arm drug
  mutate(drug = as.character(drug)) |> 
  select(refid, arm_id, drug, control_desc)

drugs_dat <- study_arm_dat |>
  # filter(refid %in% c(2598, 13171)) |> 
  select(refid, design_f_lab, study, study_l, study_l_w_linked, study_id, arm_id, arm_n, arm_kq6_proph_meds, kq6_control_desc:kq6_notes, multiple_kq) |>
  rename_with(~ str_replace(., "kq6_", ""), everything()) |>
  rename_with(~ str_replace(., "dex_", "dexmed_"), everything()) |>
  mutate(
    dexmed = ifelse(refid == 13171, NA, dexmed),
    drug = case_when(
      !is.na(dexmed) ~ dexmed,
      !is.na(ketamine) ~ ketamine,
      !is.na(melatonin) ~ melatonin,
      !is.na(ramelteon) ~ ramelteon,
      !is.na(ulinastatin) ~ ulinastatin, # all missing
      !is.na(none) ~ none
    ),
    drug = str_replace(drug, "kq6_", ""),
    drug = firstup(drug)
  ) |>
  relocate(drug, .after = arm_n) |>
  # update drug and control description for "kq5" arms
  left_join(kq5_drug_by_arm, by = c("refid", "arm_id")) |>
  mutate(
    drug = coalesce(drug.x, drug.y),
    control_desc = coalesce(control_desc.x, control_desc.y),
    control_desc = firstup(control_desc),
    arm_proph_meds = ifelse(is.na(arm_proph_meds), "kq5_arm", arm_proph_meds),
  ) |>
  select(-matches("\\.x|\\.y")) |>
  mutate(
  # FIXME: temporary fix for 13171
    drug = ifelse(refid == 13171 & arm_id == 1, "None", drug),
    drug_f = fct(drug,
      levels = c("Dexmedetomidine", "Ketamine", "Melatonin", "Ramelteon", "Ulinastatin", "Midazolam", "Oxazepam", "Haloperidol", "None", "Placebo", "Other")
    ),
    drug_f = fct_collapse(drug_f, "Control" = c("None", "Placebo", "Other"))
  ) |>
  group_by(refid) |>
  mutate(
    drug_study = case_when( # study drug
      if_any(drug_f, ~ . == "Dexmedetomidine") ~ "Dexmedetomidine",
      if_any(drug_f, ~ . == "Ketamine") ~ "Ketamine",
      if_any(drug_f, ~ . == "Melatonin") ~ "Melatonin",
      if_any(drug_f, ~ . == "Ramelteon") ~ "Ramelteon",
      if_any(drug_f, ~ . == "Ulinastatin") ~ "Ulinastatin"
      # TRUE ~ "MISSING" # NA_character_ for verification
    ),
    drug_study = fct(drug_study, levels = c("Dexmedetomidine", "Ketamine", "Melatonin", "Ramelteon", "Ulinastatin")),
    drug_recode = case_when(
      str_detect(other_spec, "Midazolam and propofol") ~ "Midazolam/propofol",
      str_detect(other_spec, "Midazolam and sevoflurane") ~ "Midazolam/sevoflurane",
      str_detect(other_spec, "[Mm]idazolam") ~ "Midazolam",
      str_detect(other_spec, "[Ss]ufentanil") ~ "Sufentanil",
      # str_detect(other_spec, "[Rr]hythim") ~ "Rhythim",
      str_detect(other_spec, "[Pp]ropofol") ~ "Propofol",
      str_detect(other_spec, "[Mm]orphine") ~ "Morphine",
      str_detect(other_spec, "[Pp]regabalin") ~ "Pregabalin",
      .default = drug
    ),
    drug_recode = ifelse(refid == 2748 & arm_id == 4, "Dexmedetomidine/Pregabalin", drug_recode),
    drug_recode = ifelse(refid == 13406 & arm_id == 3, "Dexmedetomidine/Ulinastatin", drug_recode),
    drug_recode = ifelse(refid == 13393 & arm_id == 1, "Dexmedetomidine/Ulinastatin", drug_recode),
    # FIXME: check Mahrose
    drug_recode = ifelse(refid == 13171 & arm_id == 2, "Melatonin/Dexmedetomidine", drug_recode),
    drug_recode = ifelse(refid == 13171 & arm_id == 1, "Dexmedetomidine", drug_recode),
    # HERE
    drug_recode = fct(drug_recode,
      levels = c("Dexmedetomidine", "Dexmedetomidine/Pregabalin", "Dexmedetomidine/Ulinastatin", "Ketamine", "Melatonin", "Melatonin/Dexmedetomidine","Ramelteon", "Ulinastatin", "Haloperidol", "Midazolam", "Oxazepam", "Midazolam/propofol", "Midazolam/sevoflurane", "Morphine", "Pregabalin", "Propofol", "Sufentanil", "Placebo", "None")
    ),
    drug_recode_abbr = fct_recode(drug_recode, Dex = "Dexmedetomidine", "Dex/Preg" = "Dexmedetomidine/Pregabalin", "Dex/Ulin" = "Dexmedetomidine/Ulinastatin", Ket = "Ketamine", Mel = "Melatonin", "Mel/Dex" = "Melatonin/Dexmedetomidine", Ram = "Ramelteon", Ulin = "Ulinastatin", Hal = "Haloperidol", Mid = "Midazolam", Oxaz = "Oxazepam", "Mid/Prop" = "Midazolam/propofol", "Mid/Sevo" = "Midazolam/sevoflurane", MS = "Morphine", Preg = "Pregabalin", Prop = "Propofol", Sufen = "Sufentanil", Plac = "Placebo"),
  ) |>
  ungroup() |>
  relocate(c(drug, drug_f, drug_recode, drug_recode_abbr, drug_study), .after = arm_id) |>
  relocate(c(other_spec, interv_desc, control_desc), .after = last_col()) |>
  arrange(refid, drug_study) |>
# FIXME: 2598  
  fill(drug_study) |>
  arrange(refid, arm_id)
```

```{r included_studies_table}
#| echo: false
included_dat <- study_char_dat |>
  mutate(study_l = study_l_w_linked) |> 
  select(refid, starts_with("design"), study_l, year, n_enroll, n_analyze, centers, country, non_vh_hdi, starts_with("surg")) |>
  # select(refid, study, starts_with("surg")) |> # compile surgeries
  rename_with(~ gsub("surg_", "", .x, fixed = TRUE)) |>
  mutate(across(various:other, ~ gsub("surg_", "", .x, fixed = TRUE)),
    ortho_any = ifelse(if_any(contains("ortho"), ~ !is.na(.x)), "ortho", NA),
    opth = ifelse(str_detect(other_desc, "[Cc]ataract") | !is.na(opth), "optho", opth),
    gi = ifelse(!is.na(colorectal) | !is.na(gi_other) | !is.na(abdominal), "GI/Abdominal", NA),
    across(c(various, cardiac, gyn, general, headneck, hepatic, neuro, opth, oralmax, ortho_any, ent, plastic, spine, thoracic, urol, vasc, other), ~ firstup(.x)),
  ) |>
  unite("surgs", various, cardiac, gyn, gi, general, headneck, hepatic, neuro, opth, oralmax, ortho_any, ent, plastic, spine, thoracic, urol, vasc, other, sep = "|", remove = FALSE, na.rm = TRUE) |>
  select(-c(various, abdominal, cardiac, colorectal, gyn, gi, general, headneck, hepatic, neuro, opth, oralmax, ortho_any, ent, plastic, spine, thoracic, urol, vasc, other, design_other, gi_other, starts_with("ortho"), list, other_desc, starts_with("hip"))) |>
  mutate(
    surgs = ifelse(str_count(surgs, "\\|") > 3, "Various", surgs)
  ) |>
  # left_join(drugs_dat |> group_by(refid) |> slice(1) |> ungroup() |> select(refid, drug_study), by = "refid") |>
  # # create new factor for table as gt not arranging properly
  # mutate(
  #   drug_design = fct(paste0(drug_study, " - ", design_f_lab),
  #     levels = c(
  #       "Dexmedetomidine - Randomized Clinical Trial",
  #       "Dexmedetomidine - Nonrandomized Trial",
  #       "Ketamine - Randomized Clinical Trial",
  #       "Ketamine - Prospective Cohort",
  #       "Melatonin - Randomized Clinical Trial",
  #       "Ramelteon - Randomized Clinical Trial",
  #       "Ramelteon - Before-After/Time Series",
  #       "Ulinastatin - Randomized Clinical Trial"
  #     )
  #   )
  # ) |>
  arrange(design_f, surgs, study_l) |>
  select(refid, design_f, study_l, centers, n_enroll, country, surgs, non_vh_hdi)
# 
# included_dat |>
#   mutate(drug_design = paste(drug_study, design_f_lab)) |>
#   filter(str_detect(drug_design, "NA"))
#   

included_dat |>
  group_by(design_f) |>
  gt(id = "one") |>
  cols_label(
    refid = "ID",
    study_l = "Study",
    n_enroll = "Enrolled",
    country = "Country",
    centers = "Centers",
    surgs = "Surgery"
   ) |>
  cols_hide(non_vh_hdi) |>
    fmt_markdown(columns = c(study_l)) |> 
  cols_width(
    refid ~ px(60),
    study_l ~ px(200),
    centers ~ px(45),
    n_enroll ~ px(55),
    country ~ px(100),
    surgs ~ px(220)
  ) |> 
  # opt_horizontal_padding(scale = 2) |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c("refid"))) |> 
  opt_footnote_marks(marks = "letters") |> 
  tab_footnote(footnote = md("Various indicates more than 4 different types of surgery."), locations = cells_column_labels(columns = surgs)) |>
  tab_footnote(footnote = md("Non very-high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."), 
               locations = cells_column_labels(columns = country)) |>
  tab_footnote(footnote = md("Non very-high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."), 
               locations = cells_body(columns = country, rows = !is.na(non_vh_hdi))) |>
  # tab_footnote(footnote = "Studies examining drugs not directly relevant to recommendations but potentially relevant to the evidence space (eg, a connected network) were included.",  locations = cells_row_groups(groups = )) |> 
  tab_footnote("GI: gastrointestinal; Ortho: orthopedic; Neuro: neurological; Oralmax: oral maxillofacial; Vasc: vascular.")


```

#### Country Summary

<font size = 4> `r table_ref()` Summary of studies by country where conducted. </font>

```{r country}
# CODE: table of countries
study_char_dat |>
  select(country) |>
  tbl_summary(
    sort = everything() ~ "frequency",
    label = list(country ~ "Country")
  ) |>
  modify_header(label ~ "") |> 
  as_gt(id = "one") |> 
  gt_theme_mg()

```



