---
title: "KQ 3 Regional vs. General Anesthesia"
editor: source
toc-title: "Regional vs. General Anesthesia"
toc-location: "left"
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
# bibliography: "bib/kq3.bib"
# csl: jama.csl
# link-citations: yes
# nocite: '@*'
---

## Key Question

Among older patients undergoing surgery and anesthesia, does regional anesthesia as the primary anesthetic technique improve postoperative outcomes compared with general anesthesia?

<!-- setup -------------------------------------------- (2022-12-24 16:56) @ --->

```{r read_data}
#| include: false
source("code/load_data.R")
settings.meta(CIbracket = "(")
kq3_refid <- kq3_refid[kq3_refid != 813]
study_char_dat <- data_kq(study_char_dat, kq3_refid)
study_arm_dat <- data_kq(study_arm_dat, kq3_refid)
contin_dat <- data_kq(contin_dat, kq3_refid)
dichot_dat <- data_kq(dichot_dat, kq3_refid)
likert_dat <- data_kq(likert_dat, kq3_refid)
```

## Outcome Importance Rankings

<font size = 4> `r table_ref()` Rankings of the 5 most important outcomes (11 respondents). </font>

```{r outcome_priority}
#| include: true
#| eval: true
outcome_dat <- rankings("KQ3")
outcome_tab(outcome_dat, 11)
```

### Reporting Frequency

<font size = 4> `r table_ref()` Dichotomous or count outcomes. </font>

```{r dichot_outcome_freq}
# CODE: reporting frequency tabulation
dichot_freq_fun(dichot_dat, "ADL: activities of daily living; NCR: neurocognitive recovery; NCD: neurocognitive disorder; QoR: quality of recovery; ")
```

<font size = 4> `r table_ref()` Continuous outcomes. </font>

```{r cont_outcome_freq}
contin_freq_fun(contin_dat)
```

<font size = 4> `r table_ref()` Likert or ordinal outcomes. </font>

```{r likert_outcome_freq}
likert_freq_fun(likert_dat, "ADL: activities of daily living; NCR: neurocognitive recovery; NCD: neurocognitive disorder; QoR: quality of recovery; ")
```


## **Included Studies**

<font size = 4> `r table_ref()` Number of studies by design. </font>

<!-- Number of studies by design ----------------------- (2022-12-28 10:44) @ --->

```{r studies_design}
# CODE: study design table — design and number; no duplicate counting
study_char_dat |>
  arrange(year) |> 
  group_by(linked_references_all_refid) |> # count 1 for multiple pubs from single study
  slice(1) |> 
  ungroup() |> 
  # select(refid, study, linked_references_all_refid, design_f_lab) |> # to check studies > 1 report
  select(refid, study, design_f_lab) |>
  group_by(design_f_lab, .drop = TRUE) |>
  summarise(total = n()) |>
  adorn_totals("row") |>
  gt(id = "one") |>
  cols_label(design_f_lab = "Design", total = "Studies") |>
  cols_width(
    # design_f_lab ~ px(200),
    design_f_lab ~ "1.8in",
    total ~ ".5in"
  ) |>
  gt_theme_mg() |> 
  tab_style(
    style = list(
      cell_fill(color = "#E4F3FE"),
      cell_text(weight = "bold"),
      cell_borders(sides = c("top", "bottom"), color = "#9A9EA1", style = "solid", weight = px(1.3))
    ),
    locations = cells_body(
      rows = design_f_lab == "Total"
    )
  ) |> 
  tab_style(
    style = list(
      cell_text(align = "left")),
      locations = cells_body(
        columns = design_f_lab
      )
    ) 
  # tab_footnote("Counted randomized clinical trials with more than 1 publication only once (applied to 2 trials with 2 publications).")
```

### Design, centers, country, and surgery

<font size = 4> `r table_ref()` Study design, enrollment, centers, country, and surgery (see [References](#references) for citations). </font>

<!-- design, enrollment, centers ... ------------------- (2022-12-28 10:44) @ --->

```{r included_studies_table}
#| echo: false
included_dat <- study_char_dat |>
  mutate(study_l = study_l_w_linked) |> 
  select(refid, starts_with("design"), study_l, year, n_enroll, n_analyze, centers, country, non_vh_hdi, starts_with("surg")) |>
  # select(refid, study, starts_with("surg")) |> # compile surgeries
  rename_with(~ gsub("surg_", "", .x, fixed = TRUE)) |>
  mutate(across(various:other, ~ gsub("surg_", "", .x, fixed = TRUE)),
    ortho_any = ifelse(if_any(contains("ortho"), ~ !is.na(.x)), "ortho", NA),
    opth = ifelse(str_detect(other_desc, "[Cc]ataract") | !is.na(opth), "optho", opth),
    gi = ifelse(!is.na(colorectal) | !is.na(gi_other) | !is.na(abdominal), "GI/Abdominal", NA),
    across(c(various, cardiac, gyn, general, headneck, hepatic, neuro, opth, oralmax, ortho_any, ent, plastic, spine, thoracic, urol, vasc, other), ~ firstup(.x)),
  ) |>
  unite("surgs", various, cardiac, gyn, gi, general, headneck, hepatic, neuro, opth, oralmax, ortho_any, ent, plastic, spine, thoracic, urol, vasc, other, sep = "|", remove = FALSE, na.rm = TRUE) |>
  select(-c(various, abdominal, cardiac, colorectal, gyn, gi, general, headneck, hepatic, neuro, opth, oralmax, ortho_any, ent, plastic, spine, thoracic, urol, vasc, other, design_other, gi_other, starts_with("ortho"), list, other_desc, starts_with("hip"))) |>
  mutate(
    surgs = ifelse(str_count(surgs, "\\|") > 3, "Various", surgs)
  ) |>
  arrange(design_f, surgs, study_l) |>
  select(refid, design_f, study_l, centers, n_enroll, country, surgs, non_vh_hdi)

included_dat |>
  group_by(design_f) |>
  gt(id = "one") |>
  cols_label(
    refid = "ID",
    study_l = "Study",
    n_enroll = "Enrolled",
    country = "Country",
    centers = "Centers",
    surgs = "Surgery"
   ) |>
  cols_hide(non_vh_hdi) |>
    fmt_markdown(columns = c(study_l)) |> 
  cols_width(
    refid ~ px(60),
    study_l ~ px(200),
    centers ~ px(60),
    n_enroll ~ px(60),
    country ~ px(100),
    surgs ~ px(220)
  ) |> 
  # opt_horizontal_padding(scale = 2) |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c("refid"))) |> 
  opt_footnote_marks(marks = "letters") |> 
  tab_footnote(footnote = md("Various indicates more than 4 different types of surgery."), locations = cells_column_labels(columns = surgs)) |>
  tab_footnote(footnote = md("Non very-high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."), 
               locations = cells_column_labels(columns = country)) |>
  tab_footnote(footnote = md("Non very-high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."), 
               locations = cells_body(columns = country, rows = !is.na(non_vh_hdi))) |>
  # tab_footnote(footnote = "Studies examining drugs not directly relevant to recommendations but potentially relevant to the evidence space (eg, a connected network) were included.",  locations = cells_row_groups(groups = )) |> 
  tab_footnote("GI: gastrointestinal; Ortho: orthopedic; Neuro: neurological; Oralmax: oral maxillofacial; Vasc: vascular.")


```

#### Country Summary

<font size = 4> `r table_ref()` Summary of studies by country where conducted. </font>

```{r country}
# CODE: table of countries
study_char_dat |>
  select(country) |>
  tbl_summary(
    sort = everything() ~ "frequency",
    label = list(country ~ "Country")
  ) |>
  modify_header(label ~ "") |> 
  as_gt(id = "one") |> 
  gt_theme_mg()

```



