---
title: "TIVA versus Inhaled Anesthesia"
editor: source
toc-title: "**TIVA versus Inhaled**"
toc-location: "left"
toc-depth: 3
toc_float: 
  collapsed: false
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
bibliography: "bib/kq4.bib"
csl: jama.csl
link-citations: false
nocite: '@*'
---

## Key Question

Among patients older patients undergoing surgery with general anesthesia, does the use of intravenous agents for maintenance of anesthesia improve postoperative outcomes compared with inhaled agents?

<!-- setup -------------------------------------------- (2022-12-24 16:56) @ --->

```{r read_data}
#| include: false
source("code/load_data.R")
settings.meta(CIbracket = "(")
kq4_refid <- kq4_refid[!kq4_refid %in% c(290)]

study_char_dat <- data_kq(study_char_dat, kq4_refid) |> 
  mutate(
  surgs = ifelse(str_count(surgs, "\\|") > 3 | str_detect(surgs, "Various"), "Various", surgs))

study_arm_dat <- data_kq(study_arm_dat, kq4_refid) |> 
  mutate(arm = ifelse(arm_kq4_iv_inhale == "tiva", "TIVA", "Inhaled"))

contin_dat <- data_kq(contin_dat, kq4_refid) |> 
  left_join(study_arm_dat |> select(refid, arm_id, arm), by = c("refid", "arm_id")) |> 
  relocate(arm, .after = arm_id)

likert_dat <- data_kq(likert_dat, kq4_refid) |> 
  left_join(study_arm_dat |> select(refid, arm_id, arm), by = c("refid", "arm_id")) |> 
  relocate(arm, .after = arm_id)

# VARIABLE: delirium_inc_prop <lgl> [dichot_dat] reported incidence proportion
# VARIABLE: neurocog_inc_prop <lgl> [dichot_dat] reported incidence proportion
# VARIABLE: delirium_day_max <num> [dichot_dat] max of daily 
# VARIABLE: neurocog_day_max <num> [dichot_dat] max of daily 

dichot_dat <- data_kq(dichot_dat, kq4_refid) |>
  mutate(
    delirium_inc_prop = !is.na(delitotal_n), 
    delirium_day_max = pmax(delirium_n1, delirium_n2, delirium_n3, delilast_n, na.rm = TRUE),
    delitotal_n = ifelse(is.na(delitotal_n), delirium_day_max, delitotal_n),
  ) |> 
  relocate(delirium_day_max, .after = delitotal_n) |> 
  left_join(study_arm_dat |> select(refid, arm_id, arm), by = c("refid", "arm_id")) |> 
  relocate(arm, .after = arm_id)
  
# rob_dat <- data_kq(rob_dat, kq4_refid) 
```

## Outcome Importance

<font size = 4> `r table_ref()` Rankings of the 5 most important outcomes (11 respondents). </font>

```{r outcome_priority}
#| include: true
#| eval: true
outcome_dat <- rankings("KQ4")
outcome_tab(outcome_dat, 11)
```

## Outcomes Reported

<font size = 4> `r table_ref()` Dichotomous or count outcomes. </font>

```{r dichot_outcome_freq}
# CODE: reporting frequency tabulation
dichot_freq_fun(dichot_dat, "ADL: activities of daily living; NCR: neurocognitive recovery; NCD: neurocognitive disorder; QoR: quality of recovery; ")
```

<font size = 4> `r table_ref()` Continuous outcomes. </font>

```{r cont_outcome_freq}
contin_freq_fun(contin_dat)
```

<font size = 4> `r table_ref()` Likert or ordinal outcomes. </font>

```{r likert_outcome_freq}
likert_freq_fun(likert_dat, "ADL: activities of daily living; NCR: neurocognitive recovery; NCD: neurocognitive disorder; QoR: quality of recovery; ")
```

## **Included Studies**

<font size = 4> `r table_ref()` Number of studies by design. </font>

```{r studies_design}
# CODE: study design table — design and number; no duplicate studies for kq4
study_char_dat |>
  arrange(year) |> 
  group_by(linked_references_all_refid) |> # count 1 for multiple pubs from single study
  slice(1) |> 
  ungroup() |> 
  # select(refid, study, linked_references_all_refid, design_f_lab) |> # to check studies > 1 report
  select(refid, study, design_f_lab) |>
  group_by(design_f_lab, .drop = TRUE) |>
  summarise(total = n()) |>
  adorn_totals("row") |>
  gt(id = "one") |>
  cols_label(design_f_lab = "Design", total = "Studies") |>
  cols_width(
    # design_f_lab ~ px(200),
    design_f_lab ~ "1.8in",
    total ~ ".5in"
  ) |>
  gt_theme_mg() |> 
  tab_style(
    style = list(
      cell_fill(color = "#E4F3FE"),
      cell_text(weight = "bold"),
      cell_borders(sides = c("top", "bottom"), color = "#9A9EA1", style = "solid", weight = px(1.3))
    ),
    locations = cells_body(
      rows = design_f_lab == "Total"
    )
  ) |> 
  tab_style(
    style = list(
      cell_text(align = "left")),
      locations = cells_body(
        columns = design_f_lab
      )
    ) 
  # tab_footnote("Studies with multiple publications counted only once (applied to 1 trial with 2 publications).")
```

### Design, centers, country, and surgery

<font size = 4> `r table_ref()` Study design, enrollment, centers, country, and surgery (see [References](#references) for citations). </font>

```{r included_studies_table}
#| echo: false
included_dat <- study_char_dat |>
  mutate(study_l = study_l_w_linked) |>
  select(refid, starts_with("design"), study_l, year, n_enroll, n_analyze, centers, country, non_vh_hdi) |>
  left_join(surgs |> select(refid, surgs), by = "refid") |>
  mutate(
    design_f_lab = as.character(design_f_lab),
    surgs = factor(surgs, levels = c("GI/Abdominal", "Cardiac", "Ortho", "Ent", "Ophtho", "Thoracic", "GI/Abdominal|Ortho|Ent", "General|Spine|Thoracic|Urol", "General|Thoracic|Urol", "Headneck", "Spine", "Urol", "Various"))
  ) |>
  arrange(design_f, surgs, study_l) |>
  select(refid, design_f_lab, study_l, centers, n_enroll, country, surgs, non_vh_hdi)

included_dat |>
  group_by(design_f_lab) |> 
  gt(id = "one") |>
  cols_label(
    refid = "ID",
    study_l = "Study",
    n_enroll = "Enrolled",
    country = "Country",
    centers = "Centers",
    surgs = "Surgery"
   ) |>
  cols_hide(c(non_vh_hdi, design_f_lab)) |>
    fmt_markdown(columns = c(study_l)) |> 
  cols_width(
    refid ~ px(60),
    study_l ~ px(165),
    centers ~ px(60),
    n_enroll ~ px(60),
    country ~ px(100),
    surgs ~ px(150)
  ) |> 
  # opt_horizontal_padding(scale = 2) |>
  # row_group_order(groups = c("GI/Abdominal", "Cardiac", "Ortho", "Ent", "Ophtho", "Thoracic", "GI/Abdominal|Ortho|Ent", "General|Spine|Thoracic|Urol", "General|Thoracic|Urol", "Headneck", "Spine", "Urol", "Various")) |>
  sub_missing(columns = everything(), missing_text = " — ") |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c("refid"))) |> 
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(surgs))) |>
  tab_style(style = cell_text(align = "left"),   locations = cells_column_labels(columns = c(surgs))) |>
  opt_footnote_marks(marks = "letters") |> 
  tab_footnote(footnote = md("Various indicates either described as various or more than 4 different types of surgery."), locations = cells_column_labels(columns = surgs)) |>
  tab_footnote(footnote = md("Non very-high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."), 
               locations = cells_column_labels(columns = country)) |>
  tab_footnote(footnote = md("Non very-high [Human Development Index](https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index) country."), 
               locations = cells_body(columns = country, rows = !is.na(non_vh_hdi))) |>
  # tab_footnote(footnote = "Studies examining drugs not directly relevant to recommendations but potentially relevant to the evidence space (eg, a connected network) were included.",  locations = cells_row_groups(groups = )) |> 
  tab_footnote("GI: gastrointestinal; Ortho: orthopedic; Ent: ear, nose, and throat; Neuro: neurological; Oralmax: oral maxillofacial; Vasc: vascular.")

```

### Country Summary

<font size = 4> `r table_ref()` Summary of studies by country where conducted. </font>

```{r country}
study_char_dat |>
  mutate(linked_references = ifelse(is.na(linked_references), refid, linked_references)) |> 
  slice(1, .by = linked_references) |>
  select(country) |>
  tbl_summary(
    sort = everything() ~ "frequency",
    label = list(country ~ "Country")
  ) |>
  modify_header(label ~ "") |> 
  as_gt(id = "one") |> 
  gt_theme_mg()

```

## **Comparators**

```{r tiva_inh_tab}
tiva_inh_tab <- study_arm_dat |>
  select(refid, refid_c, arm_id, study, design_f_lab, year, arm_n, arm, asa_ps_incl, kq4_desflurane, kq4_halothane, kq4_isoflurane, kq4_sevoflurane, kq4_inhale_other, kq4_fentanyl, kq4_propofol, kq4_remifent, kq4_sufentanil, kq4_thiopentone, kq4_tiva_other, kq4_control_desc) |>
  left_join(study_char_dat |> select(refid, study_l, surg_ortho_tka, surg_ortho_tha, surg_ortho_hipfx, surg_ortho_other, surg_list, surgs, surgs_noabbr_f), by = "refid") |>
  left_join(ortho_proc |> select(refid, ortho), by = c("refid")) |>
  left_join(table_age_mn_med, by = c("refid", "arm_id")) |>
  left_join(table_mn_med |> select(refid, arm_id, pre_mmse), by = c("refid", "arm_id")) |>
  rename_with(~ str_replace(.x, "kq4_", "")) |>
  mutate(
    across(desflurane:inhale_other, ~ notna_to_x(.x, symbol = "\U2713")),
    across(fentanyl:tiva_other, ~ notna_to_x(.x, symbol = "\U25CF")),
    remifent = ifelse(str_detect(control_desc, "remifent") & arm == "Inhaled", "\U25CB", remifent),
    propofol = ifelse(str_detect(control_desc, "propofol") & arm == "Inhaled", "\U25CB", propofol),
    fentanyl = ifelse(str_detect(control_desc, "fentanyl") & arm == "Inhaled", "\U25CB", fentanyl),
    sufentanil = ifelse(str_detect(control_desc, "sufentanil") & arm == "Inhaled", "\U25CB", sufentanil),
    remifentanil = ifelse(str_detect(control_desc, "remifentanil") & arm == "Inhaled", "\U25CB", sufentanil),
    thiopentone = ifelse(str_detect(control_desc, "thiopentone") & arm == "Inhaled", "\U25CB", thiopentone),
    surgs = str_replace(surgs, "Ent", "ENT"),
    surgs_design = paste0(surgs, " - ", design_f_lab) 
    # surgs = str_replace(surgs, " Other", ""),
    # surgs = str_replace(surgs, "Ortho ", "Ortho — "),
    # surgs = str_replace(surgs, "\\s{1}$", "")
  ) |>
  select(refid, surgs_design, arm_id, study, study_l, arm_n, arm, asa_ps_incl, age_table, pre_mmse, surgs, surgs_noabbr_f, year, ortho, desflurane:tiva_other) |>
  arrange(surgs, year, study, arm) 
```

#### Randomized

<font size = 4> `r table_ref()` Selected characteristics of randomized clinical trials comparing TIVA with inhaled maintenance anesthesia. </font>

```{r tiva_inh_rct_gt}
#| eval: true
tiva_inh_tab |>
  # randomized or nrsi
  filter(str_detect(surgs_design, "Random")) |> 
  remove_empty(which = "cols") |> 
  # tabyl(surgs_noabbr_f) |> arrange(desc(percent)) |> pull(surgs_noabbr_f) |> toString()
  # filter(!str_detect(surgs_design, "Random"))
  mutate(study_l = ifelse(row_number() > 1, "", study_l), .by = study) |>
  mutate(arm_n = ifelse(refid == 221, "NR", arm_n)) |> 
  group_by(surgs_noabbr_f) |>
  gt(id = "one") |>
  row_group_order(groups =  c("Gastrointestinal/Abdominal", "Various", "Thoracic", "Ophthalmologic", "Otolaryngological", "Orthopedic", "Cardiac", "Urologic", "Head & Neck", "Vascular", "Spine")) |>
  cols_hide(c(refid, arm_id, study, year, ortho, surgs_design, surgs)) |>
  cols_label(
    study_l          = "Study",
    arm_n            = "N ",
    arm              = "Comparator",
    asa_ps_incl      = "PS",
    age_table        = "    Age",
    pre_mmse         = "MMSE",
    desflurane       = "Des",
    # halothane        = "Hal",
    isoflurane       = "Iso",
    sevoflurane      = "Sev",
    inhale_other     = "Oth",
    fentanyl         = "Fen",
    propofol         = "Pro",
    remifent         = "Rem",
    tiva_other       = "Oth"
  ) |>
  tab_spanner(label = "Inhaled", columns = c(desflurane:inhale_other), level = 1) |>
  tab_spanner(label = "ASA", columns = c(asa_ps_incl), level = 1) |>
  tab_spanner(label = "TIVA", columns = c(fentanyl:tiva_other), level = 1) |>
  fmt_markdown(columns = c(study_l, age_table, pre_mmse)) |>
  # fmt_number(VARIABLE, decimals = 0) |>
  sub_missing(columns = everything(), missing_text = "") |>
  gt_theme_mg() |>
  cols_width(
    study_l ~ px(165),
    arm_n ~ px(45),
    arm ~ px(80),
    asa_ps_incl ~ px(60),
    age_table ~ px(100),
    pre_mmse ~ px(100),
    desflurane ~ px(40),
    isoflurane ~ px(40),
    sevoflurane ~ px(40),
    inhale_other ~ px(40),
    fentanyl ~ px(45),
    propofol ~ px(40),
    remifent ~ px(40),
    tiva_other ~ px(40)
  ) |> 
  tab_style(style = list(cell_text(color = color_2)), locations = cells_body(columns = c(arm_n:tiva_other), rows = str_detect(arm, "TIVA"))) |> 
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(asa_ps_incl))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(desflurane:tiva_other))) |> 
  tab_footnote(md("TIVA: total intravenous anesthesia; NR: not reported; ASA PS: ASA Physical Status; MMSE: Mini-Mental State Exam; Des: desflurane; Hal: halothane; Iso: isoflurane; Sev: sevoflurane; Oth: inhale_other; Fen: fentanyl; Pro: propofol; Rem: remifent; Oth: other.")) |> 
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(age_table, pre_mmse))) |> 
  tab_footnote("Thimylal", locations = cells_body(columns = tiva_other, rows = study == "Nishikawa 2007a" & arm_id == 2)) |> 
  tab_footnote("Induction with sevoflurane.", locations = cells_body(columns = c(isoflurane, sevoflurane), rows = study == "Forsmo 2016" & arm_id == 1)) |> 
  tab_footnote("Diazepam.", locations = cells_body(columns = arm, rows = study == "Salonia 2006" & arm_id == 2)) |>
  tab_footnote("Induction with sevoflurane.", locations = cells_body(columns = sevoflurane, rows = study == "Luntz 2004" & arm_id == 1)) |> 
  tab_footnote("Induction with sevoflurane.", locations = cells_body(columns = sevoflurane, rows = study == "Goins 2018" & arm_id == 1)) 
```

#### Nonrandomized

<font size = 4> `r table_ref()` Selected characteristics of nonrandomized studies comparing TIVA with inhaled maintenance anesthesia. </font>

```{r tiva_inh_nrsi_gt}
#| eval: true
tiva_inh_tab |>
  # randomized or nrsi
  filter(!str_detect(surgs_design, "Random")) |> 
  # remove_empty(which = "cols") |> 
  # tabyl(surgs_design) |> arrange(desc(percent)) |> pull(surgs_design) |> toString()
  mutate(study_l = ifelse(row_number() > 1, "", study_l), .by = study) |>
  mutate(arm_n = ifelse(refid == 221, "NR", arm_n)) |> 
  group_by(surgs_design) |>
  gt(id = "one") |>
  row_group_order(groups =  c("Cardiac - Retrospective Cohort", "Various - Retrospective Cohort", "GI/Abdominal - Retrospective Cohort", "General|Spine|Thoracic|Urol - Prospective Cohort", "General|Thoracic|Urol - Prospective Cohort", "Ortho - Prospective Cohort", "Ortho - Retrospective Cohort", "Thoracic - Retrospective Cohort")) |>
  cols_hide(c(refid, arm_id, study, year, ortho, surgs, surgs_noabbr_f, inhale_other, halothane, tiva_other, thiopentone)) |>
  cols_label(
    study_l          = "Study",
    arm_n            = "N ",
    arm              = "Comparator",
    asa_ps_incl      = "PS",
    age_table        = "    Age",
    pre_mmse         = "MMSE",
    desflurane       = "Des",
    isoflurane       = "Iso",
    sevoflurane      = "Sev",
    fentanyl         = "Fen",
    propofol         = "Pro",
    remifent         = "Rem",
    sufentanil       = "Suf"
  ) |>
  tab_spanner(label = "Inhaled", columns = c(desflurane:sevoflurane), level = 1) |>
  tab_spanner(label = "ASA", columns = c(asa_ps_incl), level = 1) |>
  tab_spanner(label = "TIVA", columns = c(fentanyl:sufentanil), level = 1) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |> 
  fmt_markdown(columns = c(study_l, age_table, pre_mmse)) |>
  # fmt_number(VARIABLE, decimals = 0) |>
  sub_missing(columns = everything(), missing_text = "") |>
  gt_theme_mg() |>
  cols_width(
    study_l ~ px(165),
    arm_n ~ px(65),
    arm ~ px(80),
    asa_ps_incl ~ px(60),
    age_table ~ px(100),
    pre_mmse ~ px(100),
    desflurane ~ px(40),
    isoflurane ~ px(40),
    sevoflurane ~ px(40),
    fentanyl ~ px(45),
    propofol ~ px(40),
    remifent ~ px(40),
    sufentanil ~ px(40)
  ) |> 
  tab_style(style = list(cell_text(color = color_2)), locations = cells_body(columns = c(arm_n:sufentanil), rows = str_detect(arm, "TIVA"))) |> 
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(asa_ps_incl))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(desflurane:sevoflurane))) |> 
  tab_footnote(md("TIVA: total intravenous anesthesia; NR: not reported; ASA PS: ASA Physical Status; MMSE: Mini-Mental State Exam; Des: desflurane; Iso: isoflurane; Sev: sevoflurane; Fen: fentanyl; Pro: propofol; Rem: remifent; Suf: sufentanil.")) |> 
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(age_table, pre_mmse))) |> 
  tab_footnote("Either of the two inhalent agents used.", locations = cells_body(columns = c(desflurane, sevoflurane), rows = study %in% c("Koo 2016", "Cho 2021") & arm_id == 1)) |> 
  # tab_footnote("As needed.", locations = cells_body(columns = c(remifent), rows = study == "Cho 2021" & arm_id == 1)) 
  tab_footnote("Any agent used.", locations = cells_body(columns = c(desflurane, sevoflurane, isoflurane) , rows = study == "Yoshimura 2022" & arm_id == 1))
```

## **Delirium Incidence**

```{r delirium_meta_dat}
delirium_meta_dat <- dichot_dat |>
  mutate(arm_n = ifelse(!is.na(deli_update_arm_n), deli_update_arm_n, arm_n)) |> # 2023-05-12 none to be updated
  filter(!is.na(delitotal_est) | !is.na(delilast_est) | !is.na(delirium_disch_est) | !is.na(delitotal_n)) |>
  left_join(study_char_dat |> select(refid, country), by = "refid") |>
  left_join(surgs |> select(refid, surgs_single_f), by = c("refid")) |>
  rename(surg_f = surgs_single_f) |>
  select(refid, refid_c, arm_id, arm_n, year, study, study_l, design_f_lab, country, surg_f, arm, delitotal_time:delitotal_95high, deli_cam:deli_scale_otherspec, deli_update_arm_n, delirium_inc_prop) |>
  arrange(design_f_lab, refid_c, arm_id)

delirium_rr_ref <- delirium_meta_dat |>
   select(refid, refid_c, arm_id, delitotal_n, arm_n) |>
   arrange(refid_c, arm_id) |>
   rename(ref_deli_n = delitotal_n, ref_arm_n = arm_n) |>
   group_by(refid_c) |>
   mutate(
     ref_arm_n = ifelse(row_number() > 1, NA, ref_arm_n),
     ref_deli_n = ifelse(row_number() > 1, NA, ref_deli_n)
   ) |>
   fill(ref_arm_n, ref_deli_n) |>
   mutate(
     ref_arm_n = ifelse(row_number() == 1, NA, ref_arm_n),
     ref_deli_n = ifelse(row_number() == 1, NA, ref_deli_n)
   ) |>
   select(-refid)

delirium_meta_dat <- delirium_meta_dat |>
  remove_empty(which = "cols") |>
  mutate(
    across(starts_with("deli_"), ~ str_remove_all(.x, "scale_")),
    across(starts_with("deli_"), ~ str_remove_all(.x, "deli_")),
    across(deli_cam:deli_scale_otherspec, ~ toupper(.x)),
  ) |>
  rename_with(~ gsub("scale_", "", .x, fixed = TRUE)) |>
  rename_with(~ gsub("deli_", "", .x, fixed = TRUE)) |>
  left_join(delirium_rr_ref, by = c("refid_c", "arm_id")) |>
  mutate(
    other = ifelse(str_detect(otherspec, "ICD"), "ICD codes", other),
    calc_percent = delitotal_n / arm_n * 100,
    n_percent = n_per_fun(delitotal_n, arm_n, 1),
    rr_ci = ifelse(!is.na(ref_arm_n), rr_ci_fun(delitotal_n, arm_n, ref_deli_n, ref_arm_n), "—"),
    or_ci = ifelse(!is.na(ref_arm_n), or_ci_fun(delitotal_n, arm_n, ref_deli_n, ref_arm_n), "—"),
    ln_or = ifelse(!is.na(ref_arm_n), or_ln_te_fun(delitotal_n, arm_n, ref_deli_n, ref_arm_n), NA),
    ln_se_or = ifelse(!is.na(ref_arm_n), or_ln_se_fun(delitotal_n, arm_n, ref_deli_n, ref_arm_n), NA),
    # if reported adjusted or use
    or_ci = ifelse(!is.na(delitotal_est), format_est_ci_fun(delitotal_est, delitotal_95low, delitotal_95high), or_ci),
    ln_or = ifelse(!is.na(delitotal_est), log(delitotal_est), ln_or),
    ln_se_or = ifelse(!is.na(delitotal_est), se_ln_ci_fun(delitotal_95low, delitotal_95high), ln_se_or),
  ) |>
  relocate(calc_percent, .after = delitotal_perc) |>
  unite(compare_groups, c(surg_f, design_f_lab), sep = " – ", remove = FALSE) |> 
  unite(scale_delirium, cam:other, remove = TRUE, sep = "/", na.rm = TRUE) |>
  mutate(
    scale_delirium = ifelse(scale_delirium == "UNSPEC", "NS", scale_delirium),
    effect = ifelse(!str_detect(design_f_lab, "Rand") & arm_id == 2, paste0("<u>", or_ci, "</u>"), rr_ci)) |> 
  left_join(table_mn_med |> select(refid, arm_id, pre_mmse), by = c("refid", "arm_id")) |>
  left_join(table_age_mn_med, by = c("refid", "arm_id")) |>
  relocate(pre_mmse, .before = scale_delirium) |>
  relocate(age_table, .after = arm_n) |>
  select(year, refid, refid_c, design_f_lab, compare_groups, study, study_l, arm_id, arm_n, arm, age_table, pre_mmse, scale_delirium, delitotal_time, delirium_inc_prop, n_percent, delitotal_n, calc_percent, effect, rr_ci, or_ci, ln_or, ln_se_or)

```

<font size = 4> `r table_ref()` Delirium incidence and days of ascertainment during hospitalization in randomized clinical trials comparing TIVA with inhaled anesthetics. </font>

```{r delirium_gt}
# no use of daily max est
delirium_meta_dat |>
  # tabyl(compare_groups) |> pull(compare_groups) |> toString()
  arrange(year, study, arm_id) |>
  mutate(
    delitotal_time = ifelse(delitotal_time == 999, "Stay", as.character(delitotal_time)),
    study_l = ifelse(row_number() > 1, "", study_l),
    delitotal_time = ifelse(row_number() > 1, "", delitotal_time),
    scale_delirium = ifelse(row_number() > 1, "", scale_delirium),
    bar = case_when(
      str_detect(arm, "TIVA") ~ bar_prop(calc_percent, "#A93226"),
      .default = bar_prop(calc_percent, "#969696")
    ),
    .by = study_l
  ) |>
  group_by(compare_groups) |>
  gt(id = "one") |>
  row_group_order(groups = c("GI/Abd – Randomized Clinical Trial", "Ortho – Randomized Clinical Trial", "Various – Randomized Clinical Trial", "Cardiac – Retrospective Cohort", "Various – Prospective Cohort", "Various – Retrospective Cohort")) |>
  cols_hide(c(year, refid, refid_c, design_f_lab, arm_id, study, design_f_lab, age_table, pre_mmse, calc_percent, rr_ci:ln_se_or, delirium_inc_prop, delitotal_n)) |>
  cols_label(
    study_l = "Study",
    arm_n = " N",
    # age_table = "  Age",
    arm = "Arm",
    # pre_mmse = md("  MMSE<br/>  (preop)"),
    scale_delirium = "Scale",
    delitotal_time = "Days",
    n_percent = "N (%)",
    bar = "0 – 100%",
    effect = md("RR <u>OR</U> (95% CI)")
  ) |>
  tab_spanner(label = "Incidence Proportion", columns = c(n_percent, bar)) |>
  fmt_markdown(columns = c(study_l, bar, effect)) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |> 
  sub_values(columns = effect, rows = study %in% c("Nishikawa 2004", "Tanaka 2017"), pattern = ".*", replacement = "") |> # 0 events in an arm 
  gt_theme_mg() |>
  cols_width(
    study_l ~ px(165),
    arm_n ~ px(70),
    # age_table ~ px(100),
    arm ~ px(70),
    # pre_mmse ~ px(95),
    scale_delirium ~ px(105),
    delitotal_time ~ px(50),
    n_percent ~ px(90),
    bar ~ px(100),
    effect ~ px(140)
  ) |> 
  tab_style(style = cell_text(align = "left"),   locations = cells_column_labels(columns = c(study, arm, scale_delirium))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(arm_n, delitotal_time, effect))) |>
  tab_style(style = cell_text(align = "right"),  locations = cells_column_labels(columns = c(n_percent, effect))) |>
  tab_style(style = cell_text(align = "right"),  locations = cells_body(columns = c(n_percent))) |>
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(arm, scale_delirium, bar))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(delitotal_time, effect))) |>
  tab_style(style = list(cell_text(color = "#A93226")), locations = cells_body(columns = c(arm_n:n_percent), rows = str_detect(arm, "TIVA"))) |>
  tab_footnote("RR: risk ratio; OR: odds ratio; DRS: Delirium Rating Scale; CAM: Confusion Assessment Method; NS: not specified.") |>
  # tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(age_table, pre_mmse))) |>
  tab_footnote("Days over which incidence proportion assessed. Stay indicates duration of hospitalization.", locations = cells_column_labels(columns = delitotal_time)) |> 
  tab_footnote("Adjusted from multivariable model.", locations = cells_body(columns = effect, rows = study ==  "Goins 2018" & arm_id == 2)) |> 
  tab_footnote("Propensity score matched.", locations = cells_body(columns = effect, rows = study == "Yoshimura 2022" & arm_id == 2)) 

```

### *Pooled*

<font size = 4> `r figure_ref()` Delirium incidence (TIVA versus inhaled; randomized clinical trials). </font>

```{r delirium_meta_rct_nrsi_dat}
delirium_all_meta_dat <- delirium_meta_dat |> 
  rename(n = delitotal_n) |> 
  select(refid, year, study, design_f_lab, arm, n, arm_n) 

pairs_dat <- pairwise(
  treat = arm,
  event = n,
  n = arm_n,
  studlab = study,
  data = delirium_all_meta_dat,
  sm = "RR",
  keep.all.comparisons = TRUE
)

pairwise_dat <- pairs_dat |>
  select(refid, studlab, treat1, treat2, event1, n1, event2, n2, year, design_f_lab, year) |>
  mutate(
    treat2 = "TIVA",
    treat1 = "Inhaled"
  ) |>
  rename(study = studlab)

delirium_rct_meta_dat <- pairwise_dat |> 
  filter(str_detect(design_f_lab, "Rand")) |>
  left_join(rob2_meta_dat, by = "refid") |> 
  select(-design_f_lab) |> 
  arrange(year, study)

delirium_nsri_meta_dat <- pairwise_dat |> 
  filter(!str_detect(design_f_lab, "Rand")) |> 
  left_join(delirium_meta_dat |> slice(2, .by = refid) |> select(refid, ln_or, ln_se_or), by = "refid") |> 
  left_join(robinsi_meta_dat, by = "refid") |> 
  select(-design_f_lab) |> 
  arrange(year, study)

rm(delirium_all_meta_dat)

```

```{r delirium_meta_rct, warning = FALSE, fig.width = 14, fig.height = 4.0, fig.align = "left"}
delirium_meta_rct <- metabin(event2, n2, event1, n1,
  data = delirium_rct_meta_dat,
  studlab = study,
  sm = "RR",
  method = "MH",
  method.tau = "PM",
  hakn = FALSE,
  prediction = TRUE,
  allstudies = TRUE
)

# too few studies to exam small study effects

forest(delirium_meta_rct,
  allstudies = TRUE,
  label.c = "Inhaled   ",
  label.e = "TIVA   ",
  rightcols = c("effect", "ci", "D1", "D2", "D3", "D4", "D5", "Overall"),
  rightlabs = c("RR", "(95% CI)", "D1", "D2", "D3", "D4", "D5", "All"),
  just.addcols.right = "right",
  digits.TE = 3,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = TRUE,
  fs.xlab = 11,
  pooled.events = TRUE,
  digits = 2, 
  print.pval.Q = FALSE,
  # xlim = c(0.05, 20),
  xlab = "Favors: TIVA                             Inhaled",
  addrows.below.overall = 4
)
```
<foot_mg> RR: risk ratio; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- . <br/> Hartung-Knapp adjustment not applied. Continuity correction of 0.5 added to studies arms with no events. Too few studies to examine small study effects. </foot_mg><br/>

<br/>

<font size = 4> `r figure_ref()` TIVA compared with inhaled anesthetic (nonrandomized designs). </font>

```{r delirium_meta_nrsi, fig.width = 14, fig.height = 3.5, fig.align = "left"}
delirium_meta_nrsi <- metagen(ln_or, ln_se_or,
  data = delirium_nsri_meta_dat,
  sm = "OR",
  backtransf = TRUE
)

forest(delirium_meta_nrsi,
  allstudies = TRUE,
  rightcols = c("effect", "ci", "D1", "D2", "D3", "D4", "D5", "D6", "D7", "Overall"),
  rightlabs = c("OR", "(95% CI)  ", "D1", "D2", "D3", "D4", "D5", "D6", "D7", "All"),
  leftcols = c("study", "event2", "n2", "event1", "n1"), 
  leftlabs = c("Study", "Events", "TIVA    \n Total", "Events", "Inhaled\n Total"),
  just.addcols.right = "center",
  just.addcols.left = "right",
  digits.TE = 3,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = FALSE,
  fs.xlab = 11,
  pooled.events = TRUE,
  digits = 2, 
  print.pval.Q = FALSE,
  xlim = c(0.1, 2),
  xlab = "Favors: TIVA                             Inhaled",
  addrows.below.overall = 4
)
```
<foot_mg> D1: Bias due to confounding; D2: Bias in selection of participants into the study; D3: Bias in classification of interventions; D4: Bias due to deviations from intended interventions; D5: Bias due to missing data; D6: Bias in measurement of outcomes; D7: Bias in selection of reported results; All: overall risk of bias.<br/> Risk of bias ratings: low ++, moderate +, serious -, critical - - ; NI: no information; NA: not applicable. <br/> 
Note: pooling of adjusted odds ratios from Yoshimura 2022 (propensity matching) and Goins 2018 (multivariable adjustment). </foot_mg>

## **Delayed Neurocognitive Recovery**

```{r dncr_ncd_dat}
#| eval: true
# CODE: neurocog meta data munge; here to produce figure
# VARIABLE: postop_only <lgl> from study arm only post-op administration [postop_only_dat]

## dncr_dat ------------------------------------------- (2023-04-15 15:55) @----
dncr_dat <- dichot_dat |>
  filter(if_any(c(neurocog_n1, neurocog_n2, neurocog_n3, neurocog_last_n, neurocog_total_n), ~ !is.na(.x))) |>
  # > 30 day exam
  filter(if_any(matches("neurocog.*time.*"), ~ .x <= 30)) |>
  # select(refid, study, arm_n, neurocog_update_arm_n, neurocog_n1, neurocog_n2, neurocog_n3, neurocog_last_n, neurocog_total_n, matches("neurocog.*time")) |>
  mutate(
    arm_n = ifelse(!is.na(neurocog_update_arm_n), neurocog_update_arm_n, arm_n),
    neurocog_n1 = ifelse(neurocog_time1 > 30, NA, neurocog_n1),
    neurocog_n2 = ifelse(neurocog_time2 > 30, NA, neurocog_n2),
    neurocog_n3 = ifelse(neurocog_time3 > 30, NA, neurocog_n3),
    neurocog_last_n = ifelse(neurocog_last_time > 30, NA, neurocog_last_n),
    neurocog_total_n = ifelse(neurocog_total_time > 30, NA, neurocog_total_n),
    neurocog_time1 = ifelse(neurocog_time1 > 30, NA, neurocog_time1),
    neurocog_time2 = ifelse(neurocog_time2 > 30, NA, neurocog_time2),
    neurocog_time3 = ifelse(neurocog_time3 > 30, NA, neurocog_time3),
    neurocog_last_time = ifelse(neurocog_last_time > 30, NA, neurocog_last_time),
    neurocog_total_time = ifelse(neurocog_total_time > 30, NA, neurocog_total_time),
    dncr_time = pmax(neurocog_time1, neurocog_time2, neurocog_time3, neurocog_last_time, neurocog_total_time, na.rm = TRUE),
    neurocog_total_n = case_when(
      neurocog_time1 == dncr_time ~ neurocog_n1,
      neurocog_time2 == dncr_time ~ neurocog_n2,
      neurocog_time3 == dncr_time ~ neurocog_n3,
      neurocog_last_time == dncr_time ~ neurocog_last_n,
      neurocog_total_time == dncr_time ~ neurocog_total_n
    ),
    neurocog_prop = neurocog_total_n/arm_n,
    neurocog_nper = n_per_fun(neurocog_total_n, arm_n, 1)
  ) |>
  left_join(study_char_dat |> select(refid, country, neuro_threshold), by = "refid") |>
  left_join(surgs |> select(refid, surgs_single_f, surgs_noabbr_f), by = c("refid")) |>
  left_join(table_mn_med |> select(refid, arm_id, pre_mmse), by = c("refid", "arm_id")) |>
  rename(surg_f = surgs_single_f) |>
  arrange(refid_c, arm_id) |>
  mutate(
    bar = case_when(
      str_detect(arm, "TIVA") ~ bar_prop(neurocog_prop * 100, "#A93226"),
      .default = bar_prop(neurocog_prop * 100, "#969696")),
    year = as.numeric(str_extract(study, "\\d{4}")),
    # arm = fct_collapse(arm, "Plac/None" = c("Plac", "None")),
    across(c(arm, design_f_lab, surg_f), ~ fct_drop(.x)),
    scale_mmse = ifelse(!is.na(neurocog_mmse), "\U2713", NA),
    scale_dst = ifelse(!is.na(neurocog_dst) | str_detect(neurocog_scale_otherspec, "[Dd]igit"), "\U2713", NA),
    scale_moca = ifelse(str_detect(neurocog_scale_otherspec, "MoCA|Montreal"), "\U2713", NA),
    scale_other = neurocog_scale_otherspec,
    scale_other = str_to_title(str_replace(scale_other, "Digit [Ss]ymbol [Tt]est; |Digit symbol substitution test; |Montreal Cognitive Assessment \\(MoCA\\)|MoCA", "")),
    scale_other = ifelse(scale_other == "", NA, scale_other),
    scale_other = str_replace_all(scale_other, "Pocd", "POCD"),
    scale_other_tf = ifelse(!is.na(scale_other), "\U2713", NA)
  ) |> 
  select(refid, refid_c, year, arm_id, study, study_l, design_f_lab, pre_mmse, country, surg_f, surgs_noabbr_f, arm, pre_mmse, dncr_time, neurocog_total_n, arm_n, arm, neurocog_nper, neurocog_prop, bar, scale_mmse:scale_other_tf, neuro_threshold)

# add referents for rr calculation
dncr_rr_ref <- dncr_dat |>
  select(refid, refid_c, arm_id, neurocog_total_n, arm_n) |>
  arrange(refid_c, arm_id) |>
  rename(ref_neurocog_n = neurocog_total_n, ref_arm_n = arm_n) |>
  group_by(refid_c) |>
  mutate(
    ref_arm_n = ifelse(row_number() > 1, NA, ref_arm_n),
    ref_neurocog_n = ifelse(row_number() > 1, NA, ref_neurocog_n)
  ) |>
  fill(ref_arm_n, ref_neurocog_n) |>
  mutate(
    ref_arm_n = ifelse(row_number() == 1, NA, ref_arm_n),
    ref_neurocog_n = ifelse(row_number() == 1, NA, ref_neurocog_n)
  ) |>
  select(-refid)

#| DATA: neurocog_allarms_meta_dat for subsequent pooling, arms not collapsed
neurocog_allarms_meta_dat <- dncr_dat |> 
  select(refid, study, design_f_lab, year, arm_id, arm, neurocog_total_n, arm_n, dncr_time, surgs_noabbr_f) 

dncr_dat <- dncr_dat |> 
  left_join(dncr_rr_ref, by = c("refid_c", "arm_id")) |> 
  mutate(rr_ci = ifelse(!is.na(ref_arm_n), rr_ci_fun(neurocog_total_n, arm_n, ref_neurocog_n, ref_arm_n), "—")) |> 
  select(refid, year, design_f_lab, surg_f, surgs_noabbr_f, study, study_l, arm_id, arm_n, arm, pre_mmse, scale_mmse:scale_other_tf, neuro_threshold, dncr_time, neurocog_nper, bar, rr_ci)

rm(dncr_rr_ref)
```

<font size = 4> `r table_ref()` Delayed neurocognitive recovery incidence and ascertainment (TIVA versus inhaled; randomized and nonrandomized designs). </font>

```{r dncr_gt}
#| eval: true

# create footnotes for thresholds
# dncr_dat |>
#   select(refid, study, scale_mmse, scale_dst, scale_moca, neuro_threshold) |>
#   slice(1, .by = refid) |>
#   mutate(
#     neuro_threshold = str_replace(neuro_threshold, "≤-", "≥"),
#     footnotes = case_when(
#     !is.na(scale_mmse) ~ paste0("tab_footnote('", neuro_threshold, ".', locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == '", study, "')) |>"),
#     !is.na(scale_dst) ~ paste0("tab_footnote('", neuro_threshold, ".', locations = cells_body(columns = c(scale_dst), rows = arm_id == 1 & study == '", study, "')) |>"),
#     !is.na(scale_moca) ~ paste0("tab_footnote('", neuro_threshold, ".', locations = cells_body(columns = c(scale_moca), rows = arm_id == 1 & study == '", study, "')) |>")
#   ),
#   footnotes = ifelse(row_number() == n(), str_remove(footnotes, ".{2}$"), footnotes)) |>
#   filter(!is.na(footnotes)) |>
#   pull(footnotes) |>
#   noquote()

dncr_dat |>
  arrange(year, study) |>
  mutate(
    design_surg = paste0(as.character(design_f_lab), " — ", as.character(surgs_noabbr_f)),
    # design_surg = str_remove(design_surg, "Randomized Clinical Trial — ")
  ) |>
  # tabyl(design_surg) |> arrange(desc(percent)) |> pull(design_surg) |> toString()
  mutate(
    study_l = ifelse(row_number() > 1, NA, study_l),
    across(scale_mmse:scale_other_tf, ~ ifelse(row_number() > 1, NA, .x)),
    dncr_time = ifelse(row_number() > 1, NA, dncr_time),
    .by = study
  ) |>
  # tabyl(design_surg) |> arrange(desc(percent))
  group_by(design_surg) |>
  gt(id = "one") |>
  row_group_order(groups = c("Randomized Clinical Trial — Gastrointestinal/Abdominal", "Randomized Clinical Trial — Thoracic", "Randomized Clinical Trial — Otolaryngological", "Randomized Clinical Trial — Spine", "Randomized Clinical Trial — Various", "Randomized Clinical Trial — Vascular", "Prospective Cohort — Orthopedic")) |>
  cols_hide(c(refid, year, arm_id, study, scale_other, design_f_lab, surg_f, neuro_threshold, surgs_noabbr_f)) |>
  cols_label(
    study_l          = "Study",
    arm_n            = " N",
    arm              = "Drug",
    pre_mmse         = "MMSE",
    scale_mmse       = "MMSE",
    scale_dst        = "DST",
    scale_moca       = "MoCA",
    scale_other_tf   = "Other",
    dncr_time        = "Day",
    neurocog_nper    = "N (%)",
    bar              = "0 — 100%",
    rr_ci            = "RR (95% CI)"
  ) |>
  gt_theme_mg() |>
  fmt_markdown(columns = c(study_l, bar, pre_mmse, scale_mmse:scale_other_tf)) |>
  fmt_number(dncr_time, decimals = 0) |>
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Instrument", columns = c(scale_mmse:scale_other_tf), level = 1) |>
  tab_spanner(label = "Delayed Neurocognitive Recovery", columns = c(neurocog_nper:rr_ci), level = 1) |>
  tab_spanner(label = "Preop", columns = c(pre_mmse), level = 1) |>
  cols_width(
    study_l ~ px(165),
    arm_n ~ px(45),
    arm ~ px(70),
    pre_mmse ~ px(100),
    scale_mmse ~ px(50),
    scale_dst ~ px(50),
    scale_moca ~ px(50),
    scale_other_tf ~ px(50),
    dncr_time ~ px(60),
    neurocog_nper ~ px(90),
    bar ~ px(100),
    rr_ci ~ px(140),
  ) |>
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels(columns = c(study, arm))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(starts_with("scale"), pre_mmse, dncr_time, neurocog_nper, rr_ci))) |>
  tab_style(style = cell_text(align = "right"), locations = cells_column_labels(columns = c(neurocog_nper))) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(study, arm, pre_mmse))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(starts_with("scale"), dncr_time, rr_ci))) |>
  tab_style(style = cell_text(align = "right"), locations = cells_body(columns = c(neurocog_nper))) |>
  tab_style(style = list(cell_text(color = "#A93226")), locations = cells_body(columns = c(arm_n:pre_mmse, neurocog_nper), rows = str_detect(arm, "TIVA"))) |>
  tab_footnote("Mini-Mental State Exam; DST: Digit Span Test; MoCA: Montreal Cognitive Assessment; RR: risk ratio; Dex: Dexmedetomidine; Mid: Midazolam; Prop: Propofol; Ulin: ulinastatin; Plac/None: placebo or no intervention.") |>
  tab_footnote("Day of assessment.", locations = cells_column_labels(columns = c(dncr_time))) |>
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(pre_mmse))) |>
  tab_footnote("Z ≥1.96.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Zhang 2018a")) |>
  tab_footnote("Difference from baseline >20%.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Egawa 2016")) |>
  tab_footnote("Difference from baseline >20%.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Geng 2017")) |>
  tab_footnote("Z ≥1.96.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Tang 2014")) |>
  tab_footnote("Difference from baseline >2 pts.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Qiao 2023")) |>
  tab_footnote("Z ≥1.96.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Li 2021a")) |>
  tab_footnote("Z ≥1.96.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Konishi 2018")) |>
  tab_footnote("Z ≥1.96.", locations = cells_body(columns = c(scale_mmse), rows = arm_id == 1 & study == "Rohan 2005"))

```

### *Pooled*

<font size = 4> `r figure_ref()` Delayed neurocognitive recovery assessed postoperative day 3 or later (TIVA versus inhaled; randomized clinical trials). </font>

```{r dncr_meta_dat}
#| eval: true
# NOTE: 2023-04-20 adding ketamine studies to dexmedetomidine dncr would not connect any network; so left distinct
neurocog_meta_dat <- neurocog_allarms_meta_dat |>
  filter(dncr_time >= 3) |> 
  # collapse arms
  mutate(
    neurocog_total_n = case_when(
      study == "Geng 2017" & arm_id == 1 ~ collapse_dichot(neurocog_allarms_meta_dat, "Geng 2017", c(1, 2), neurocog_total_n),
      .default = neurocog_total_n
    ),
    arm_n = case_when(
      study == "Geng 2017" & arm_id == 1 ~ collapse_dichot(neurocog_allarms_meta_dat, "Geng 2017", c(1, 2), arm_n),
      .default = arm_n
    )
  ) |>
  filter(!(study %in% c("Geng 2017") & arm_id %in% c(2))) |>
  left_join(surgs |> select(refid, surgs_single_f), by = c("refid")) 
```

```{r dncr_meta}
#| eval: true
# CODE: dncr meta data, pairwise and network (netmeta)
nma_dncr_dat <- neurocog_meta_dat |>
  mutate(time = ifelse(dncr_time < 3, "at <3 days", "at ≥3 days" )) |> 
  filter(time == "at ≥3 days") |> 
  select(-dncr_time) |> 
  filter(design_f_lab == "Randomized Clinical Trial") 

pairs_dat <- pairwise(
  treat = arm,
  event = neurocog_total_n,
  n = arm_n,
  studlab = study,
  data = nma_dncr_dat,
  sm = "RR",
  keep.all.comparisons = TRUE
)

```

```{r dncr__meta, fig.width = 14, fig.height = 4, fig.align = "left", warning = FALSE}
#| eval: true
dncr_meta_dat <- pairs_dat |>
  arrange(year, study) |> 
  left_join(rob2_meta_dat, by = "refid") |>
  select(refid, study, year, event2, n2, event1, n1, D1:Overall, surgs_single_f) |>
  mutate(
    rob = case_when(
      Overall == "+" ~ "Low",
      Overall == "?" ~ "Some Concerns",
      Overall == "–" ~ "High"
    )
  ) |>
  left_join(study_char_dat |> select(refid, country), by = "refid") |> 
  arrange(study)

tiva_inhaled_meta <- metabin(event2, n2, event1, n1,
  data = dncr_meta_dat,
  studlab = study,
  sm = "RR",
  method = "MH",
  method.tau = "PM",
  hakn = TRUE,
  prediction = TRUE,
  allstudies = TRUE,
  # subgroup = country
  )
# summary(plac_meta)
forest(tiva_inhaled_meta,
  # sortvar = year,
  allstudies = TRUE,
  common = TRUE,
  label.e = "TIVA     ",
  label.c = "Inhaled  ",
  rightcols = c("effect", "ci", "surgs_single_f", "D1", "D2", "D3", "D4", "D5", "Overall"),
  rightlabs = c("RR ", "(95% CI)   ", "Procedure", "D1", "D2", "D3", "D4", "D5", "All"),
  just.addcols.right = "left",
  digits = 2,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  # subgroup = TRUE,
  # print.subgroup.labels = TRUE,
  print.I2.ci = TRUE,
  prediction = TRUE,
  colgap.right = "5mm",
  fs.xlab = 11,
  pooled.events = TRUE,
  print.pval.Q = FALSE,
  xlim = c(0.1, 3),
  xlab = "Favors: TIVA                    Inhaled",
  addrows.below.overall = 4
  # text.addline1 = "Hartung-Knapp adjustment not applied owing to subgroups — overall RR 0.55 (95% CI, 0.37–0.79) when used.",
  # text.addline2 = "Excluding studies with assessments at less than 3 days (95% prediction interval, 0.24–0.92)."
)  

```
<foot_mg> RR: risk ratio; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .<br/> 
Five trials conducted in China and 1 each in Norway and Japan.</foot_mg><br/>

## **Neurocognitive Disorders**

<font size = 4> `r table_ref()` Neurocognitive disorders and ascertainment (TIVA versus inhaled; prospective cohort studies). </font>

```{r ncd_dat}
ncd_dat <- dichot_dat |>
  filter(if_any(c(neurocog_n1, neurocog_n2, neurocog_n3, neurocog_last_n, neurocog_total_n), ~ !is.na(.x))) |>
  # > 30 day exam
  filter(if_any(matches("neurocog.*time.*"), ~ .x > 30)) |>
  mutate(
    arm_n = ifelse(!is.na(neurocog_update_arm_n), neurocog_update_arm_n, arm_n),
    ncd_time = case_when(
      neurocog_time1 > 30 ~ neurocog_time1,
      neurocog_time2 > 30 ~ neurocog_time2,
      neurocog_time3 > 30 ~ neurocog_time3,
      neurocog_last_time > 30 ~ neurocog_last_time,
      neurocog_total_time > 30 ~ neurocog_total_time,
      .default = NA
    ),
    neurocog_total_n = case_when(
      neurocog_time1 > 30 ~ neurocog_n1,
      neurocog_time2 > 30 ~ neurocog_n2,
      neurocog_time3 > 30 ~ neurocog_n3,
      neurocog_last_time > 30 ~ neurocog_last_n,
      neurocog_total_time > 30 ~ neurocog_total_n
    ),
    neurocog_prop = neurocog_total_n / arm_n,
    neurocog_nper = n_per_fun(neurocog_total_n, arm_n, 1)
  ) |>
  left_join(study_char_dat |> select(refid, country), by = "refid") |>
  left_join(surgs |> select(refid, surgs_single_f), by = c("refid")) |>
  left_join(table_mn_med |> select(refid, arm_id, pre_mmse), by = c("refid", "arm_id")) |>
  rename(surg_f = surgs_single_f) |>
  arrange(refid, arm_id) |>
  mutate(
    bar = case_when(
      str_detect(arm, "Inhaled") ~ bar_prop(neurocog_prop * 100, "#969696"),
      str_detect(arm, "TIVA") ~ bar_prop(neurocog_prop * 100, color_2),
      .default = bar_prop(neurocog_prop * 100, color_1)),
    year = as.numeric(str_extract(study, "\\d{4}")),
    scale_mmse = ifelse(!is.na(neurocog_mmse), "\U2713", NA),
    scale_dst = ifelse(!is.na(neurocog_dst) | str_detect(neurocog_scale_otherspec, "[Dd]igit"), "\U2713", NA),
    scale_moca = ifelse(str_detect(neurocog_scale_otherspec, "MoCA|Montreal"), "\U2713", NA),
    scale_other = neurocog_scale_otherspec,
    scale_other = str_to_title(str_replace(scale_other, "Digit [Ss]ymbol [Tt]est; |Digit symbol substitution test; |Montreal Cognitive Assessment \\(MoCA\\)|MoCA", "")),
    scale_other = ifelse(scale_other == "", NA, scale_other),
    scale_other = str_replace_all(scale_other, "Pocd", "POCD"),
    scale_other_tf = ifelse(!is.na(scale_other), "\U2713", NA)
  ) |>
  select(refid, year, arm_id, study, study_l, design_f_lab, pre_mmse, country, surg_f, pre_mmse, ncd_time, neurocog_total_n, arm_n, arm, neurocog_nper, neurocog_prop, bar, scale_mmse:scale_other_tf)

ncd_rr_ref <- ncd_dat |>
  select(refid, arm_id, neurocog_total_n, arm_n) |>
  arrange(refid, arm_id) |>
  rename(ref_neurocog_n = neurocog_total_n, ref_arm_n = arm_n) |>
  group_by(refid) |>
  mutate(
    ref_arm_n = ifelse(row_number() > 1, NA, ref_arm_n),
    ref_neurocog_n = ifelse(row_number() > 1, NA, ref_neurocog_n)
  ) |>
  fill(ref_arm_n, ref_neurocog_n) |>
  mutate(
    ref_arm_n = ifelse(row_number() == 1, NA, ref_arm_n),
    ref_neurocog_n = ifelse(row_number() == 1, NA, ref_neurocog_n)
  )

ncd_dat <- ncd_dat |>
  left_join(ncd_rr_ref, by = c("refid", "arm_id")) |>
  mutate(rr_ci = ifelse(!is.na(ref_arm_n), rr_ci_fun(neurocog_total_n, arm_n, ref_neurocog_n, ref_arm_n), "—")) |>
  select(refid, year, design_f_lab, study, study_l, arm_id, arm_n, arm, pre_mmse, scale_mmse:scale_other_tf, ncd_time, neurocog_nper, bar, rr_ci)
```

```{r ncd_gt}
#| eval: true
ncd_dat |>
  arrange(year, study) |>
  mutate(study_l = ifelse(row_number() > 1, NA, study_l),
         across(scale_mmse:scale_other_tf, ~ ifelse(row_number() > 1, NA, .x)),
         ncd_time = ifelse(row_number() > 1, NA, ncd_time),
         .by = study) |>
  group_by(design_f_lab) |>
  gt(id = "one") |>
  row_group_order(groups = c("Prospective Cohort")) |>
  cols_hide(c(refid, year, arm_id, study, scale_other)) |>
  cols_label(
    study_l          = "Study",
    arm_n            = " N",
    arm              = "Comparator",
    pre_mmse         = "MMSE",
    scale_mmse       = "MMSE",
    scale_dst        = "DST",
    scale_moca       = "MoCA",
    scale_other_tf   = "Other",
    ncd_time         = "Day",
    neurocog_nper    = "N (%)",
    bar              = "0 — 100%",
    rr_ci            = "RR (95% CI)"
  ) |>
  gt_theme_mg() |>
  fmt_markdown(columns = c(study_l, bar, pre_mmse, scale_mmse:scale_other_tf)) |>
  fmt_number(ncd_time, decimals = 0) |>
  sub_missing(columns = everything(), missing_text = "") |>
  tab_spanner(label = "Instrument", columns = c(scale_mmse:scale_other_tf), level = 1) |>
  tab_spanner(label = "Neurocognitive Disorders", columns = c(neurocog_nper:rr_ci), level = 1) |>
  tab_spanner(label = "Preop", columns = c(pre_mmse), level = 1) |>
  cols_width(
    study_l          ~ px(165),
    arm_n            ~ px(45),
    arm              ~ px(70),
    pre_mmse         ~ px(80),
    scale_mmse       ~ px(50),
    scale_dst        ~ px(50),
    scale_moca       ~ px(50),
    scale_other_tf   ~ px(50),
    ncd_time         ~ px(60),
    neurocog_nper    ~ px(90),
    bar              ~ px(100),
    rr_ci            ~ px(140),
  ) |>
  tab_style(style = cell_text(align = "left"),        locations = cells_column_labels(columns = c(study, arm))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(starts_with("scale"), pre_mmse, ncd_time, neurocog_nper, rr_ci))) |>
  # tab_style(style = cell_text(align = "right"),       locations = cells_column_labels(columns = c(neurocog_nper))) |>
  tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(study, arm, pre_mmse))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(starts_with("scale"), ncd_time, rr_ci))) |>
  tab_style(style = cell_text(align = "right"),       locations = cells_body(columns = c(neurocog_nper))) |>
  tab_style(style = list(cell_text(color = color_2)), locations = cells_body(columns = c(arm_n:pre_mmse, neurocog_nper), rows = str_detect(arm, "TIVA"))) |>
  tab_footnote("Mini-Mental State Exam; DST: Digit Span Test; MoCA: Montreal Cognitive Assessment; RR: risk ratio; Gen: general anesthesia; Reg: regional anesthesia.") |>
  tab_footnote("Day of assessment.",                   locations = cells_column_labels(columns = c(ncd_time))) |>
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(pre_mmse))) |> 
  tab_footnote('Z ≥1.96.', locations = cells_body(columns = c(scale_dst), rows = arm_id == 1 & study == 'Rasmussen 2003')) |> 
  tab_footnote("Uniform Data Set Battery", locations = cells_body(columns = c(scale_other_tf), rows = study == "Deiner 2015" & arm_id == 1))
```

<br/>

## **Complications**

```{r complications_check}
#| eval: false
# create excel file to inspect
complication_fun <- function(var_prefix) {
  dichot_dat %>%
    filter(if_any(!!paste0(var_prefix, "_per"):!!paste0(var_prefix, "_95high"), ~ !is.na(.x))) |>
    select(refid, study, arm_id, arm, arm_n, comp_update_arm_n, !!paste0(var_prefix, "_n"):!!paste0(var_prefix, "_95high"))
}

complication_incl <- c("cardiac", "myoinfarct", "cardarr", "stroke", "kidneyinj", "asppneum", "atelec", "pulm", "pneum", "pthorax", "airleak", "pulcongest", "pe", "pinfiltrate", "respfail", "intub", "upperair", "vent48")

# complication <- c("medical", "surg", "cardiac", "gastro", "neuro", "pulm", "thromb", "infect", "fall", "stroke", "othcomp", "asppneum", "atelec", "bronch", "cardarr", "myoinfarct", "ssi", "sepsis", "uti", "pneum", "pthorax", "airleak", "pulcongest", "pe", "pinfiltrate", "respfail", "intub", "upperair", "vent48", "kidneyinj", "nerveinj", "clavien1", "clavien2", "clavien3", "clavien4", "clavien5")

adverse_events_dat <- map(complication_incl, complication_fun)

wb <- openxlsx::createWorkbook("kq4_complications")

for (i in 1:17) {
    temp_sheet <- adverse_events_dat[[i]]
    addWorksheet(wb, sheetName = complication_incl[i])
    setColWidths(wb, i, cols = c(1:12), widths = c(rep(15, 12)))
    writeData(wb, sheet = i, temp_sheet)
}

path <- glue::glue("/Users/mgrant/Desktop/temp.xlsx")
saveWorkbook(wb, "/Users/mgrant/Desktop/kq4.xlsx", overwrite = TRUE)
```

<font size = 4> `r table_ref()` Reported complications in TIVA versus general anesthesia — cardiac, pulmonary, and acute kidney injury (TIVA versus inhaled; randomized and nonrandomized designs). </font>

```{r complications}
#| warning: false
#| eval: true

# included complications
complication_incl <- c("cardiac", "myoinfarct", "cardarr", "stroke", "kidneyinj", "asppneum", "atelec", "pulm", "pneum", "pthorax", "airleak", "pulcongest", "pe", "pinfiltrate", "respfail", "intub", "upperair", "vent48")

# complication_all <- c("medical", "surg", "cardiac", "gastro", "neuro", "pulm", "thromb", "infect", "fall", "stroke", "othcomp", "asppneum", "atelec", "bronch", "cardarr", "myoinfarct", "ssi", "sepsis", "uti", "pneum", "pthorax", "airleak", "pulcongest", "pe", "pinfiltrate", "respfail", "intub", "upperair", "vent48", "kidneyinj", "nerveinj", "clavien1", "clavien2", "clavien3", "clavien4", "clavien5")

complication_fun <- function(var_prefix) {
  dichot_dat %>%
    filter(if_any(!!paste0(var_prefix, "_per"):!!paste0(var_prefix, "_95high"), ~ !is.na(.x))) |>
    select(refid, year, study, arm_id, arm, arm_n, comp_update_arm_n, !!paste0(var_prefix, "_n"):!!paste0(var_prefix, "_95high")) |>
    mutate(complication = var_prefix) |>
    rename_with(~ str_replace(.x, "95", "ci_"), .cols = everything()) |>
    rename_with(~ str_replace(.x, "^.*_", ""), .cols = c(8:15)) |>
    arrange(complication, year, study, arm_id)
}

# adverse event data includes all reported complications in liss=t
adverse_events_dat <- map_df(complication_incl, complication_fun) |>
  mutate(
    arm_n = ifelse(!is.na(comp_update_arm_n), comp_update_arm_n, arm_n),
    calc_per = n / arm_n * 100,
    n_per = n_per_fun(n, arm_n, 1),
    diff = per - calc_per
  )

# if RR convert to OR get ln_te ln_se
# if reported OR use ests to get ln_te ln_se
# if neither use estimate

adverse_events_dat <- adverse_events_dat |>
  left_join(study_char_dat |> select(refid, study_l, surgs_single, design_f_lab), by = "refid") |>
  left_join(table_age_mn_med, by = c("refid", "arm_id")) |>
  arrange(complication, surgs_single, year, study, arm_id) |>
  mutate(
    study_compl = paste0(study, complication),
    ref_arm_n = arm_n,
    ref_n = n
  ) |>
  group_by(study_compl) |>
  mutate(
    ref_arm_n = ifelse(row_number() > 1, NA, ref_arm_n),
    ref_n = ifelse(row_number() > 1, NA, ref_n)
  ) |>
  fill(ref_arm_n, ref_n) |>
  mutate(
    ref_arm_n = ifelse(row_number() == 1, NA, ref_arm_n),
    ref_n = ifelse(row_number() == 1, NA, ref_n)
  ) |>
  ungroup() |>
  mutate(
    # Luntz 2004 combine inhalation arms; differed in induction
    ref_arm_n = ifelse(study == "Luntz 2004" & arm_id == 3, 64, ref_arm_n),
    ref_n = ifelse(study == "Luntz 2004" & arm_id == 3, 5, ref_n),
    ref_arm_n = ifelse(study == "Luntz 2004" & arm_id == 2, NA, ref_arm_n),
    ref_n = ifelse(study == "Luntz 2004" & arm_id == 2, NA, ref_n),
    rd_ci = ifelse(!is.na(ref_n), rd_per_ci_fun(n, arm_n, ref_n, ref_arm_n, digits = 1), "—"),
    or_ci = ifelse(!is.na(ref_n) & n != 0 & ref_arm_n != 0, or_ci_fun(n, arm_n, ref_n, ref_arm_n, digits = 2), "—"), # not if any Os
    rr_ci = ifelse(!is.na(ref_n) & n != 0 & ref_arm_n != 0, rr_ci_fun(n, arm_n, ref_n, ref_arm_n, digits = 2), "—"), # not if any Os
    # or_ci = ifelse(!is.na(ref_n), or_ci_fun(n, arm_n, ref_n, ref_arm_n, digits = 2), "—"),
    or_ln_te = ifelse(!is.na(ref_n), or_ln_te_fun(n, arm_n, ref_n, ref_arm_n), NA),
    or_ln_se_te = ifelse(!is.na(ref_n), or_ln_se_fun(n, arm_n, ref_n, ref_arm_n), NA),
    bar = case_when(
      # str_detect(arm, "Dex") ~ bar_prop(calc_per, "#A93226"),
      # str_detect(arm, "Ket|Mel|Ram") ~ bar_prop(calc_per, "#A93226"),
      str_detect(arm, "Inhaled") ~ bar_prop(calc_per, "#969696"),
      .default = bar_prop(calc_per, "#A93226"))) |>
  select(refid, year, arm_id, study, study_l, study_compl, arm_n, arm, n, age_table, surgs_single, n_per, bar, rd_ci, rr_ci, or_ci, or_ln_te, or_ln_se_te, complication, design_f_lab, effect:high)

# temp <- adverse_events_dat |>
#   # filter(!str_detect(design_f_lab, "Random")) |>
#   mutate(
#     effect = ifelse(is.na(est), "OR", effect),
#     est = case_when(
#       !is.na(effect) & !is.na(est) & !is.na(low + high) ~ paste0(est, " (", sprintf("%.2f", low), ", ", sprintf("%.2f", high), ")"),
#       is.na(est) & effect == "OR" ~ or_ci),
#     # est = ifelse(is.na(est), or_ci, est),
#     # effect = ifelse(est == "—", NA, effect),
#     # # est = ifelse(!is.na(low) & effect != "RD", paste0(est, " (", sprintf("%.2f", low), ", ", sprintf("%.2f", high), ")"), est)
#   ) |>
#   mutate(effect = ifelse(est == "—", NA, effect)) |>
#   select(refid, study,  arm_n, arm, n, est, n_per, bar, effect, low, high, or_ci, rd_ci, rr_ci, complication, design_f_lab)
```

```{r complications_gt}
#| eval: true
# propensity matched
# Park 2020 (refid: 1134), Oh 2019 (refid: 132), Yoshimura 2022 (refid: 16890)
propensity_refid <- c(1134, 132, 16890)

adverse_events_gt_dat <- adverse_events_dat |>
  filter(complication %in% complication_incl) |>
  mutate(complication = factor(complication, levels = c("cardiac", "myoinfarct", "cardarr", "kidneyinj", "pneum", "pulcongest", "pe", "respfail"), labels = c("Cardiac", "MI", "Cardiac Arrest", "AKI", "Pneumonia", "Pulmonary Congestion", "PE", "Respiratory Failure"))) |>
  arrange(year, study, arm) |>
  mutate(
    rd_or = ifelse(refid %in% propensity_refid & row_number() != 1, paste0("<u>", or_ci, "</u>"), rd_ci),
    rd_or = ifelse(rd_or == "<u>—</u>", "—", rd_or),
    surgs_single = ifelse(surgs_single == "Vasc", "Vascular", surgs_single),
    study_l = ifelse(row_number() > 1, "", study_l),
    surgs_single = ifelse(row_number() > 1, "", surgs_single),
    complication = fct_drop(complication),
    .by = study_compl
  ) |>
  unite(complication, complication, design_f_lab, sep = " – ") 

adverse_meta_dat <- adverse_events_gt_dat |>
  select(refid, year, study, arm_id, arm, arm_n, n, complication, or_ln_te, or_ln_se_te) |>
  mutate(
    n = case_when(
      study == "Luntz 2004" & arm_id == 1 ~ collapse_dichot(adverse_events_gt_dat, "Luntz 2004", c(1, 2), n),
      .default = n
    ),
    arm_n = case_when(
      study == "Luntz 2004" & arm_id == 1 ~ collapse_dichot(adverse_events_gt_dat, "Luntz 2004", c(1, 2), arm_n),
      .default = arm_n
    )
  ) |>
  filter(!(study %in% c("Luntz 2004") & arm_id  == 2)) 

adverse_meta_wide_dat <- adverse_meta_dat |> 
  arrange(refid, complication) |> 
  pivot_wider(names_from = "arm", values_from = arm_n:n) |> 
  group_by(refid, complication) |> 
  fill(or_ln_te:n_TIVA) |> 
  slice(2) |> 
  ungroup() |> 
  mutate(
    complication_nodesign = str_remove(complication, " – .*$"),
    study_design = ifelse(str_detect(complication, "Rand"), paste0(study, "*"), study),
    complication_nodesign = factor(complication_nodesign, levels = c("Cardiac", "MI", "Cardiac Arrest", "Pneumonia", "Pulmonary Congestion", "PE", "Respiratory Failure", "AKI"), labels = c("Cardiac", "MI", "Cardiac Arrest", "Pneumonia", "Pulmonary Congestion", "Pulmonary Embolism", "Respiratory Failure", "Acute Kidney Injury"))
  )

adverse_events_gt_dat |> 
  # tabyl(complication) |> arrange(desc(percent)) |> pull(complication) |> toString()
  group_by(complication) |>
  gt(id = "one") |>
  row_group_order(groups = c("Cardiac – Randomized Clinical Trial", "MI – Randomized Clinical Trial", "MI – Retrospective Cohort", "Cardiac Arrest – Retrospective Cohort", "Pneumonia – Randomized Clinical Trial", "Respiratory Failure – Randomized Clinical Trial", "Respiratory Failure – Retrospective Cohort", "PE – Randomized Clinical Trial", "PE – Retrospective Cohort", "Pulmonary Congestion – Retrospective Cohort", "AKI – Retrospective Cohort")) |>
  cols_hide(c(refid, year, study, arm_id, n, study, study_compl, rd_ci, rr_ci, or_ci, or_ln_te, or_ln_se_te, effect, adjcrude, est, low, high )) |>
  cols_label(
    study_l          = "Study",
    arm_n            = " N",
    arm              =  "Arm",
    age_table        = "    Age",
    surgs_single     = "Surgery",
    n_per            = "N (%)",
    bar              = "0 – 100%",
    rd_or            = md("RD <u>OR</u> (95% CI)")
  ) |>
  # tab_spanner(label = "", columns = c(VARIABLES), level = 1) |>
  fmt_markdown(columns = c(study_l, bar, age_table, rd_or)) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |> 
  sub_missing(columns = everything(), missing_text = "") |>
  gt_theme_mg() |>
  cols_width(
    study_l          ~ px(140),
    arm_n            ~ px(60),
    arm              ~ px(60),
    age_table        ~ px(100),
    surgs_single     ~ px(80),
    n_per            ~ px(90),
    bar              ~ px(100),
    rd_or            ~ px(140)
  ) |>
  tab_style(style = cell_text(align = "left"),        locations = cells_column_labels(columns = c(arm))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(arm_n, rd_or))) |>
  # tab_style(style = cell_text(align = "right"),      locations = cells_column_labels(columns = c())) |>
  tab_style(style = cell_text(align = "left"),        locations = cells_body(columns = c(arm, age_table, rd_or, surgs_single))) |>
  tab_style(style = cell_text(align = "center"),      locations = cells_body(columns = c(rd_or))) |>
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(age_table))) |> 
  tab_footnote("Odds ratios reported for propensity-matched studies (risk difference with 95% CI reported accounting for matching were not reported).", locations = cells_column_labels(columns = c(rd_or))) |> 
  tab_footnote("RD: risk difference; OR: odds ratio; Ophtho: ophthalmologic.") |> 
  tab_footnote("Compared with combined inhalation arms — differed only in induction agents.", locations = cells_body(columns = c(rd_or), rows = study == "Luntz 2004" & arm_id == 3)) |>
  tab_style(style = list(cell_text(color = "#A93226")), locations = cells_body(columns = c(arm_n:age_table, n_per), rows = str_detect(arm, "TIVA"))) 
  # tab_style(style = cell_text(align = "right"),       locations = cells_body(columns = c())) |>
  # tab_style(style = cell_text(align = "center", font = "IBM Plex Mono"), locations = cells_body(columns = c(asa_ps_incl))) |>
  # tab_style(style = list(cell_text(color = "#969696")), locations = cells_body(columns = c(arm_n:age_table, n_per), rows = str_detect(arm, "Inhaled"))) |>
  # tab_style(style = list(cell_text(color = "#F39C12")), locations = cells_body(columns = c(arm_n:age_table, n_per), rows = str_detect(arm, "Ket|Mel|Ram"))) |>
  # tab_style(style = list(cell_text(color = "#969696")), locations = cells_body(columns = c(arm_n:age_table, n_per), rows = str_detect(arm, "Plac|None"))) |>
  # gtsave(filename = "/Users/mgrant/Desktop/table.", inline_css = TRUE)
```

### *Pooled*

```{r complication_meta,  fig.width = 14, fig.height = 12.5, fig.align = "left"}
complication_meta_fun <- function(compl_label, use_hakn = TRUE, predictive = TRUE){
meta_dat <- adverse_meta_wide_dat |>
  select(-complication) |>
  rename(complication = complication_nodesign) |>
  filter(complication %in% compl_label) |> 
  left_join(rob2_meta_dat, by = "refid")

complication_bin <- metagen(
  or_ln_te, or_ln_se_te,
  data = meta_dat,
  studlab = study,
  sm = "OR",
  prediction = predictive,  
  hakn = use_hakn,
  allstudies = FALSE,
)  
}

complication_forest_fun <- function(adverse_meta, use_predictive = TRUE){
forest(adverse_meta,
  allstudies = TRUE,
  random = TRUE,
  rightcols = c("effect", "ci"),
  rightlabs = c("OR ", "(95% CI)   "),
  leftcols = c("study_design", "n_TIVA", "arm_n_TIVA", "n_Inhaled", "arm_n_Inhaled"), 
  leftlabs = c("Complication &\nStudy", "Events", "TIVA\n Total", "Events", "Inhaled\n Total"),
  colgap.right = "4mm",
  just.addcols.right = "center",
  just.addcols.left = "right",
  digits.TE = 3,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  # print.subgroup.name = FALSE,
  overall = TRUE,
  print.I2.ci = TRUE,
  prediction = use_predictive,
  fs.xlab = 11,
  # pooled.events = TRUE,
  digits = 2, 
  print.pval.Q = FALSE,
  xlim = c(0.1, 10),
  xlab = "Favors: TIVA                             Inhaled",
  addrows.below.overall = 4,
  text.addline1 = "*Randomized clinical trial."
)
}

complication_forest_rct_fun <- function(adverse_meta, use_predictive = TRUE){
forest(adverse_meta,
  allstudies = TRUE,
  random = TRUE,
  # rightcols = c("effect", "ci"),
  # rightlabs = c("OR ", "(95% CI)   "),
  leftcols = c("study_design", "n_TIVA", "arm_n_TIVA", "n_Inhaled", "arm_n_Inhaled"), 
  leftlabs = c("Complication &\nStudy", "Events", "TIVA\n Total", "Events", "Inhaled\n Total"),
  rightcols = c("effect", "ci", "D1", "D2", "D3", "D4", "D5", "Overall"),
  rightlabs = c("OR ", "(95% CI)   ", "D1", "D2", "D3", "D4", "D5", "All"),
  colgap.right = "4mm",
  just.addcols.right = "center",
  just.addcols.left = "right",
  digits.TE = 3,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  # print.subgroup.name = FALSE,
  overall = TRUE,
  print.I2.ci = TRUE,
  prediction = use_predictive,
  fs.xlab = 11,
  # pooled.events = TRUE,
  digits = 2, 
  print.pval.Q = FALSE,
  xlim = c(0.1, 10),
  xlab = "Favors: TIVA                             Inhaled",
  addrows.below.overall = 4,
  text.addline1 = "*Randomized clinical trial."
)
}

## old code ------------------------------------------- (2023-05-22 10:23) @----
# adverse_meta <- metagen(or_ln_te, or_ln_se_te,
#   data = adverse_meta_wide_dat,
#   sm = "OR",
#   backtransf = TRUE,
#   subgroup = complication_nodesign
# )  


# forest(adverse_meta,
#   allstudies = TRUE,
#   random = TRUE,
#   rightcols = c("effect", "ci"),
#   rightlabs = c("OR ", "(95% CI)   "),
#   leftcols = c("study_design", "n_TIVA", "arm_n_TIVA", "n_Inhaled", "arm_n_Inhaled"), 
#   leftlabs = c("Complication &\nStudy", "Events", "TIVA\n Total", "Events", "Inhaled\n Total"),
#   colgap.right = "4mm",
#   just.addcols.right = "center",
#   just.addcols.left = "right",
#   digits.TE = 3,
#   digits.tau2 = 1,
#   overall.hetstat = FALSE,
#   print.subgroup.name = FALSE,
#   overall = FALSE,
#   print.I2.ci = TRUE,
#   prediction = FALSE,
#   fs.xlab = 11,
#   # pooled.events = TRUE,
#   digits = 2, 
#   print.pval.Q = FALSE,
#   xlim = c(0.1, 10),
#   xlab = "Favors: TIVA                             Inhaled",
#   addrows.below.overall = 4,
#   text.addline1 = "*Randomized clinical trial."
# )
```

#### Cardiac Composite

<font size = 4> `r figure_ref()` Risk ratio for composite measures of cardiac complications (TIVA versus inhaled anesthesia; randomized clinical trials). </font>

```{r complication_cardiac,  fig.width = 14, fig.height = 3.75, fig.align = "left"}
temp_meta <- complication_meta_fun("Cardiac", use_hakn = FALSE)
complication_forest_rct_fun(temp_meta)
```
<foot_mg> RR: risk ratio; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .<br/>
Hartung-Knapp adjustment not used — applying yielded a 95% confidence interval of (0.33–4.19).
</foot_mg> 

#### Myocardial Infarction

<font size = 4> `r figure_ref()` Risk ratio for myocardial infarction (regional versus general anesthesia; randomized and nonrandomized studies). </font>

```{r complication_mi,  fig.width = 14, fig.height = 3.75, fig.align = "left"}
temp_meta <- complication_meta_fun("MI", use_hakn = FALSE)
complication_forest_fun(temp_meta)
```
<foot_mg> RR: risk ratio; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .<br/>
Similar arms combined for Liang 2017.
</foot_mg> 

#### Stroke

Not reported in included studies.

#### Acute Kidney Injury

<font size = 4> `r figure_ref()` Risk ratio for acute kidney injury (regional versus general anesthesia; nonrandomized studies). </font>

```{r complication_aki,  fig.width = 14, fig.height = 3.35, fig.align = "left"}
temp_meta <- complication_meta_fun("Acute Kidney Injury", use_hakn = FALSE, predictive = FALSE)
complication_forest_fun(temp_meta)
```
<foot_mg> RR: risk ratio; ; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .<br/>
</foot_mg> 

#### Pulmonary

Complications categorized as "pulmonary" not reported in included studies.

#### Pneumonia

<font size = 4> `r figure_ref()` Risk ratio for pneumonia (regional versus general anesthesia; randomized clinical trials). </font>

```{r complication_pneumonia,  fig.width = 14, fig.height = 3.35, fig.align = "left"}
temp_meta <- complication_meta_fun("Pneumonia", use_hakn = FALSE, predictive = FALSE)
complication_forest_rct_fun(temp_meta, use_predictive = FALSE)
```
<foot_mg> RR: risk ratio; ; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .<br/>
Similar arms combined for Bielka 2021 and Liang 2017.
</foot_mg> 

#### Pulmonary Embolism

<font size = 4> `r figure_ref()` Risk ratio for pulmonary embolism (regional versus general anesthesia; randomized clinical trials). </font>

```{r complication_pe,  fig.width = 14, fig.height = 3.35, fig.align = "left"}
temp_meta <- complication_meta_fun("Pulmonary Embolism", use_hakn = FALSE, predictive = FALSE)
complication_forest_fun(temp_meta, use_predictive = FALSE)
```
<foot_mg> RR: risk ratio; ; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .<br/>
Similar arms combined for Liang 2017.
</foot_mg> 

```{r complication_pulmonary-congestion,  fig.width = 14, fig.height = 2, fig.align = "left"}
#| eval: false
temp_meta <- complication_meta_fun("Pulmonary Congestion", use_hakn = FALSE, predictive = FALSE)
complication_forest_fun(temp_meta)

```

## **Patient Satisfaction**

<font size = 4> `r table_ref()` Patient satisfaction according to TIVA or inhalation anesthesia. </font>

```{r pt_satisfaction}
satis_dat_gt <- dichot_dat |>
  select(refid, year, study, study_l, arm_id, arm_n, arm, design_f_lab, matches("satis"), notes_d) |>
  left_join(surgs |> select(refid, surgs_noabbr_f), by = "refid") |>
  left_join(study_arm_dat |> select(refid, arm_id, asa_ps_incl), by = c("refid", "arm_id")) |>
  left_join(table_age_mn_med, by = c("refid", "arm_id")) |> # age_table
  filter(if_any(satis_n:satis_95high, ~ !is.na(.x))) |>
  select(!c(d_satisfaction, satis_pval:satis_95high)) |>
  mutate(
    n_percent = n_per_fun(satis_n, arm_n, n_sig_dig = 1),
    bar = case_when(
      str_detect(arm, "Inhaled") ~ bar_prop(satis_n / arm_n * 100, "#969696"),
      str_detect(arm, "TIVA") ~ bar_prop(satis_n / arm_n * 100, color_2)
    )
  ) |>
  arrange(year, study, arm_id) 

satis_dat_gt <- satis_dat_gt |>
  mutate(
    satis_n = case_when(
      study == "Luntz 2004" & arm_id == 1 ~ collapse_dichot(satis_dat_gt, "Luntz 2004", c(1, 2), satis_n),
      .default = satis_n
    ),
    arm_n = case_when(
      study == "Luntz 2004" & arm_id == 1 ~ collapse_dichot(satis_dat_gt, "Luntz 2004", c(1, 2), arm_n),
      .default = arm_n
    )
  ) |>
  filter(!(study %in% c("Luntz 2004") & arm_id == 2)) |>
  mutate(
    ref_arm_n = arm_n,
    ref_n = satis_n
  ) |>
  group_by(refid) |>
  mutate(
    ref_arm_n = ifelse(row_number() > 1, NA, ref_arm_n),
    ref_n = ifelse(row_number() > 1, NA, ref_n)
  ) |>
  fill(ref_arm_n, ref_n) |>
  mutate(
    ref_arm_n = ifelse(row_number() == 1, NA, ref_arm_n),
    ref_n = ifelse(row_number() == 1, NA, ref_n)
  ) |>
  ungroup() |>
  mutate(
    rd_ci = ifelse(!is.na(ref_n), rd_per_ci_fun(satis_n, arm_n, ref_n, ref_arm_n, digits = 1), "—")
  )
  
satis_dat_gt |> 
 mutate(study_l = ifelse(row_number() > 1, "", study_l), 
        surgs_noabbr_f = ifelse(row_number() > 1, "", as.character(surgs_noabbr_f)), 
        surgs_noabbr_f = ifelse(str_detect(surgs_noabbr_f, "Gast"), "GI/Abdominal", surgs_noabbr_f), 
        asa_ps_incl = ifelse(row_number() > 1, "", asa_ps_incl), 
        .by = study) |>
  gt(id = "one") |>
  cols_hide(c(refid, year, arm_id, study, design_f_lab, satis_n, satis_per, notes_d, ref_arm_n, ref_n)) |>
  cols_label(
    study_l          = "Study",
    arm_n            = " N",
    arm              = "Anesth",
    asa_ps_incl      = "PS",
    age_table        = "Age",
    surgs_noabbr_f   = "Surgery",
    n_percent        = "     N (%)",
    bar              = "0 – 100%",
    rd_ci            = "RD (95% CI)"
  ) |>
  tab_spanner(label = "ASA", columns = c(asa_ps_incl), level = 1) |>
  fmt_markdown(columns = c(study_l, age_table, bar)) |>
  sub_missing(columns = everything(), missing_text = "") |>
  gt_theme_mg() |>
  cols_width(
    study_l          ~ px(165),
    arm_n            ~ px(45),
    arm              ~ px(80),
    asa_ps_incl      ~ px(60),
    age_table        ~ px(80),
    surgs_noabbr_f   ~ px(100),
    n_percent        ~ px(100),
    bar              ~ px(100),
    rd_ci            ~ px(140),
  ) |> 
  tab_style(style = cell_text(align = "center", font = "IBM Plex Mono"), locations = cells_body(columns = c(asa_ps_incl))) |>
  tab_style(style = cell_text(align = "left"),        locations = cells_column_labels(columns = c(study, arm))) |> 
  tab_style(style = cell_text(align = "center"),      locations = cells_column_labels(columns = c(asa_ps_incl, age_table, n_percent))) |> 
  tab_footnote("Mean (SD).",   locations = cells_column_labels(columns = c(age_table))) |>
  tab_footnote("TIVA: total intravenous anesthesia; ASA PS: ASA Physical Status; RD: risk difference.") |> 
  tab_style(style = list(cell_text(color = color_2)), locations = cells_body(columns = c(arm_n:n_percent), rows = str_detect(arm, "TIVA"))) |> 
  tab_footnote("Completely satisfied.",               locations = cells_body(columns = c(n_percent), rows = study == "Epple 2001"), placement = "right") |>  
  tab_footnote("Highly satisfied.",                   locations = cells_body(columns = c(n_percent), rows = study == "Luntz 2004"), placement = "right") |>  
  tab_footnote("Inhaled arms combined.",              locations = cells_body(columns = c(arm_n), rows = study == "Luntz 2004" & arm == "Inhaled"), placement = "right") |>  
  tab_footnote("Very satisfied.",                     locations = cells_body(columns = c(n_percent), rows = study == "Nishikawa 2007a"), placement = "right") 

```

### *Pooled*

<font size = 4> `r figure_ref()` Risk difference in patient satisfaction (TIVA versus inhaled; randomized clinical trials). </font>

```{r satis_rct_meta, fig.dim = c(14, 3), fig.align = "center"}
satis_meta_dat <- satis_dat_gt |> 
  select(refid, year, study, arm, satis_n, arm_n) |> 
  pivot_wider(names_from = "arm", values_from = satis_n:arm_n) |> 
  left_join(rob2_meta_dat, by = "refid") 

satis_meta <- metabin(satis_n_TIVA, arm_n_TIVA, satis_n_Inhaled, arm_n_Inhaled,
  data = satis_meta_dat,
  studlab = study,
  # cluster = refid,
  sm = "RR",
  method = "MH",
  method.tau = "REML",
  hakn = FALSE,
  prediction = FALSE,
  allstudies = TRUE,
)

# summary(plac_meta)
forest(satis_meta,
  allstudies = TRUE,
  # random = FALSE,
  label.e = "TIVA     ",
  label.c = "Inhaled     ",
  rightcols = c("effect", "ci", "D1", "D2", "D3", "D4", "D5", "Overall"),
  rightlabs = c("RR", "(95% CI)", "D1", "D2", "D3", "D4", "D5", "All"),
  just.addcols.right = "right",
  colgap.right = "4mm",
  digits.TE = 3,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = FALSE,
  fs.xlab = 11,
  pooled.events = TRUE,
  pscale = 100,
  digits = 2, 
  print.pval.Q = FALSE,
  # xlim = c(0.1, 20),
  xlab = "Favors: Inhaled                       TIVA       ",
  addrows.below.overall = 4
)

```
<foot_mg> RD: risk difference; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .</foot_mg> 

<br/>

## **Length of Stay**

<font size = 4> `r table_ref()` Length of stay according to procedure classification and comparator. </font>

```{r length_of_stay}
#| eval: true
los_tab <- contin_dat |>
  mutate(los_for_tables(contin_dat)) |>
  filter(if_any(los_m:los_diff_pval, ~ !is.na(.))) |>
  left_join(table_age_mn_med, by = c("refid", "arm_id")) |> # age_table
  left_join(study_arm_dat |> select(refid, arm_id, asa_ps_incl), by = c("refid", "arm_id")) |>
  left_join(surgs |> select(refid, surgs_noabbr_f), by = c("refid")) |>
  left_join(study_char_dat |> select(refid, country), by = "refid" ) |> 
  mutate(
    refid_arm_id = paste0(refid, "-", arm_id),
    surg_groups = paste0(design_f_lab, " - ", surgs_noabbr_f),
    mean_med = case_when(
      !is.na(los_m) ~ los_m,
      !is.na(los_med) ~ los_med
    ),
    calc_prop_35d = 100 * mean_med / 35,
    bar = case_when(
      str_detect(arm, "TIVA") ~ bar_prop(calc_prop_35d, "#A93226"),
      .default = bar_prop(calc_prop_35d, "#969696")
    )
  ) |>
  arrange(surg_groups, year, study, arm_id) |> 
  select(refid, refid_arm_id, study, study_l, arm_n, arm, asa_ps_incl, age_table, los_table, bar, surg_groups, country)

los_tab |>
  mutate(study_l = ifelse(row_number() > 1, "", study_l),
         country = ifelse(row_number() > 1, "", country),
         .by = refid) |> 
  # tabyl(surg_groups) |> pull(surg_groups) |> toString()
  group_by(surg_groups) |>
  gt(id = "one") |>
  row_group_order(groups = c("Randomized Clinical Trial - Gastrointestinal/Abdominal", "Randomized Clinical Trial - Thoracic", "Randomized Clinical Trial - Various", "Retrospective Cohort - Cardiac", "Retrospective Cohort - Orthopedic", "Retrospective Cohort - Various")) |> 
  cols_hide(c(refid, refid_arm_id, study)) |>
  cols_label(
    study_l = "Study",
    arm_n = " N",
    arm = "Anesth",
    asa_ps_incl = "PS",
    age_table = "    Age",
    los_table = "    LOS",
    bar = "0 – 35 days",
    country = "Country"
  ) |>
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |> 
  cols_width(
    study_l ~ px(165),
    arm_n ~ px(60),
    arm ~ px(80),
    asa_ps_incl ~ px(60),
    age_table ~ px(100),
    los_table ~ px(100),
    bar ~ px(120),
    country ~ px(80)
    )  |> 
  fmt_markdown(columns = c(study_l, bar, age_table, los_table)) |> 
  tab_style(style = cell_text(align = "center", font = "IBM Plex Mono"), locations = cells_body(columns = c(asa_ps_incl))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(arm_n, arm,  bar))) |>
  tab_style(style = cell_text(align = "left"),   locations = cells_column_labels(columns = c(study_l, age_table, los_table))) |>
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(study_l, age_table, los_table, bar, arm))) |> 
  tab_style(style = list(cell_text(color = "#A93226")), locations = cells_body(columns = c(arm_n:los_table), rows = str_detect(arm, "TIVA"))) |> 
  tab_footnote(md("NR: not reported")) |> 
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(age_table, los_table))) |> 
  tab_footnote(md("ASA Physical Status."), locations = cells_column_labels(columns = c(asa_ps_incl)))
  
```

### *Pooled*

<font size = 4> `r figure_ref()` Mean difference in lengths of stay (TIVA versus inhaled; randomized clinical trials). </font>

```{r los_meta, fig.width = 14, fig.height = 3, fig.align = "left"}
los_meta_dat <- contin_dat |>
  filter(refid %in% los_tab$refid) |> 
  select(refid, study, design_f_lab, arm, arm_n, los_m, los_sd, los_med, los_rl, los_ru, los_iqrl, los_iqru, los_95l, los_95u) |> 
  rename_with(~ str_remove(.x, "los_")) |> 
  select(!matches("95")) |> 
  pivot_wider(names_from = "arm", values_from = arm_n:iqru) |> 
  mutate(year = str_extract(study, "\\d{4}")) |> 
  arrange(year) 

los_rct_meta_dat <- los_meta_dat |> 
  filter(str_detect(design_f_lab, "Rand")) |> 
  left_join(rob2_meta_dat, by = "refid") |> 
  left_join(surgs |> select(refid, surgs_single), by = "refid")

los_nrsi_meta_dat <- los_meta_dat |> 
  filter(!str_detect(design_f_lab, "Rand")) |> 
  left_join(robinsi_meta_dat, by = "refid") |> 
  left_join(surgs |> select(refid, surgs_single), by = "refid")

los_meta <- metacont(
  n.e = arm_n_TIVA, 
  n.c = arm_n_Inhaled,
  common =  TRUE,
  mean.e = m_TIVA,
  sd.e = sd_TIVA,
  median.e = med_TIVA,
  q1.e = iqrl_TIVA,
  q3.e = iqru_TIVA,
  min.e = rl_TIVA,
  max.e = ru_TIVA,
  mean.c = m_Inhaled,
  sd.c = sd_Inhaled,
  median.c = med_Inhaled,
  q1.c = iqrl_Inhaled,
  q3.c = iqru_Inhaled,
  min.c = rl_Inhaled,
  max.c = ru_Inhaled,
  data = los_rct_meta_dat,
  sm = "MD",
  method.tau = "REML",
  hakn = FALSE,
  prediction = TRUE,
  studlab = study
)

forest(los_meta,
  weight.study = "random",
  common =  FALSE,
  label.e = "TIVA     ",
  label.c = "Inhaled   ",
  print.tau2 = FALSE,
  print.tau = TRUE,
  print.tau.ci = TRUE,
  digits = 1,
  digits.sd = 1,
  digits.mean = 1,
  digits.tau = 1,
  # digits.pval.Q = 2,
  print.I2.ci = TRUE,
  fs.xlab = 10,
  just.addcols.right = "right",
  print.pval.Q = FALSE,
  # sortvar = -TE,
  xlim = c(-10, 10),
  # at = c(-80, -60, -40, -20, 0, 20, 40),
  rightcols = c("effect", "ci", "surgs_single", "D1", "D2", "D3", "D4", "D5", "Overall"),
  rightlabs = c("MD ", "(95% CI)   ", "Procedure", "D1", "D2", "D3", "D4", "D5", "All"),
  xlab = "Favors: TIVA                                      Inhaled           ",
  smlab = "Mean Difference (days)",
  addrows.below.overall = 4
)

```
<foot_mg> RR: risk ratio; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .<br/>
When the mean or standard deviation were not reported, they were imputed from from the median, interquartile range, and/or range.  </foot_mg> 

<font size = 4> `r figure_ref()` Mean difference in lengths of stay (TIVA versus inhaled; nonrandomized designs). </font>

```{r los_nrsi_meta, fig.width = 14, fig.height = 3, fig.align = "left"}
los_meta <- metacont(
  n.e = arm_n_TIVA, 
  n.c = arm_n_Inhaled,
  common =  TRUE,
  mean.e = m_TIVA,
  sd.e = sd_TIVA,
  median.e = med_TIVA,
  q1.e = iqrl_TIVA,
  q3.e = iqru_TIVA,
  min.e = rl_TIVA,
  max.e = ru_TIVA,
  mean.c = m_Inhaled,
  sd.c = sd_Inhaled,
  median.c = med_Inhaled,
  q1.c = iqrl_Inhaled,
  q3.c = iqru_Inhaled,
  min.c = rl_Inhaled,
  max.c = ru_Inhaled,
  data = los_nrsi_meta_dat,
  sm = "MD",
  method.tau = "REML",
  hakn = FALSE,
  prediction = TRUE,
  studlab = study
)

forest(los_meta,
  weight.study = "random",
  common =  FALSE,
  label.e = "TIVA     ",
  label.c = "Inhaled   ",
  print.tau2 = FALSE,
  print.tau = TRUE,
  print.tau.ci = TRUE,
  digits = 1,
  digits.sd = 1,
  digits.mean = 1,
  digits.tau = 1,
  print.I2.ci = TRUE,
  fs.xlab = 10,
  just.addcols.right = "right",
  print.pval.Q = FALSE,
  # sortvar = -TE,
  xlim = c(-10, 10),
  # at = c(-80, -60, -40, -20, 0, 20, 40),
  rightcols = c("effect", "ci", "surgs_single", "D1", "D2", "D3", "D4", "D5", "D6", "D7", "Overall"),
  rightlabs = c("MD", "(95% CI)  ", "Procedure", "D1", "D2", "D3", "D4", "D5", "D6", "D7", "All"),
  xlab = "Favors: TIVA                                      Inhaled           ",
  smlab = "Mean Difference (days)",
  addrows.below.overall = 4
)

```
<foot_mg> D1: Bias due to confounding; D2: Bias in selection of participants into the study; D3: Bias in classification of interventions; D4: Bias due to deviations from intended interventions; D5: Bias due to missing data; D6: Bias in measurement of outcomes; D7: Bias in selection of reported results; All: overall risk of bias.<br/> Risk of bias ratings: low ++, moderate +, serious -, critical - - ; NI: no information; NA: not applicable. <br/> 
When the mean or standard deviation were not reported, they were imputed from from the median, interquartile range, and/or range.  </foot_mg> 

## **Mortality**

```{r mortality_data}
#| eval: true
mortality_dat <- dichot_dat |>
  filter(if_any(starts_with("mort"), ~ !is.na(.x))) |> 
  # filter(arm_n != mort_update_arm_n) |> 
  # select(refid, arm_n, mort_update_arm_n)
  mutate(
    # arm_n use mort_update_arm_n if different
    arm_n = ifelse(!is.na(mort_update_arm_n), mort_update_arm_n, arm_n)
  ) |> 
  select(refid, refid_c, arm_id, arm, year, study, study_l, design_f_lab, arm_n, matches("_n|per") & starts_with("mort"), -mort_update_arm_n) |> 
  pivot_longer(
    cols = starts_with("mort"),
    names_to = "estimand",
    values_to = "estimate",
    values_drop_na = TRUE
  ) |>
  mutate(
    mort_period = str_remove(estimand, "_.*"),
    estimand = str_replace(estimand, ".*_(.*)$", "\\1")
  ) |>
  pivot_wider(
    names_from = estimand,
    values_from = estimate
  ) |>
  mutate(
    mort_period = case_when(
      str_detect(mort_period, "hosp") ~ "Hospital",
      str_detect(mort_period, "mort30") ~ "30-day",
      str_detect(mort_period, "mort90") ~ "90-day",
      str_detect(mort_period, "mort1") ~ "1-year"
    ), 
    per = per/100
  ) |>
  rename(mort_n = n, mort_per_rep = per) |>
  # for Park 2020 and Dai 2021 reported both in-hospital and 30-day
  mutate(
    refid_c = ifelse(study %in% c("Park 2020", "Dai 2021") & mort_period == "30-day", paste0(refid_c, "-30"), refid_c)
  ) |> 
  arrange(refid_c, arm_id) |>
  mutate(
    ref_arm_n = arm_n,
    ref_mort_n = mort_n
  ) |>
  group_by(refid_c) |>
  mutate(
    ref_arm_n = ifelse(row_number() > 1, NA, ref_arm_n),
    ref_mort_n = ifelse(row_number() > 1, NA, ref_mort_n)
  ) |>
  fill(ref_arm_n, ref_mort_n) |>
  mutate(
    ref_arm_n = ifelse(row_number() == 1, NA, ref_arm_n),
    ref_mort_n = ifelse(row_number() == 1, NA, ref_mort_n)
  ) |>
  ungroup() |> 
  left_join(study_char_dat |> select(refid, surgs_single_f), by = "refid") |>
  left_join(table_age_mn_med, by = c("refid", "arm_id")) |>
  left_join(asa_combine |> select(refid, arm_id, asa_ps_incl), by = c("refid", "arm_id")) |> 
  mutate(mort_percent = mort_n/arm_n,
         mort_period = factor(mort_period, levels = c("Hospital", "30-day", "90-day", "1-year"))) |>
  select(refid, refid_c, arm_id, year, study, study_l, arm_n, arm, asa_ps_incl, age_table, design_f_lab, mort_n, mort_percent, ref_mort_n, ref_arm_n, mort_period, mort_per_rep, surgs_single_f)


```

<font size = 4> `r table_ref()` Reported in-hospital, 30-day, and 1-year mortality from randomized clinical trials.</font>

```{r mortality_rct_gt}
#| eval: true
mortality_dat |>
  arrange(mort_period, surgs_single_f, year, study, arm_id) |>
  filter(str_detect(design_f_lab, "Rand")) |> 
  group_by(mort_period, study_l) |>
  mutate(
    surgs_single_f = as.character(surgs_single_f),
    study_l = ifelse(row_number() == 1, study_l, NA),
    study = ifelse(row_number() == 1, study, NA),
    across(c(surgs_single_f, asa_ps_incl,), ~ ifelse(row_number() > 1, NA, .x)),
    # bar = bar_prop(50, color_1),
    bar = case_when(
      str_detect(arm, "TIVA") ~ bar_prop(mort_percent * 100, "#A93226"),
      .default = bar_prop(mort_percent * 100, "#969696")
    ),
  ) |>
  ungroup() |>
  mutate(
    # de Jonghe 2014 reported in hospital and 90-day
    # study_l = ifelse(refid == 16552 & arm_id == 1, "[de Jonghe 2014](evidence_tables.html#16552)", study_l),
    # surgs_single_f = ifelse(refid == 16552 & arm_id == 1, "Ortho", surgs_single_f),
    rd_ci = ifelse(!is.na(ref_mort_n), rd_per_ci_fun(mort_n, arm_n, ref_mort_n, ref_arm_n, digits = 1), "—"),
    mort_n_percent = n_per_fun(mort_n, arm_n, 1)
  ) |> 
  relocate(surgs_single_f, .before = asa_ps_incl) |> 
  relocate(mort_n_percent, .before = bar) |> 
  select(-mort_n) |> 
  arrange(year, refid_c, arm_id) |> 
  group_by(mort_period) |> 
  gt(id = "one") |> 
  cols_hide(c(refid, refid_c, arm_id, year, study, design_f_lab, mort_percent, ref_mort_n, ref_arm_n, mort_per_rep)) |>
  # row_group_order(groups = c("Hospital", "30-day", "90-day")) |> 
  cols_label(
    study_l = "Study",
    arm_n = "N  ",
    arm = "Arm",
    surgs_single_f = "Surgery",
    age_table = "Age",
    asa_ps_incl = "PS",
    mort_n_percent = "N (%)",
    bar = md("0 - 100%"),
    rd_ci = "RD (95% CI)"
  ) |> 
  fmt_markdown(columns = c(study_l, bar, age_table)) |>
  tab_spanner(label = "Mortality", columns = c(mort_n_percent, bar)) |> 
  tab_spanner(label = "ASA", columns = c(asa_ps_incl)) |> 
  row_group_order(groups = c("Hospital", "30-day", "1-year")) |> 
  gt_theme_mg() |> 
  tab_style(style = cell_text(align = "left"),   locations = cells_column_labels(columns = c(study, arm, surgs_single_f))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(age_table, asa_ps_incl, rd_ci))) |>
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(study, arm, surgs_single_f, bar))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(rd_ci))) |>
  tab_style(style = cell_text(align = "right"),  locations = cells_column_labels(columns = c(arm_n, mort_n_percent))) |>
  tab_style(style = cell_text(align = "right"),  locations = cells_body(columns = c(mort_n_percent))) |>
  tab_style(style = cell_text(align = "center",  font = "IBM Plex Mono"), locations = cells_body(columns = c(asa_ps_incl))) |> 
  tab_style(style = list(cell_text(color = "#A93226")), locations = cells_body(columns = c(arm_n, arm, age_table, mort_n_percent), rows = str_detect(arm, "TIVA"))) |> 
  sub_missing(columns = everything(), rows = everything(), missing_text = "") |> 
  cols_width(
    study_l ~ px(140),
    arm_n ~ px(65),
    arm ~ px(70),
    surgs_single_f ~ px(95),
    age_table ~ px(100),
    asa_ps_incl ~ px(60),
    mort_n_percent ~ px(80),
    bar ~ px(100),
    rd_ci ~ px(145)
  ) |> 
  # opt_css(css = "#one .gt_column_spanner {border-bottom-style: hidden;}") |>
  tab_footnote("ASA PS: American Society of Anesthesiologists Physical Status; RD: risk difference; GI: gastrointestinal; Abd: abdominal (includes hepatic); Various: more that one procedure category.") |> 
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(age_table)))  
  # tab_footnote("Different lengths of follow-up from the same trial.", locations = cells_body(columns = study_l, rows = study %in% c("Su 2016", "Zhang 2019b"))) 

```

<font size = 4> `r table_ref()` Reported in-hospital and 30-day mortality from nonrandomized designs (all retrospective cohort studies).</font>

```{r mortality_nrsi_gt}
#| eval: true
mortality_dat |>
  arrange(mort_period, surgs_single_f, year, study, arm_id) |>
  filter(!str_detect(design_f_lab, "Rand")) |> 
  group_by(mort_period, study_l) |>
  mutate(
    surgs_single_f = as.character(surgs_single_f),
    study_l = ifelse(row_number() == 1, study_l, NA),
    study = ifelse(row_number() == 1, study, NA),
    across(c(surgs_single_f, asa_ps_incl,), ~ ifelse(row_number() > 1, NA, .x)),
    # bar = bar_prop(50, color_1),
    bar = case_when(
      str_detect(arm, "TIVA") ~ bar_prop(mort_percent * 100, "#A93226"),
      .default = bar_prop(mort_percent * 100, "#969696")
    ),
  ) |>
  ungroup() |>
  mutate(
    # de Jonghe 2014 reported in hospital and 90-day
    # study_l = ifelse(refid == 16552 & arm_id == 1, "[de Jonghe 2014](evidence_tables.html#16552)", study_l),
    # surgs_single_f = ifelse(refid == 16552 & arm_id == 1, "Ortho", surgs_single_f),
    rd_ci = ifelse(!is.na(ref_mort_n), rd_per_ci_fun(mort_n, arm_n, ref_mort_n, ref_arm_n, digits = 1), "—"),
    mort_n_percent = n_per_fun(mort_n, arm_n, 1)
  ) |> 
  relocate(surgs_single_f, .before = asa_ps_incl) |> 
  relocate(mort_n_percent, .before = bar) |> 
  select(-mort_n) |> 
  arrange(year, refid_c, arm_id) |> 
  group_by(mort_period) |> 
  gt(id = "one") |> 
  cols_hide(c(refid, refid_c, arm_id, year, study, design_f_lab, mort_percent, ref_mort_n, ref_arm_n, mort_per_rep)) |>
  # row_group_order(groups = c("Hospital", "30-day", "90-day")) |> 
  cols_label(
    study_l = "Study",
    arm_n = "N    ",
    arm = "Arm",
    surgs_single_f = "Surgery",
    age_table = "Age",
    asa_ps_incl = "PS",
    mort_n_percent = "N (%)",
    bar = md("0 - 100%"),
    rd_ci = "RD (95% CI)"
  ) |> 
  fmt_markdown(columns = c(study_l, bar, age_table)) |>
  tab_spanner(label = "Mortality", columns = c(mort_n_percent, bar)) |> 
  tab_spanner(label = "ASA", columns = c(asa_ps_incl)) |> 
  fmt_integer(use_seps = TRUE, sep_mark = ",") |>
  gt_theme_mg() |> 
  tab_style(style = cell_text(align = "left"),   locations = cells_column_labels(columns = c(study, arm, surgs_single_f))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(age_table, asa_ps_incl, rd_ci))) |>
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(study, arm, surgs_single_f, bar))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(rd_ci))) |>
  tab_style(style = cell_text(align = "right"),  locations = cells_column_labels(columns = c(arm_n, mort_n_percent))) |>
  tab_style(style = cell_text(align = "right"),  locations = cells_body(columns = c(mort_n_percent))) |>
  tab_style(style = cell_text(align = "center",  font = "IBM Plex Mono"), locations = cells_body(columns = c(asa_ps_incl))) |> 
  tab_style(style = list(cell_text(color = "#A93226")), locations = cells_body(columns = c(arm_n, arm, age_table, mort_n_percent), rows = str_detect(arm, "TIVA"))) |> 
  sub_missing(columns = everything(), rows = everything(), missing_text = "") |> 
  cols_width(
    study_l ~ px(140),
    arm_n ~ px(65),
    arm ~ px(70),
    surgs_single_f ~ px(95),
    age_table ~ px(100),
    asa_ps_incl ~ px(60),
    mort_n_percent ~ px(80),
    bar ~ px(100),
    rd_ci ~ px(145)
  ) |> 
  # opt_css(css = "#one .gt_column_spanner {border-bottom-style: hidden;}") |>
  tab_footnote("ASA PS: American Society of Anesthesiologists Physical Status; RD: risk difference; GI: gastrointestinal; Abd: abdominal (includes hepatic); Various: more that one procedure category.") |> 
  tab_footnote(md("Mean <u>Med</u> (SD) [Range] {IQR}."), locations = cells_column_labels(columns = c(age_table)))  
  # tab_footnote("Different lengths of follow-up from the same trial.", locations = cells_body(columns = study_l, rows = study %in% c("Su 2016", "Zhang 2019b"))) 

```

```{r mortality_hosp_30d_meta}
#| eval: true
mortality_rct_meta_dat <- mortality_dat |>
  filter(str_detect(design_f_lab, "Rand")) |> 
  filter(mort_period %in% c("Hospital", "30-day")) |>
  # exclude Dai 2021 hospital 30-day; retain 30-day
  filter(!(study == "Dai 2021" & mort_period == "Hospital")) |> 
  select(refid, study, arm, mort_n, arm_n, mort_period)

mortality_nrsi_meta_dat <- mortality_dat |>
  filter(!str_detect(design_f_lab, "Rand")) |> 
  filter(mort_period %in% c("Hospital", "30-day")) |>
  # exclude hospital retain 30-day
  filter(!(study %in% c("Jakobsen 2007", "Park 2020") & mort_period == "Hospital")) |> 
  select(refid, study, arm, mort_n, arm_n, mort_period)

pairwise_rct_mort_dat <- pairwise(
  treat = arm,
  event = mort_n,
  n = arm_n,
  studlab = study,
  allstudies = TRUE,
  data = mortality_rct_meta_dat,
  sm = "RR",
  keep.all.comparisons = TRUE
)

pairwise_nrsi_mort_dat <- pairwise(
  treat = arm,
  event = mort_n,
  n = arm_n,
  studlab = study,
  allstudies = TRUE,
  data = mortality_nrsi_meta_dat,
  sm = "RR",
  keep.all.comparisons = TRUE
)

```

### *Pooled*

<font size = 4> `r figure_ref()` Risk ratio for hospital or 30-day mortality (TIVA versus inhaled; randomized clinical trials). </font>

```{r mort_rct_meta, fig.dim = c(14, 4), fig.align = "center"}
# ```{r nma_dat, out.width = 50%, out.height = 100%}
mort_meta_dat <- pairwise_rct_mort_dat |> 
  mutate(year = str_extract(study, "\\d{4}")) |> 
  left_join(rob2_meta_dat, by = "refid") |> 
  left_join(surgs |> select(refid, surgs_single), by = "refid") |> 
  select(study, year, event2, n2, event1, n1, surgs_single, D1:Overall, mort_period, refid)

# total_meta(mort_meta_dat)
# refid_meta_fun(mort_meta_dat)

mort_rct_meta <- metabin(event2, n2, event1, n1,
  data = mort_meta_dat,
  studlab = study,
  # cluster = refid,
  sm = "RR",
  method = "MH",
  method.tau = "PM",
  hakn = TRUE,
  prediction = FALSE,
  allstudies = TRUE,
)

# summary(plac_meta)
forest(mort_rct_meta,
  allstudies = TRUE,
  # random = FALSE,
  label.e = "TIVA     ",
  label.c = "Inhaled     ",
  rightcols = c("effect", "ci", "surgs_single", "D1", "D2", "D3", "D4", "D5", "Overall"),
  rightlabs = c("RR", "(95% CI)", "Procedure", "D1", "D2", "D3", "D4", "D5", "All"),
  just.addcols.right = "right",
  digits.TE = 3,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = TRUE,
  fs.xlab = 11,
  pooled.events = TRUE,
  pscale = 1000,
  digits = 2, 
  print.pval.Q = FALSE,
  xlim = c(0.1, 20),
  xlab = "Favors: TIVA                       Inhaled       ",
  addrows.below.overall = 4
)

```
<foot_mg> RR: risk ratio; D1: bias arising from the randomization process; D2: bias due to deviations from intended interventions; D3: bias due to missing outcome data; D4: bias in measurement of the outcome; D5: bias in selection of the reported result: All: overall risk of bias.<br/> Risk of bias ratings: low +, some concerns ?, high -- .</foot_mg> 

<font size = 4> `r figure_ref()` Risk ratio for hospital or 30-day mortality (TIVA versus inhaled; nonrandomized designs). </font>

```{r mort_nrsi_meta, fig.dim = c(14, 4), fig.align = "center"}
mort_meta_dat <- pairwise_nrsi_mort_dat |> 
  mutate(year = str_extract(study, "\\d{4}")) |> 
  left_join(robinsi_meta_dat, by = "refid") |> 
  left_join(surgs |> select(refid, surgs_single), by = "refid") |> 
  select(study, year, event2, n2, event1, n1, surgs_single, D1:Overall, mort_period, refid)

# total_meta(mort_meta_dat)
# refid_meta_fun(mort_meta_dat)

mort_rct_meta <- metabin(event2, n2, event1, n1,
  data = mort_meta_dat,
  studlab = study,
  # cluster = refid,
  sm = "RR",
  method = "MH",
  method.tau = "PM",
  hakn = TRUE,
  prediction = FALSE,
  allstudies = TRUE,
)

# summary(plac_meta)
forest(mort_rct_meta,
  allstudies = TRUE,
  # random = FALSE,
  label.e = "TIVA     ",
  label.c = "Inhaled     ",
  rightcols = c("effect", "ci", "surgs_single", "D1", "D2", "D3", "D4", "D5", "D6", "D7", "Overall"),
  rightlabs = c("RR", "(95% CI)  ", "Procedure", "D1", "D2", "D3", "D4", "D5", "D6", "D7", "All"),
  just.addcols.right = "right",
  digits.TE = 3,
  digits.tau2 = 1,
  overall.hetstat = TRUE,
  print.I2.ci = TRUE,
  prediction = TRUE,
  fs.xlab = 11,
  pooled.events = TRUE,
  pscale = 1000,
  digits = 2, 
  print.pval.Q = FALSE,
  xlim = c(0.1, 10),
  xlab = "Favors: TIVA                                     Inhaled       ",
  addrows.below.overall = 4
)
```
<foot_mg> D1: Bias due to confounding; D2: Bias in selection of participants into the study; D3: Bias in classification of interventions; D4: Bias due to deviations from intended interventions; D5: Bias due to missing data; D6: Bias in measurement of outcomes; D7: Bias in selection of reported results; All: overall risk of bias.<br/> Risk of bias ratings: low ++, moderate +, serious -, critical - - ; NI: no information; NA: not applicable.<br/>
Note for Yoshimura 2022 naïve risk ratio, but identical to odds ratio reported respecting propensity matching.</foot_mg> 



## **Risk of Bias**

### Randomized

<font size = 4> `r figure_ref()` Summary risk of bias assessment for randomized clinical trials. </font>

```{r rob2_summary_overall, fig.height = 3, out.width = "60%"}
rob_temp_dat <- rob2_dat |>
  filter(!is.na(Study) & refid %in% kq4_refid) |> 
  select(-refid)

rob_summary(rob_temp_dat, tool = "ROB2", colour = "colourblind", weighted = FALSE)
```

<font size = 4> `r figure_ref()` Risk of bias assessments for randomized clinical trials. </font>

```{r rob_overall_study, out.width = "55%", fig.height = 7}
rob_traffic_light(rob_temp_dat, psize = 4, tool = "ROB2", colour = "colourblind")
```

### Nonrandomized

<font size = 4> `r figure_ref()` Summary risk of bias assessment for nonrandomized studies. </font>

```{r nrsi_summary_overall, fig.height = 3, out.width = "60%"}
robinsi_temp_dat <- robinsi_dat |>
  filter(!is.na(Study) & refid %in% kq4_refid) |> 
  select(-refid)

rob_summary(robinsi_temp_dat, tool = "ROBINS-I", colour = "colourblind", weighted = FALSE)
```

<font size = 4> `r figure_ref()` Risk of bias assessments for nonrandomized studies. </font>

```{r nrsi_overall_study, out.width = "55%", fig.height = 4.5}
rob_traffic_light(robinsi_temp_dat, psize = 4, tool = "ROBINS-I", colour = "colourblind")
```

## **References** {#references}

```{r}
#| eval: false
dichot_dat |> 
  select(matches("satis")) |> 
  filter(if_any(matches("satis"), ~ !is.na(.x)))

temp <- likert_dat |> 
  select(cog_func_cdr:cog_func_other) |> 
  filter(if_any(cog_func_cdr:cog_func_other, ~ !is.na(.x)))

temp <- likert_dat |> 
  select(digit_time1:drstotal_pval_betw) |> 
  filter(if_any(digit_time1:drstotal_pval_betw, ~ !is.na(.x)))

writexl::write_xlsx(temp, "/Users/mgrant/Desktop/temp.xlsx")






cog_func_cfq
cog_func_dst
cog_func_mmse
cog_func_moca
cog_func_trail
cog_func_other

```




