---
title: "Outcome Rankings by Key Question"
editor: source
toc-title: "Outcome Rankings by Key Question"
toc-location: "left"
toc_float: 
  collapsed: true
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
---


```{r}
#| message: false
#| echo: false
source("code/readfiles_geri_2022-11-16.R")
```

Rankings of the 5 most important outcomes for each question (10 respondents).

## KQ 1 Expanded Preoperative Evaluation
<font size = 4> `r table_ref()`  Among older patients anticipating surgery and anesthesia, does expanded preoperative evaluation (e.g., for frailty, cognitive impairment, functional status, or psychosocial issues) lead to improved postoperative outcomes? </font>

```{r}
#| include: true
outcome_dat <- rankings("KQ1")
outcome_tab(outcome_dat)
```

## KQ 2 Prehabilitation 
<font size = 4> `r table_ref()`  Among geriatric patients anticipating surgery and anesthesia, do interventions targeted at improving physical function, cognition, and nutritional status before surgery (“prehabilitation”) improve postoperative outcomes? </font>


```{r}
#| include: true
outcome_dat <- rankings("KQ2")
outcome_tab(outcome_dat)
```

## KQ 3 Regional vs. General Anesthesia

<font size = 4> `r table_ref()` Among older patients undergoing surgery, does regional anesthesia as the primary anesthetic technique improve postoperative outcomes compared with general anesthesia? </font>

```{r}
#| include: true
outcome_dat <- rankings("KQ3")
outcome_tab(outcome_dat)
```

## KQ 4 Intravenous vs. Inhaled Anesthesia

<font size = 4> `r table_ref()` Among older patients undergoing surgery with general anesthesia, does the use of intravenous agents for maintenance of anesthesia improve postoperative outcomes compared with inhaled agents? </font>

```{r}
#| include: true
outcome_dat <- rankings("KQ4")
outcome_tab(outcome_dat)
```

## KQ 5 Potentially Inappropriate Medications

<font size = 4> `r table_ref()` Among older patients undergoing surgery and anesthesia, do commonly used potentially inappropriate medications administered during the perioperative period increase the risk of postoperative delirium or other adverse outcomes? </font>

```{r}
#| include: true
outcome_dat <- rankings("KQ5")
outcome_tab(outcome_dat)
```

## KQ 6 Delirium Prophylaxis

<font size = 4> `r table_ref()` Among older patients undergoing surgery and anesthesia, do dexmedetomidine, ketamine, ramelteon, or melatonin administered during the perioperative period decrease the risk of postoperative delirium or other adverse cognitive outcomes? </font>

```{r}
#| include: true
outcome_dat <- rankings("KQ6")
outcome_tab(outcome_dat)
```

## KQ 7 Lower Limb Regional Anesthesia
<font size = 4> `r table_ref()` Among older patients undergoing surgery, do postoperative lower limb regional anesthetic techniques, such as continuous epidural anesthesia improve postoperative outcomes? </font>

```{r}
#| include: true
outcome_dat <- rankings("KQ7")
outcome_tab(outcome_dat)
```

## KQ 8 Delirium Screening

<font size = 4> `r table_ref()` Does screening older patients for postoperative delirium in the post anesthesia care unit improve postoperative outcomes? </font>

```{r}
outcome_dat <- rankings("KQ8")
outcome_tab(outcome_dat)
```
