---
title: "Strength of Evidence"
editor: source
toc-title: "**Strength of Evidence**"
toc-location: "left"
toc-depth: 4
toc_float: 
  collapsed: false
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "

---

## Updates
::: {.callout-important collapse="true"}
### `r lubridate::today()`

| Date               | Modification|
|:------------------------|:-----------------------------------------------|
| 2024-01-02 | Updated regional versus general for consistent language, removed *I* <sup>2</sup> (can be found in forest plots), and added prediction intervals where relevant.|
| 2024-01-06 | Regional now only neuraxial. Updated summaries to be consistent with revised analyses.|
| 2024-04-10 | Updated expanded preoperative evaluation. |    

:::


```{r preliminaries}
#| include: false
## preliminaries -------------------------------------- (2022-11-16 11:49) @----
library(conflicted)
library(janitor)
library(htmltools)
library(gt, quietly = TRUE)
library(gtsummary)
library(gtExtras)
library(glue)
library(tidyverse)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::lag)
knitr::opts_chunk$set(echo = FALSE)
source("code/functions_2023-04-26.R")

soe_footnote <- function(x) {
  x |>
    tab_footnote("Pts: patients; RCT: randomized clinical trial; NRSI: non-randomized studies of interventions (inlcudes non-randomized trials, before-after/time series, and observational); GRADE: Grades of Recommendation, Assessment, Development, and Evaluation; ACCF/AHA: American College of Cardiology Foundation/American Heart Association; RR: risk ratio; OR: odds ratio; MD: mean difference; RD: risk difference; PI: prediction interval.") |>
    tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |>
    tab_footnote("A: high-quality evidence from more than 1 RCT; B-R: moderate-quality evidence from more than 1 RCT; B-NR: moderate-quality evidence from more than one observational study; C-LD: randomized or non-randomized observational or registry studies with limited data; C-EO: consensus of expert opinion.", locations = cells_column_labels(columns = acc)) |>
    tab_footnote("Limited +; Important ++; Critical +++.", locations = cells_column_labels(columns = out_import)) |> 
    tab_footnote("Complications were judged critical without specification to type except stroke.", locations = cells_body(columns = out_import, rows = outcome %in% c("Myocardial infarction", "Stroke", "Renal complications", "Pulmonary complications", "Pneumonia", "Pulmonary embolism", "Pulmonary congestion", "Acute kidney injury", "Respiratory failure", "Cardiac Arrest", "Bradycardia", "Hypotension")))
}

domain_footnote <- function(x) {
  x |>
    tab_footnote("If not specified in footnotes, all references are to 95% confidence and prediction intervals.") |>
    tab_footnote("RCT: randomized clinical trial; NRSI: non-randomized studies of interventions (inlcudes non-randomized trials, before-after/time series, and observational).") |>
    tab_footnote(md(domain_footnotes))
}



```

## **Expanded Preoperative Evaluation**

```{r soe_kq1_data}
#| include: false
col_types_soe <- c("numeric", rep("text", 5), "numeric", rep("text", 16))
soe_kq1_dat <- readxl::read_xlsx("data/soe_2023-05-22_local.xlsx", range = "A1:W24", sheet = "soe_kq1", col_types = col_types_soe) |>
  clean_names() |>
  filter(outcome != "Atelectasis") |> 
  filter(!n %in% c(1.011, 1.012)) |>
  mutate(
    n_s = case_when(
      !is.na(n_studies) & !is.na(n_pts) ~ paste0(n_studies, " <br/>(", format(n_pts, big.mark = ","), ")"),
      !is.na(n_studies) & is.na(n_pts) ~ n_studies, 
      is.na(n_studies) & is.na(n_pts) ~ "—"), 
    n = paste0(n, outcome),
    n_s = replace_na(n_s, "—"),
    out_import = firstup(out_import),
    out_import = case_when(
      out_import == "Limited" ~ "+",
      out_import == "Important" ~ "++",
      out_import == "Critical" ~ "+++"
    ),
    compare_group = case_when(
      comparison == "reg_gen" ~ "Regional vs. General Anesthesia",
    )
  )

soe_summary <- soe_kq1_dat |>
  select(n, comparison, outcome, n_s, design, grade, acc, out_import, summary, result_links, compare_group) |>
  mutate(
    grade = case_when(
      grade == "very low" ~ vlow,
      grade == "low" ~ low,
      grade == "moderate" ~ mod, 
      grade == "high" ~ high,
      .default = grade
    )
  ) 

domain_summary <- soe_kq1_dat |> 
  select(n, comparison, outcome, design, n_studies, n_pts, rob, consist, direct, prec, other, summary, ends_with("foot")) |> 
  # sentence case and add period if missing
  mutate(design = str_to_sentence(design),
         consist_foot = ifelse(!grepl("\\.$", consist_foot) & !is.na(consist_foot), paste0(consist_foot, "."), consist_foot),
         direct_foot  = ifelse(!grepl("\\.$", direct_foot ) & !is.na(direct_foot ), paste0(direct_foot , "."), direct_foot ),
         prec_foot    = ifelse(!grepl("\\.$", prec_foot   ) & !is.na(prec_foot   ), paste0(prec_foot   , "."), prec_foot   ),
         rob_foot     = ifelse(!grepl("\\.$", rob_foot    ) & !is.na(rob_foot    ), paste0(rob_foot    , "."), rob_foot    ),
         other_foot   = ifelse(!grepl("\\.$", other_foot  ) & !is.na(other_foot  ), paste0(other_foot  , "."), other_foot  ),
         across(ends_with("foot"), ~ firstup(.x))
         ) 

```

<caption_mg> `r table_ref()` Strength of evidence summaries — expanded versus standard preoperative evaluation. </caption_mg>

```{r kq1_soe_gt}
#| echo: false

soe_summary |>
  mutate(across(grade:result_links, ~ replace_na(., "")),
    design = ifelse(design %in% c("Before/after", "Non-randomized"), "NRSI", design),
    outcome = ifelse(outcome == lag(outcome) & row_number() > 1, "", outcome)
  ) |>
  gt(id = "one") |>
  cols_hide(c(n, comparison, compare_group)) |>
  cols_label(
    outcome = "Outcome",
    design = "Study Design",
    n_s = "Studies (Pts)",
    grade = "GRADE",
    acc = "ACCF AHA",
    out_import = "Importance",
    summary = "Summary",
    result_links = "Result Detail"
  ) |>
  fmt_markdown(columns = c(outcome, n_s, grade, summary, result_links)) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(outcome, summary, result_links))) |>
  tab_style(style = "vertical-align:top", locations = cells_body(columns = everything())) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(200),
    design ~ px(80),
    n_s ~ px(85),
    grade ~ px(60),
    acc ~ px(60),
    out_import ~ px(90),
    summary ~ px(325),
    result_links ~ px(125)
  ) |>
  opt_css(
    css = "
    #one p {
    line-height: 1.4;
    }
  "
  ) |>
  opt_footnote_marks(marks = "numbers") |>
  sub_values(values = c("NA <br/>(NA)"), replacement = "—") |>
  soe_footnote()

```

### GRADE Domains

<font size = 4> `r table_ref()` GRADE domains for strength of evidence ratings — expanded versus standard preoperative evaluation. </font>

```{r kq1_domain}
#| warning: true
#| include: true
#| echo: false
kq1_domain_summary <- domain_summary |>
  select(-summary) |>
  mutate(
    design = str_replace(design, "Rct", "RCT"),
  )
         
foot_unique <- kq1_domain_summary |> 
  select(ends_with("foot")) 

foot_unique <- c(t(foot_unique)) |> 
  unlist(use.names = FALSE) |> 
  discard(is.na) 

foot_unique <- unique(foot_unique)

numbers <- c(1:100)
kq1_domain <- kq1_domain_summary |> 
  mutate(rob_let     = numbers[match(rob_foot, foot_unique)],
         consist_let = numbers[match(consist_foot, foot_unique)],
         direct_let  = numbers[match(direct_foot, foot_unique)],
         prec_let    = numbers[match(prec_foot, foot_unique)],
         other_let   = numbers[match(other_foot, foot_unique)],
         )

for (i in 1:nrow(kq1_domain)) {
  for (j in 7:11) {
    kq1_domain[i, j] <- ifelse(!is.na(kq1_domain[i, j + 10]), paste0(kq1_domain[i, j], "<sup>", kq1_domain[i, j + 10], "</sup>"), kq1_domain[i, j])
  }
}

# create domain footnotes
domain_footnotes <- as_tibble(foot_unique) |> 
  mutate(n = row_number(),
         value = paste0("<sup>", n, " </sup>", value)) |> 
  pull(value)

domain_footnotes <- glue_collapse(domain_footnotes, sep = "<br>")

kq1_domain |> 
  filter(!design == "No studies") |> 
  mutate(n_s = paste0(n_studies, "<br>(", n_pts, ")"),
         design = ifelse(design %in% c("Before/after", "Non-randomized"), "NRSI", design),
         # outcome = str_replace(outcome, "Cognitive dysfunction", "Cognitive dysfunction<br/>"),
         outcome = ifelse(outcome == lag(outcome) & row_number() > 1, "", outcome)) |> 
  mutate(space = "") |> 
  left_join(soe_kq1_dat |> select(compare_group, n), by = "n") |>
  # group_by(compare_group) |> 
  select(outcome, design, space, n_s, rob, consist, direct, prec, other) |> 
  gt(id = "one") |> 
  cols_hide(n_s) |> 
  cols_label(
    outcome = "Outcome",
    design = "Design",
    space = "",
    # n_s = "Studies (Pts)",
    rob = "Bias",  
    consist = "Inconsistency",
    direct = "Indirectness",
    prec = "Imprecision", 
    other = "Other"
  ) |>
  fmt_markdown(columns = c(n_s:other)) |> 
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(design, rob:other))) |>
  # tab_style(style = "padding-right:80px",       locations = cells_column_labels(columns = c(design))) |> 
  # tab_style(style = "padding-left:10px",        locations = cells_body(columns = c(design))) |>
  # tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(design))) |> 
  # tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(design))) |>
  tab_spanner(label = "GRADE Domains", columns = c(rob:other)) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(200),
    # n_s ~ px(85),
    design ~ px(100),
    space ~ px(20),
    rob ~ px(110),
    consist ~ px(110),
    direct ~ px(110),
    prec ~ px(110),
    other ~ px(110)
  ) |> 
  domain_footnote() |> 
  tab_footnote(md(domain_footnotes))

```

## **Neuraxial versus General Anesthesia**

```{r soe_kq3_data}
#| include: false
col_types_soe <- c("numeric", rep("text", 5), "numeric", rep("text", 16))
soe_kq3_dat <- readxl::read_xlsx("data/soe_2023-05-22_local.xlsx", range = "A1:W20", sheet = "soe_kq3", col_types = col_types_soe) |>
  clean_names() |>
  mutate(
    n_s = paste0(n_studies, " <br/>(", format(n_pts, big.mark = ","), ")"),
    n = paste0(n, outcome),
    n_s = str_remove_all(n_s, "\\s"),
    n_s = ifelse(str_detect(n_s, "NA"), "—", n_s),
    # outcome = tools::toTitleCase(outcome) |>
    # outcome = str_to_sentence(outcome),
    out_import = case_when(
      out_import == "Limited" ~ "+",
      out_import == "Important" ~ "++",
      out_import == "Critical" ~ "+++"
    ),
    compare_group = case_when(
      comparison == "reg_gen" ~ "Regional vs. General Anesthesia",
    )
  )

# soe_summary <- soe_kq3_dat |>
#   select(n, comparison, outcome, n_s, design, grade, acc, out_import, summary, result_links, compare_group) |>
#   mutate(
#     grade = case_when(
#       grade == "very low" ~ vlow,
#       grade == "low" ~ low,
#       grade == "moderate" ~ mod, 
#       grade == "high" ~ high,
#       .default = grade
#     )
#   ) 

soe_summary <- soe_kq3_dat |>
  select(n, comparison, outcome, n_s, design, grade, acc, out_import, summary, result_links, compare_group) |>
  mutate(
    high = paste0("[", vlow, "]", "(soe_gt.html#reg-gen-grade)"), 
    mod = paste0("[", mod, "]",   "(soe_gt.html#reg-gen-grade)"),
    low = paste0("[", low, "]",   "(soe_gt.html#reg-gen-grade)"),
    vlow = paste0("[", vlow, "]", "(soe_gt.html#reg-gen-grade)"),
    low_very = paste0("[", low_very, "]", "(soe_gt.html#reg-grade)"),
    grade = case_when(
      grade == "very low" ~ vlow,
      grade == "low" ~ low,
      grade == "moderate" ~ mod,
      grade == "high" ~ high,
      .default = grade
    )
  ) |> 
  select(-c(vlow, low, mod, high, low_very)) 

domain_summary <- soe_kq3_dat |> 
  select(n, comparison, outcome, design, n_studies, n_pts, rob, consist, direct, prec, other, summary, ends_with("foot")) |> 
  # sentence case and add period if missing
  mutate(design = str_to_sentence(design),
         consist_foot = ifelse(!grepl("\\.$", consist_foot) & !is.na(consist_foot), paste0(consist_foot, "."), consist_foot),
         direct_foot  = ifelse(!grepl("\\.$", direct_foot ) & !is.na(direct_foot ), paste0(direct_foot , "."), direct_foot ),
         prec_foot    = ifelse(!grepl("\\.$", prec_foot   ) & !is.na(prec_foot   ), paste0(prec_foot   , "."), prec_foot   ),
         rob_foot     = ifelse(!grepl("\\.$", rob_foot    ) & !is.na(rob_foot    ), paste0(rob_foot    , "."), rob_foot    ),
         other_foot   = ifelse(!grepl("\\.$", other_foot  ) & !is.na(other_foot  ), paste0(other_foot  , "."), other_foot  ),
         across(ends_with("foot"), ~ firstup(.x))
         ) 

```

<font size = 4> `r table_ref()` Strength of evidence summaries — neuraxial versus general anesthesia. </font>

```{r kq3_soe_gt}
#| include: true
#| echo: false
soe_summary |>
  mutate(across(grade:result_links, ~ replace_na(., "")),
         design = ifelse(design %in% c("Before/after", "Non-randomized"), "NRSI", design),
         # outcome = str_replace(outcome, "Cognitive dysfunction", "Cognitive dysfunction<br/>"),
         outcome = ifelse(outcome == lag(outcome) & row_number() > 1, "", outcome)
         ) |> 
  # group_by(compare_group) |> 
  gt(id = "one") |>
  cols_hide(c(n, comparison, compare_group)) |>
  cols_label(
    outcome = "Outcome",
    design = "Study Design",
    n_s = "Studies (Pts)",
    grade = "GRADE",
    acc = "ACCF AHA",
    out_import = "Importance",
    summary = "Summary",
    result_links = "Result Detail"
  ) |>
  # tab_row_group(
  #   label = "powerful",
  #   rows = outcome == "Delirium incidence"
  # ) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(220),
    design ~ px(80),
    n_s ~ px(85),
    grade ~ px(50),
    acc ~ px(60),
    out_import ~ px(90),
    summary ~ px(325),
    result_links ~ px(120)
  ) |>
    opt_css(
    css = "
    #one p {
    line-height: 1.4;
    }
  "
  ) |> 
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(outcome, summary, result_links))) |>
  text_replace("8<br\\/>\\(7,419\\)", "8 RR<br/>(7,419) <br/><br/> 10 RD<br/>(7,577)", locations = cells_body(columns = n_s)) |> 
  fmt_markdown(columns = c(outcome, n_s, grade, summary, result_links)) |>
  opt_footnote_marks(marks = "numbers") |>
  sub_values(values = c("NA <br/>(NA)"), replacement = "—") |>
  soe_footnote() 

```

<a id="reg-gen-grade"></a> 

### GRADE Domains

<font size = 4> `r table_ref()` GRADE domains for strength of evidence ratings — neuraxial versus general anesthesia. </font>

```{r kq3_domain, eval = TRUE}
#| warning: true
#| include: true
#| echo: false
kq3_domain_summary <- domain_summary |>
  select(-summary) |>
  mutate(
    design = str_replace(design, "Rct", "RCT"),
  )
         
foot_unique <- kq3_domain_summary |> 
  select(ends_with("foot")) 

foot_unique <- c(t(foot_unique)) |> 
  unlist(use.names = FALSE) |> 
  discard(is.na) 

foot_unique <- unique(foot_unique)

numbers <- c(1:100)
kq3_domain <- kq3_domain_summary |> 
  mutate(rob_let     = numbers[match(rob_foot, foot_unique)],
         consist_let = numbers[match(consist_foot, foot_unique)],
         direct_let  = numbers[match(direct_foot, foot_unique)],
         prec_let    = numbers[match(prec_foot, foot_unique)],
         other_let   = numbers[match(other_foot, foot_unique)],
         )

for (i in 1:nrow(kq3_domain)) {
  for (j in 7:11) {
    kq3_domain[i, j] <- ifelse(!is.na(kq3_domain[i, j + 10]), paste0(kq3_domain[i, j], "<sup>", kq3_domain[i, j + 10], "</sup>"), kq3_domain[i, j])
  }
}

# create domain footnotes
domain_footnotes <- as_tibble(foot_unique) |> 
  mutate(n = row_number(),
         value = paste0("<sup>", n, " </sup>", value)) |> 
  pull(value)

domain_footnotes <- glue_collapse(domain_footnotes, sep = "<br>")

kq3_domain |> 
  filter(!design == "No studies") |> 
  mutate(n_s = paste0(n_studies, "<br>(", n_pts, ")")) |> 
  mutate(space = "") |> 
  left_join(soe_kq3_dat |> select(compare_group, n), by = "n") |>
  # group_by(compare_group) |> 
  select(outcome, design, space, n_s, rob, consist, direct, prec, other) |> 
  gt(id = "one") |> 
  cols_hide(n_s) |> 
  cols_label(
    outcome = "Outcome",
    design = "Design",
    space = "",
    # n_s = "Studies (Pts)",
    rob = "Bias",  
    consist = "Inconsistency",
    direct = "Indirectness",
    prec = "Imprecision", 
    other = "Other"
  ) |>
  fmt_markdown(columns = c(n_s:other)) |> 
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(design, rob:other))) |>
  # tab_style(style = "padding-right:80px",       locations = cells_column_labels(columns = c(design))) |> 
  # tab_style(style = "padding-left:10px",        locations = cells_body(columns = c(design))) |>
  # tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(design))) |> 
  # tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(design))) |>
  tab_spanner(label = "GRADE Domains", columns = c(rob:other)) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(220),
    # n_s ~ px(85),
    design ~ px(60),
    space ~ px(50),
    rob ~ px(120),
    consist ~ px(120),
    direct ~ px(120),
    prec ~ px(120),
    other ~ px(120)
  ) |> 
  domain_footnote() |> 
  tab_footnote(md(domain_footnotes))

```

## **TIVA versus Inhaled**

```{r soe_kq4_data}
#| include: false
col_types_soe <- c("numeric", rep("text", 5), "numeric", rep("text", 16))
soe_kq4_dat <- readxl::read_xlsx("data/soe_2023-05-22_local.xlsx", range = "A1:W24", sheet = "soe_kq4", col_types = col_types_soe) |>
  filter(!n %in% c(4.52, 4.41)) |> # cardiac composite, nrsi mi combined with rct
  clean_names() |>
  mutate(
    n_s = paste0(n_studies, " <br/>(", format(n_pts, big.mark = ","), ")"),
    n = paste0(n, outcome),
    n_s = str_remove_all(n_s, "\\s"),
    n_s = ifelse(str_detect(n_s, "NA"), "—", n_s),
    # outcome = tools::toTitleCase(outcome) |>
    # outcome = str_to_sentence(outcome),
    out_import = case_when(
      out_import == "Limited" ~ "+",
      out_import == "Important" ~ "++",
      out_import == "Critical" ~ "+++"
    ),
    compare_group = case_when(
      comparison == "reg_gen" ~ "Regional vs. General Anesthesia",
    )
  )

soe_summary <- soe_kq4_dat |>
  select(n, comparison, outcome, n_s, design, grade, acc, out_import, summary, result_links, compare_group) |>
  mutate(
    high = paste0("[", vlow, "]", "(soe_gt.html#tiva-grade)"), 
    mod = paste0("[", mod, "]",   "(soe_gt.html#tiva-grade)"),
    low = paste0("[", low, "]",   "(soe_gt.html#tiva-grade)"),
    vlow = paste0("[", vlow, "]", "(soe_gt.html#tiva-grade)"),
    low_very = paste0("[", low_very, "]", "(soe_gt.html#tiva-grade)"),
    grade = case_when(
      grade == "very low" ~ vlow,
      grade == "low" ~ low,
      grade == "moderate" ~ mod,
      grade == "high" ~ high,
      .default = grade
    )
  ) |> 
  select(-c(vlow, low, mod, high, low_very)) 

domain_summary <- soe_kq4_dat |> 
  select(n, comparison, outcome, design, n_studies, n_pts, rob, consist, direct, prec, other, summary, ends_with("foot")) |> 
  # sentence case and add period if missing
  mutate(design = str_to_sentence(design),
         consist_foot = ifelse(!grepl("\\.$", consist_foot) & !is.na(consist_foot), paste0(consist_foot, "."), consist_foot),
         direct_foot  = ifelse(!grepl("\\.$", direct_foot ) & !is.na(direct_foot ), paste0(direct_foot , "."), direct_foot ),
         prec_foot    = ifelse(!grepl("\\.$", prec_foot   ) & !is.na(prec_foot   ), paste0(prec_foot   , "."), prec_foot   ),
         rob_foot     = ifelse(!grepl("\\.$", rob_foot    ) & !is.na(rob_foot    ), paste0(rob_foot    , "."), rob_foot    ),
         other_foot   = ifelse(!grepl("\\.$", other_foot  ) & !is.na(other_foot  ), paste0(other_foot  , "."), other_foot  ),
         across(ends_with("foot"), ~ firstup(.x))
         ) 

```

<font size = 4> `r table_ref()` Strength of evidence summaries — TIVA versus inhaled anesthesia. </font>

```{r kq4_soe_gt}
#| include: true
#| echo: false
soe_summary |>
  mutate(across(grade:result_links, ~ replace_na(., "")),
         design = ifelse(design %in% c("Before/after", "Non-randomized"), "NRSI", design),
         # outcome = str_replace(outcome, "Cognitive dysfunction", "Cognitive dysfunction<br/>"),
         outcome = ifelse(outcome == lag(outcome) & row_number() > 1, "", outcome)
         ) |> 
  # group_by(compare_group) |> 
  gt(id = "one") |>
  cols_hide(c(n, comparison, compare_group)) |>
  cols_label(
    outcome = "Outcome",
    design = "Study Design",
    n_s = "Studies (Pts)",
    grade = "GRADE",
    acc = "ACCF AHA",
    out_import = "Importance",
    summary = "Summary",
    result_links = "Result Detail"
  ) |>
  fmt_markdown(columns = c(outcome, n_s, grade, summary, result_links)) |>
  # tab_row_group(
  #   label = "powerful",
  #   rows = outcome == "Delirium incidence"
  # ) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(outcome, summary, result_links))) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(220),
    design ~ px(80),
    n_s ~ px(85),
    grade ~ px(50),
    acc ~ px(60),
    out_import ~ px(90),
    summary ~ px(325),
    result_links ~ px(120)
  ) |>
  opt_css(
    css = "
    #one p {
    line-height: 1.4;
    }
  "
  ) |> 
  opt_footnote_marks(marks = "numbers") |>
  sub_values(values = c("NA <br/>(NA)"), replacement = "—") |>
  soe_footnote()

```

<a id="tiva-grade"></a>   

### GRADE Domains

<font size = 4> `r table_ref()` GRADE domains for strength of evidence ratings --- TIVA versus inhaled anesthesia. </font>

```{r kq4_domain, eval = TRUE}
#| warning: true
#| include: true
#| echo: false
kq4_domain_summary <- domain_summary |>
  # filter(comparison == "sug_neo") |>
  select(-summary) |>
  mutate(
    design = str_replace(design, "Rct", "RCT"),
  )
         
foot_unique <- kq4_domain_summary |> 
  select(ends_with("foot")) 

foot_unique <- c(t(foot_unique)) |> 
  unlist(use.names = FALSE) |> 
  discard(is.na) 

foot_unique <- unique(foot_unique)

numbers <- c(1:100)
kq4_domain <- kq4_domain_summary |> 
  mutate(rob_let     = numbers[match(rob_foot, foot_unique)],
         consist_let = numbers[match(consist_foot, foot_unique)],
         direct_let  = numbers[match(direct_foot, foot_unique)],
         prec_let    = numbers[match(prec_foot, foot_unique)],
         other_let   = numbers[match(other_foot, foot_unique)],
         )

for (i in 1:nrow(kq4_domain)) {
  for (j in 7:11) {
    kq4_domain[i, j] <- ifelse(!is.na(kq4_domain[i, j + 10]), paste0(kq4_domain[i, j], "<sup>", kq4_domain[i, j + 10], "</sup>"), kq4_domain[i, j])
  }
}

# create domain footnotes
domain_footnotes <- as_tibble(foot_unique) |> 
  mutate(n = row_number(),
         value = paste0("<sup>", n, " </sup>", value)) |> 
  pull(value)

domain_footnotes <- glue_collapse(domain_footnotes, sep = "<br>")

kq4_domain |>
  filter(!design == "No studies") |>
  mutate(
    n_s = paste0(n_studies, "<br>(", n_pts, ")"),
    design = str_replace(design, "Nrsi", "NRSI"),
    design = str_replace(design, "RCT/nrsi", "RCT/NRSI"),
    outcome = ifelse(outcome == lag(outcome) & row_number() > 1, "", outcome)
  ) |>
  mutate(space = "") |>
  left_join(soe_kq4_dat |> select(compare_group, n), by = "n") |>
  # group_by(compare_group) |>
  select(outcome, design, space, n_s, rob, consist, direct, prec, other) |>
  gt(id = "one") |>
  cols_hide(n_s) |>
  cols_label(
    outcome = "Outcome",
    design = "Design",
    space = "",
    # n_s = "Studies (Pts)",
    rob = "Bias",
    consist = "Inconsistency",
    direct = "Indirectness",
    prec = "Imprecision",
    other = "Other"
  ) |>
  fmt_markdown(columns = c(n_s:other)) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(design, rob:other))) |>
  tab_spanner(label = "GRADE Domains", columns = c(rob:other)) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(250),
    # n_s ~ px(85),
    design ~ px(85),
    space ~ px(50),
    rob ~ px(120),
    consist ~ px(120),
    direct ~ px(120),
    prec ~ px(120),
    other ~ px(120)
  ) |>
  domain_footnote() |> 
  tab_footnote(md(domain_footnotes))

```

## **Delirium Prophylaxis**

```{r soe_kq6_data}
#| include: false
col_types_soe <- c("numeric", rep("text", 5), "numeric", rep("text", 16))
soe_kq6_dat <- readxl::read_xlsx("data/soe_2023-05-22_local.xlsx", range = "A1:W29", sheet = "soe_kq6", col_types = col_types_soe) |>
# FIXME: respiratory failure fix
  clean_names() |>
  filter(n != 6.13) |> 
  mutate(
    n_s = paste0(n_studies, " <br/>(", format(n_pts, big.mark = ","), ")"),
    n_s = paste0(n_studies, " <br/>(", n_pts, ")"),
    n = paste0(n, outcome),
    # outcome = tools::toTitleCase(outcome) |>
    # outcome = str_to_sentence(outcome),
    out_import = case_when(
      out_import == "Limited" ~ "+",
      out_import == "Important" ~ "++",
      out_import == "Critical" ~ "+++"
    ),
    compare_group = case_when(
      comparison == "dex_plac" ~ "Dexmedetomidine vs. Placebo/None",
      comparison == "ket_plac" ~ "Ketamine vs. Placebo",
      comparison == "mel_ram_plac" ~ "Melatonin or Ramelteon vs. Placebo"
    )
  )

soe_summary <- soe_kq6_dat |>
  select(n, comparison, outcome, n_s, design, grade, acc, out_import, summary, result_links, compare_group) |>
  mutate(
    grade = case_when(
      grade == "very low" ~ vlow,
      grade == "low" ~ low,
      grade == "moderate" ~ mod, 
      grade == "high" ~ high,
      .default = grade
    )
  ) 

domain_summary <- soe_kq6_dat |> 
  select(n, comparison, outcome, design, n_studies, n_pts, rob, consist, direct, prec, other, summary, ends_with("foot")) |> 
  # sentence case and add period if missing
  mutate(design = str_to_sentence(design),
         consist_foot = ifelse(!grepl("\\.$", consist_foot) & !is.na(consist_foot), paste0(consist_foot, "."), consist_foot),
         direct_foot  = ifelse(!grepl("\\.$", direct_foot ) & !is.na(direct_foot ), paste0(direct_foot , "."), direct_foot ),
         prec_foot    = ifelse(!grepl("\\.$", prec_foot   ) & !is.na(prec_foot   ), paste0(prec_foot   , "."), prec_foot   ),
         rob_foot     = ifelse(!grepl("\\.$", rob_foot    ) & !is.na(rob_foot    ), paste0(rob_foot    , "."), rob_foot    ),
         other_foot   = ifelse(!grepl("\\.$", other_foot  ) & !is.na(other_foot  ), paste0(other_foot  , "."), other_foot  ),
         across(ends_with("foot"), ~ firstup(.x))
         ) 

```

<font size = 4> `r table_ref()` GRADE strength of evidence ratings --- delirium prophylaxis. </font>

```{r kq6_soe_gt}
#| include: true
#| echo: false
soe_summary |>
  mutate(across(grade:result_links, ~ replace_na(., "")),
    design = ifelse(design %in% c("Before/after", "Non-randomized"), "NRSI", design),
    # outcome = str_replace(outcome, "Cognitive dysfunction", "Cognitive dysfunction<br/>"),
    outcome = ifelse(outcome == lag(outcome) & row_number() > 1, "", outcome)
  ) |>
  group_by(compare_group) |>
  gt(id = "one") |>
  cols_hide(c(n, comparison)) |>
  cols_label(
    outcome = "Outcome",
    design = "Study Design",
    n_s = "Studies (Pts)",
    grade = "GRADE",
    acc = "ACCF AHA",
    out_import = "Importance",
    summary = "Summary",
    result_links = "Result Detail"
  ) |>
  fmt_markdown(columns = c(outcome, n_s, grade, summary, result_links)) |>
  # tab_row_group(
  #   label = "powerful",
  #   rows = outcome == "Delirium incidence"
  # ) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(outcome, summary, result_links))) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(200),
    design ~ px(80),
    n_s ~ px(85),
    grade ~ px(60),
    acc ~ px(60),
    out_import ~ px(90),
    summary ~ px(325),
    result_links ~ px(175)
  ) |>
  opt_css(
    css = "
    #one p {
    line-height: 1.4;
    }
  "
  ) |>
  opt_footnote_marks(marks = "numbers") |>
  sub_values(values = c("NA <br/>(NA)"), replacement = "—") |>
  soe_footnote() |> 
  tab_footnote("Common effects model.", locations = cells_body(columns = summary, rows = str_detect(n, "5.34"))) |>
  tab_footnote("Network meta-analysis results were consistent.", locations = cells_body(columns = summary, rows = str_detect(n, "5.11"))) |>
  tab_footnote("Results from the largest trial (N = 650 analyzed) were not consistent with an effect.", locations = cells_body(columns = summary, rows = str_detect(n, "5.21"))) |>
  tab_footnote("Network meta-anlaysis yielded narrower 95% confidence interval attributable to pairwise result incorportating Hartung-Knapp adjustment.", locations = cells_body(columns = summary, rows = str_detect(n, "5.33")))

```

### GRADE Domains

<font size = 4> `r table_ref()` GRADE domains for strength of evidence rating for outcomes relevant to delirium prophylaxis. </font>

```{r kq6_domain, eval = TRUE}
#| warning: false
#| include: true
#| echo: false
kq6_domain_summary <- domain_summary |>
  # filter(comparison == "sug_neo") |>
  select(-summary) |>
  mutate(
    design = str_replace(design, "Rct", "RCT"),
  )
         
foot_unique <- kq6_domain_summary |> 
  select(ends_with("foot")) 

foot_unique <- c(t(foot_unique)) |> 
  unlist(use.names = FALSE) |> 
  discard(is.na) 

foot_unique <- unique(foot_unique)

numbers <- c(1:100)
kq6_domain <- kq6_domain_summary |> 
  mutate(rob_let     = numbers[match(rob_foot, foot_unique)],
         consist_let = numbers[match(consist_foot, foot_unique)],
         direct_let  = numbers[match(direct_foot, foot_unique)],
         prec_let    = numbers[match(prec_foot, foot_unique)],
         other_let   = numbers[match(other_foot, foot_unique)],
         )

for (i in 1:nrow(kq6_domain)) {
  for (j in 7:11) {
    kq6_domain[i, j] <- ifelse(!is.na(kq6_domain[i, j + 10]), paste0(kq6_domain[i, j], "<sup>", kq6_domain[i, j + 10], "</sup>"), kq6_domain[i, j])
  }
}

# create domain footnote
domain_footnotes <- as_tibble(foot_unique) |> 
  mutate(n = row_number(),
         value = paste0("<sup>", n, " </sup>", value)) |> 
  pull(value)

domain_footnotes <- glue_collapse(domain_footnotes, sep = "<br>")

kq6_domain |>
  filter(!design == "No studies") |>
  mutate(n_s = paste0(n_studies, "<br>(", n_pts, ")")) |>
  mutate(
    space = "",
    design = ifelse(design %in% c("Before-after", "RCT/nrsi", "Nrsi"), "NRSI", design),
  ) |>
  left_join(soe_kq6_dat |> select(compare_group, n), by = "n") |>
  group_by(compare_group) |>
  select(outcome, design, space, n_s, rob, consist, direct, prec, other, compare_group) |>
  gt(id = "one") |>
  cols_hide(n_s) |>
  cols_label(
    outcome = "Outcome",
    design = "Design",
    space = "",
    # n_s = "Studies (Pts)",
    rob = "Bias",
    consist = "Inconsistency",
    direct = "Indirectness",
    prec = "Imprecision",
    other = "Other"
  ) |>
  fmt_markdown(columns = c(n_s:other)) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(design, rob:other))) |>
  tab_spanner(label = "GRADE Domains", columns = c(rob:other)) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(200),
    # n_s ~ px(85),
    design ~ px(65),
    space ~ px(50),
    rob ~ px(120),
    consist ~ px(120),
    direct ~ px(120),
    prec ~ px(120),
    other ~ px(120)
  ) |>
  domain_footnote() |>
  tab_footnote(md(domain_footnotes))

```

<hr style="height:2px;border-width:0;color:gray;background-color:gray">


# **Rating Systems Reference**

## GRADE

<br> <font size = 4> <a id="High"></a> **High** --- We are very confident that the true effect lies close to that of the estimate of the effect.

**Moderate** --- We are moderately confident in the effect estimate: The true effect is likely to be close to the estimate of the effect, but there is a possibility that it is substantially different.

**Low** --- Our confidence in the effect estimate is limited: The true effect may be substantially different from the estimate of the effect.

**Very Low** --- We have very little confidence in the effect estimate: The true effect is likely to be substantially different from the estimate of effect.

</font>

### Domains (downgrade)

<font size = 4>

*Bias* --- Systematic error (eg, selection bias, confounding bias, measurement bias).

*Inconsistency* --- Unexplained heterogeneity of results; studies find effect estimates that differ widely.

*Imprecision* --- The range of plausible effects estimated from relevant studies.

*Indirectness* --- Direct evidence consists of research that directly compares the interventions which we are interested in, delivered to the populations in which we are interested, and measures the outcomes important to patients.

*Other (eg, publication bias)* --- Selective publication or reporting of results (typically of positive results).

### Domains (upgrade)

*Effect Size* --- Large effect size (eg, risk ratio \>2 or \<0.5).

*Dose-response* --- When relevant exposure categories.

*Plausible Residual Confounding* --- When unaccounted residual confounding would increase the effect magnitude.

</font>

## ACCF/AHA

<font size = 4>

**Level A** --- High-quality evidence from more than 1 RCTs. Meta-analyses of high-quality RCTs. One or more RCTs corroborated by high-quality registry studies.

**Level B-R** --- Moderate-quality evidence from 1 or more randomized controlled trials. Meta-analyses of moderate-quality RCTs.

**Level B-NR** --- Moderate-quality evidence from 1 or more well-designed, well-executed nonrandomized studies, observational studies, or registry studies. Meta-analyses of such studies.

**Level C-LD** --- Randomized or nonrandomized observational or registry studies with limitations of design or execution. Meta-analyses of such studies. Physiological or mechanistic studies in human subjects.

**Level C-EO** --- Consensus of expert opinion based on clinical experience when evidence is insufficient, vague, or conflicting.

</font>

<font size = 3> RCT: randomized controlled trial; NR: nonrandomized; LD: limited data; EO: expert opinion </font>



