---
title: "Strength of Evidence"
editor: source
toc-title: "Delirium Prophylaxis"
toc-location: "left"
toc-depth: 4
toc_float: 
  collapsed: false
tbl-cap-location: "top"
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
# bibliography: "bib/kq6.bib"
# csl: jama.csl
# link-citations: no
# nocite: '@*'
---

```{r preliminaries}
#| include: false
## preliminaries -------------------------------------- (2022-11-16 11:49) @----
library(conflicted)
library(janitor)
library(htmltools)
library(gt, quietly = TRUE)
library(gtsummary)
library(gtExtras)
library(glue)
library(tidyverse)
conflicts_prefer(dplyr::filter)
knitr::opts_chunk$set(echo = FALSE)
source("code/functions_2023-04-26.R")
```

```{r soe_grade_refs}
# grade footnote
vlow <-  '<span><span class="quality-sign">⨁</span><span class="quality-sign">◯</span><span class="quality-sign">◯</span><span class="quality-sign">◯</span>'
low <- '<span><span class="quality-sign">⨁</span><span class="quality-sign">⨁</span><span class="quality-sign">◯</span><span class="quality-sign">◯</span>'
mod <- '<span><span class="quality-sign">⨁</span><span class="quality-sign">⨁</span><span class="quality-sign">⨁</span><span class="quality-sign">◯</span>'
high <- '<span><span class="quality-sign">⨁</span><span class="quality-sign">⨁</span><span class="quality-sign">⨁</span><span class="quality-sign">⨁</span>'
grade_foot <- paste0("Very low: ", vlow, "; Low: ", low, "; Moderate: ", mod, "; High: ", high, ".")

# TODO: add functions to read data
```

# Delirium Prophylaxis

```{r soeKq6Data}
#| include: false
## soeKq6Data (updated 2022/01/20 09:18) ----------------------------------
col_types_soe <- c("numeric", rep("text", 5), "numeric", rep("text", 19))
soe_kq6.dat <- readxl::read_xlsx("data/soe_2023-03-11.xlsx", range = "A1:Z8", sheet = "soe_kq6", col_types = col_types_soe) |>
  clean_names() |>
  mutate(
    n_s = paste0(n_studies, " <br/>(", n_pts, ")"),
    n = paste0(n, outcome),
    # outcome = tools::toTitleCase(outcome) |>
    # outcome = str_to_sentence(outcome),
    out_import = case_when(
      out_import == "Limited" ~ "+",
      out_import == "Important" ~ "++",
      out_import == "Critical" ~ "+++"
    ),
    compare_group = case_when(
      comparison == "dex_plac" ~ "Dexmedetomidine vs. Placebo/None",
      comparison == "ket_plac" ~ "Ketamine vs. Placebo",
      comparison == "mel_ram_plac" ~ "Melatonin or Ramelteon vs. Placebo"
    )
  )

## (updated 2021/11/17 11:44) soe_summary ---------------------------------
soe_summary <- soe_kq6.dat |>
  select(n, comparison, outcome, n_s, design, grade, acc, out_import, summary, result_links, compare_group) |>
  mutate(
    grade = case_when(
      grade == "very low" ~ vlow,
      grade == "low" ~ low,
      grade == "moderate" ~ mod, 
      grade == "high" ~ high,
      .default = grade
    )
  ) 

## (updated 2021/11/17 11:44) domain_summary ------------------------------
domain_summary <- soe_kq6.dat |> 
  select(n, comparison, outcome, design, n_studies, n_pts, rob, consist, direct, prec, other, summary, ends_with("foot")) |> 
  # sentence case and add period if missing
  mutate(design = str_to_sentence(design),
         consist_foot = ifelse(!grepl("\\.$", consist_foot) & !is.na(consist_foot), paste0(consist_foot, "."), consist_foot),
         direct_foot  = ifelse(!grepl("\\.$", direct_foot ) & !is.na(direct_foot ), paste0(direct_foot , "."), direct_foot ),
         prec_foot    = ifelse(!grepl("\\.$", prec_foot   ) & !is.na(prec_foot   ), paste0(prec_foot   , "."), prec_foot   ),
         rob_foot     = ifelse(!grepl("\\.$", rob_foot    ) & !is.na(rob_foot    ), paste0(rob_foot    , "."), rob_foot    ),
         other_foot   = ifelse(!grepl("\\.$", other_foot  ) & !is.na(other_foot  ), paste0(other_foot  , "."), other_foot  ),
         across(ends_with("foot"), ~ firstup(.x))
         ) 

```

<br/>

### Strength of Evidence Ratings

<br/>

<font size = 4> `r table_ref()` Strength of evidence for outcomes relevant to delirium prophylaxis. </font>

```{r kq6SOE_gt}
#| include: true
#| echo: false

## kq6SOE (updated 2022/01/20 15:00) --------------------------------------
soe_summary |>
  mutate(across(grade:result_links, ~ replace_na(., ""))) |> 
  group_by(compare_group) |> 
  gt(id = "one") |>
  cols_hide(c(n, comparison)) |>
  cols_label(
    outcome = "Outcome",
    design = "Study Design",
    n_s = "Studies (Pts)",
    grade = "GRADE",
    acc = "ACCF AHA",
    out_import = "Importance",
    summary = "Summary",
    result_links = "Result Detail"
  ) |>
  fmt_markdown(columns = c(outcome, n_s, grade, summary, result_links)) |>
  # tab_row_group(
  #   label = "powerful",
  #   rows = outcome == "Delirium incidence"
  # ) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(n_s, grade, acc, out_import, summary))) |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(outcome, summary, result_links))) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(120),
    design ~ px(90),
    n_s ~ px(85),
    grade ~ px(60),
    acc ~ px(60),
    out_import ~ px(90),
    summary ~ px(350),
    result_links ~ px(150)
  ) |>
  opt_footnote_marks(marks = "numbers") |>
  # tab_style(style = "vertical-align:top", locations = cells_body(columns = everything())) |> 
  tab_footnote("Pts: patients; GRADE: Grades of Recommendation, Assessment, Development, and Evaluation; ACCF/AHA: American College of Cardiology Foundation/American Heart Association; RR: risk ratio.") |>
  tab_footnote(md(grade_foot), locations = cells_column_labels(columns = grade)) |>
  tab_footnote("A: high-quality evidence from more than 1 RCT; B-R: moderate-quality evidence from more than 1 RCT; B-NR: moderate-quality evidence from more than one observational study; C-LD: randomized or non-randomized observational or registry studies with limited data; C-EO: consensus of expert opinion.", locations = cells_column_labels(columns = acc)) |>
  tab_footnote("Limited +; Important ++; Critical +++.", locations = cells_column_labels(columns = out_import)) |> 
  tab_footnote("Common effects model.", locations = cells_body(columns = summary, rows = str_detect(n, "5.14"))) |> 
  tab_footnote("Network meta-analysis results were consistent.", locations = cells_body(columns = summary, rows = str_detect(n, "5.11"))) |> 
  tab_footnote("Results from the largest trial (N = 650 analyzed) were not consistent with an effect.", locations = cells_body(columns = summary, rows = str_detect(n, "5.12"))) |> 
  tab_footnote("Network meta-anlaysis yielded narrower 95% confidence interval attributable to pairwise result incorportating Hartung-Knapp adjustment.", locations = cells_body(columns = summary, rows = str_detect(n, "5.13")))

```
### GRADE Domains

<br>

<font size = 4> Table `r table_n`. GRADE domains for strength of evidence rating for outcomes relevant to delirium prophylaxis. </font>

```{r kq6Domain, eval = TRUE}
#| warning: false
#| include: true
#| echo: false
kq6_domain_summary <- domain_summary |>
  # filter(comparison == "sug_neo") |>
  select(-summary) |>
  mutate(
    design = str_replace(design, "Rct", "RCT"),
  )
         
# (updated 2021/05/14 07:42) get list of unique footnotes ----------------
foot_unique <- kq6_domain_summary |> 
  select(ends_with("foot")) 

foot_unique <- c(t(foot_unique)) |> 
  unlist(use.names = FALSE) |> 
  discard(is.na) 

foot_unique <- unique(foot_unique)

numbers <- c(1:100)
kq6_domain <- kq6_domain_summary |> 
  mutate(rob_let     = numbers[match(rob_foot, foot_unique)],
         consist_let = numbers[match(consist_foot, foot_unique)],
         direct_let  = numbers[match(direct_foot, foot_unique)],
         prec_let    = numbers[match(prec_foot, foot_unique)],
         other_let   = numbers[match(other_foot, foot_unique)],
         )

## (updated 2021/05/14 08:04) add footnotes -------------------------------
for (i in 1:nrow(kq6_domain)) {
  for (j in 7:11) {
    kq6_domain[i, j] <- ifelse(!is.na(kq6_domain[i, j + 10]), paste0(kq6_domain[i, j], "<sup>", kq6_domain[i, j + 10], "</sup>"), kq6_domain[i, j])
  }
}

# create domain footnote
domain_footnotes <- as_tibble(foot_unique) |> 
  mutate(n = row_number(),
         value = paste0("<sup>", n, " </sup>", value)) |> 
  pull(value)

domain_footnotes <- glue_collapse(domain_footnotes, sep = "<br>")

## (updated 2021/05/14 08:27) domain summary table ------------------------
kq6_domain |> 
  mutate(n_s = paste0(n_studies, "<br>(", n_pts, ")")) |> 
  mutate(space = "") |> 
  left_join(soe_kq6.dat |> select(compare_group, n), by = "n") |>
  group_by(compare_group) |> 
  select(outcome, design, space, n_s, rob, consist, direct, prec, other) |> 
  gt(id = "one") |> 
  cols_hide(n_s) |> 
  cols_label(
    outcome = "Outcome",
    design = "Design",
    space = "",
    # n_s = "Studies (Pts)",
    rob = "Bias",  
    consist = "Inconsistency",
    direct = "Indirectness",
    prec = "Imprecision", 
    other = "Other"
  ) |>
  fmt_markdown(columns = c(n_s:other)) |> 
  tab_style(style = cell_text(align = "left"),   locations = cells_body(columns = c(rob:other))) |>
  # tab_style(style = "padding-right:80px",       locations = cells_column_labels(columns = c(design))) |> 
  # tab_style(style = "padding-left:10px",        locations = cells_body(columns = c(design))) |>
  tab_style(style = cell_text(align = "center"), locations = cells_column_labels(columns = c(design))) |> 
  tab_style(style = cell_text(align = "center"), locations = cells_body(columns = c(design))) |>
  tab_spanner(label = "GRADE Domains", columns = c(rob:other)) |>
  gt_theme_mg() |>
  cols_width(
    outcome ~ px(120),
    # n_s ~ px(85),
    design ~ px(80),
    space ~ px(50),
    rob ~ px(120),
    consist ~ px(120),
    direct ~ px(120),
    prec ~ px(120),
    other ~ px(120)
  ) |> 
  tab_footnote("If not specified in footnotes, all references are to 95% confidence and prediction intervals.") |>
  tab_footnote("RCT: randomized clincal trial; RR: risk ratio; OR: odds ratio.") |> 
  tab_footnote(md(domain_footnotes))
```


<hr style="height:2px;border-width:0;color:gray;background-color:gray">

<br/>

<br/>

# **Rating Systems Reference**

## GRADE

<br> <font size = 4> 
<a id="High"></a>
**High** --- We are very confident that the true effect lies close to that of the estimate of the effect.

**Moderate** --- We are moderately confident in the effect estimate: The true effect is likely to be close to the estimate of the effect, but there is a possibility that it is substantially different.

**Low** --- Our confidence in the effect estimate is limited: The true effect may be substantially different from the estimate of the effect.

**Very Low** --- We have very little confidence in the effect estimate: The true effect is likely to be substantially different from the estimate of effect.

</font>

### Domains (downgrade)

<font size = 4>

*Bias* --- Systematic error (eg, selection bias, confounding bias, measurement bias).

*Inconsistency* --- Unexplained heterogeneity of results; studies find effect estimates that differ widely.

*Imprecision* --- The range of plausible effects estimated from relevant studies.

*Indirectness* --- Direct evidence consists of research that directly compares the interventions which we are interested in, delivered to the populations in which we are interested, and measures the outcomes important to patients.

*Other (eg, publication bias)* --- Selective publication or reporting of results (typically of positive results).

### Domains (upgrade)

*Effect Size* --- Large effect size (eg, risk ratio >2 or <0.5).

*Dose-response* --- When relevant exposure categories. 

*Plausible Residual Confounding* --- When unaccounted residual confounding would increase the effect magnitude.

</font>

<br/><br/>

## ACCF/AHA

<font size = 4>

**Level A** --- High-quality evidence from more than 1 RCTs. Meta-analyses of high-quality RCTs. One or more RCTs corroborated by high-quality registry studies.

**Level B-R** --- Moderate-quality evidence from 1 or more randomized controlled trials. Meta-analyses of moderate-quality RCTs.

**Level B-NR** --- Moderate-quality evidence from 1 or more well-designed, well-executed nonrandomized studies, observational studies, or registry studies. Meta-analyses of such studies.

**Level C-LD** --- Randomized or nonrandomized observational or registry studies with limitations of design or execution. Meta-analyses of such studies. Physiological or mechanistic studies in human subjects.

**Level C-EO** --- Consensus of expert opinion based on clinical experience when evidence is insufficient, vague, or conflicting.

</font>

<font size = 3> RCT: randomized controlled trial; NR: nonrandomized; LD: limited data; EO: expert opinion </font>
