---
title: "Study/Patient Characteristics Delirium Prophylaxis"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
editor: source
toc-title: "**Delirium Prophylaxis**"
toc-location: "left"
cap-location: "top"
toc-depth: 3
page-layout: full
css: styles.css
tables:
      style: Table
      caption:
        pre: "Table "
        sep: " -- "
---

```{r read_data}
#| include: false
source("code/load_data.R")

study_char_dat <- study_char_dat |>
  mutate(
  funding = ifelse(refid == 13367, "NR", funding),
  arms = ifelse(refid == 120, 2, arms),
  )

asa_class <- asa_combine |>
  mutate(asa = str_trim(asa_ps_incl)) |>
  select(refid, asa) |>
  slice(1, .by = "refid")

all_est <- "{mean} <u>{median}</u> ({min} - {max})"

```

```{r drugs_by_arm}
#| message: false
# drugs & recode drugs/comparators so that usable; "other" category recode to comparator 
# drugs_dat <- study_arm_dat include drug arm data; adds kq5/6 arms

## drug levels and abbreviations ---------------------- (2024-04-14 08:45) @----
drug_recode_levels <- c("Dexmedetomidine",
"Dexmedetomidine/Pregabalin",
"Dexmedetomidine/Ulinastatin",
"Ulinastatin",
"Haloperidol",
"Ketamine",
"Melatonin",
"Ramelteon",
"Gabapentin",
"Midazolam",
"Midazolam/propofol",
"Midazolam/sevoflurane",
"Remimazolam",
"Oxazepam",
# "Morphine",
"Sufentanil",
"Pregabalin",
"Propofol",
"Placebo",
"None",
"Other")

drug_recode_abbr <- c(Dex = "Dexmedetomidine",
"Dex/Preg" = "Dexmedetomidine/Pregabalin",
"Dex/Ulin" = "Dexmedetomidine/Ulinastatin",
Ulin = "Ulinastatin",
Hal = "Haloperidol",
Ket = "Ketamine",
Mel = "Melatonin",
Ram = "Ramelteon",
Gab = "Gabapentin",
Mid = "Midazolam",
"Mid/Prop" = "Midazolam/propofol",
"Mid/Sevo" = "Midazolam/sevoflurane",
Rem = "Remimazolam",
Oxaz = "Oxazepam",
# MS = "Morphine",
Suf = "Sufentanil",
Preg = "Pregabalin",
Prop = "Propofol",
Plac = "Placebo",
None = "None",
Other = "Other")

## drugs; from kq6, add kq5 arm drugs ----------------- (2023-01-16 13:46) @----
# drugs for kq5 studies; needed to fill in "missings" for kq6 arms coded as kq5 arms with detail there
kq5_drug_by_arm <- read_csv("data/kq56_drug_by_arm.csv") |>
  rename(drug = drug_f) |> # arm drug
  mutate(drug = as.character(drug)) |> 
  select(refid, arm_id, drug, control_desc) |> 
  rename(control_desc_kq5 = control_desc, drug_kq5 = drug)

## combine data from kq5 and kq6 ---------------------- (2024-04-14 08:45) @----
drugs_dat_prelim <- study_arm_dat |>
  select(refid, design_f_lab, study, study_l, study_l_w_linked, study_id, arm_id, arm_n, arm_kq6_proph_meds, kq6_control_desc:kq6_notes, multiple_kq) |>
  rename_with(~ str_replace(., "kq6_", ""), everything()) |>
  rename_with(~ str_replace(., "dex_", "dexmed_"), everything()) |> # dexmed to avoid confusion w/dexamethasone
  mutate(
    drug = case_when(
      !is.na(dexmed) ~ dexmed,
      !is.na(ketamine) ~ ketamine,
      !is.na(melatonin) ~ melatonin,
      !is.na(ramelteon) ~ ramelteon,
      !is.na(gabapentin) ~ gabapentin,
      !is.na(ulinastatin) ~ ulinastatin, # all missing
      !is.na(none) ~ none
    ),
    drug = str_replace(drug, "kq6_", ""),
    drug = firstup(drug)
  ) |>
  relocate(drug, .after = arm_n) |>
  left_join(kq5_drug_by_arm, by = c("refid", "arm_id")) |>  # select(refid, study, arm_id, drug, drug_kq5, control_desc, control_desc_kq5)
  # populate drug and control description when recorded only in kq6 arms
  mutate( 
    drug = coalesce(drug, drug_kq5), 
    control_desc = coalesce(control_desc, control_desc_kq5),
    control_desc = firstup(control_desc),
    arm_proph_meds = ifelse(is.na(arm_proph_meds), "kq5_arm", arm_proph_meds), # for origin of data; bookeeping
  ) 

## convert to factors with clean labels for analysis -- (2024-04-14 08:45) @----
drugs_dat <- drugs_dat_prelim |>
  mutate(
    drug_f = fct(drug, levels = c("Dexmedetomidine", "Ketamine", "Melatonin", "Ramelteon", "Ulinastatin", "Midazolam", "Oxazepam", "Haloperidol", "Gabapentin", "Remimazolam", "None", "Placebo", "Other")),
    drug_f = fct_collapse(drug_f, "Control" = c("None", "Placebo", "Other"))
  ) |>
  group_by(refid) |>
  mutate(
    drug_study = case_when( # study drug
      if_any(drug_f, ~ . == "Dexmedetomidine") ~ "Dexmedetomidine",
      if_any(drug_f, ~ . == "Ketamine") ~ "Ketamine",
      if_any(drug_f, ~ . == "Melatonin") ~ "Melatonin",
      if_any(drug_f, ~ . == "Ramelteon") ~ "Ramelteon",
      if_any(drug_f, ~ . == "Remimazolam") ~ "Remimazolam",
      if_any(drug_f, ~ . == "Gabapentin") ~ "Gabapentin",
      if_any(drug_f, ~ . == "Ulinastatin") ~ "Ulinastatin"
      # TRUE ~ "MISSING" # NA_character_ for verification
    ),
    drug_study = fct(drug_study, levels = c("Dexmedetomidine", "Ketamine", "Melatonin", "Ramelteon", "Remimazolam", "Gabapentin", "Ulinastatin")),
    drug_recode = case_when(
      str_detect(other_spec, "Midazolam and propofol") ~ "Midazolam/propofol",
      str_detect(other_spec, "Midazolam and sevoflurane") ~ "Midazolam/sevoflurane",
      str_detect(other_spec, "[Mm]idazolam") ~ "Midazolam",
      str_detect(other_spec, "[Ss]ufentanil") ~ "Sufentanil",
      str_detect(other_spec, "[Pp]ropofol") ~ "Propofol",
      # str_detect(other_spec, "[Mm]orphine") ~ "Morphine",
      str_detect(other_spec, "[Pp]regabalin") ~ "Pregabalin",
      # str_detect(other_spec, "[Rr]hythim") ~ "Rhythim",
      .default = drug
    ),
    drug_recode = ifelse(refid == 2748 & arm_id == 4, "Dexmedetomidine/Pregabalin", drug_recode),
    drug_recode = ifelse(refid == 13406 & arm_id == 3, "Dexmedetomidine/Ulinastatin", drug_recode),
    drug_recode = ifelse(refid == 13393 & arm_id == 1, "Dexmedetomidine/Ulinastatin", drug_recode),
    # drug_recode = ifelse(refid == 13171 & arm_id == 2, "Melatonin/Dexmedetomidine", drug_recode), # exclude nrc
    # drug_recode = ifelse(refid == 13171 & arm_id == 1, "Dexmedetomidine", drug_recode),
    drug_recode = fct(drug_recode, levels = drug_recode_levels),
    drug_recode_abbr = fct_recode(drug_recode, !!!drug_recode_abbr)
  ) |>
  ungroup() |>
  relocate(c(drug, drug_f, drug_recode, drug_recode_abbr, drug_study), .after = arm_id) |>
  relocate(c(other_spec, interv_desc, control_desc), .after = last_col()) |>
  arrange(refid, drug_study) |>
  fill(drug_study) |>
  arrange(refid, arm_id)

# write_csv(drugs_dat, "data/drugs_dat.csv", na = "")

```

```{r refids}
linked_refid <- study_char_dat |>
  filter(refid %in% kq6_refid) |>
  arrange(year) |> 
  group_by(linked_references_all_refid) |> # count 1 for multiple pubs from single study
  slice(2) |> 
  pull(refid) 

dex_refid <- drugs_dat |> 
  filter(drug == "Dexmedetomidine") |> 
  filter(!refid %in% linked_refid) |>
  pull(refid) 

mel_ram_refid <- drugs_dat |> 
  filter(drug %in% c("Melatonin", "Ramelteon")) |> 
  filter(!refid %in% linked_refid) |>
  pull(refid)

ket_refid <- drugs_dat |> 
  filter(drug == "Ketamine") |> 
  filter(!refid %in% linked_refid) |>
  pull(refid)

```

# **Dexmedetomidine**

## Randomized Clinical Trials

<font size = 4> `r table_ref()` Study and patient characteristics — randomized clinical trials of dexmedetomidine. </font>

```{r dex_rct}
#| layout: [[35, 30, 35]]

summary_study_char_tab_rct(dex_refid)

summary_surg_tab_rct(dex_refid)

## table data ----
pt_char_tab <- study_arm_dat |>
  filter(refid %in% pt_char_tab_refids_rct(dex_refid)) |> 
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

## summary table ----
pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, pre_mmse_mean_med, cog_imp, dm, cardiac) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean/med)",
      bmi_mean_med = "BMI (mean/med)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status, N (%)",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      # living_independent = "Lives Independently (%)",
      # living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preop MMSE (mean/med)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)"
      # malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ c(0, 1),
      white ~ 1,
      black ~ 1,
      asian ~ 0,
      # living_independent ~ 1,
      # living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1
      # malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ all_est,
      bmi_mean_med ~ all_est,
      female_perc ~ all_est,
      asa ~ "{n} ({p})",
      white ~ all_est,
      black ~ "{median}",
      asian ~ all_est,
      # living_independent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # living_dependent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_home ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_assisted ~ "{mean} <u>{median}</u> ({min} - {max})",
      pre_mmse_mean_med ~ all_est,
      cog_imp ~ all_est,
      dm ~ all_est,
      cardiac ~ all_est
      # malnourish ~ "{mean} <u>{median}</u> ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "continuous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "continuous",
      black ~ "continuous",
      asian ~ "continuous",
      # living_independent ~ "continuous",
      # living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "continuous",
      cog_imp ~ "continuous",
      dm ~ "continuous",
      cardiac ~ "continuous"
      # malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
    missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean<u> Med </u>(Range) <br/> or N (%)**") |>
  modify_footnote(update = stat_0 ~ NA) |>
  as_gt(id = "one") |>
  cols_width(
    3 ~ px(170),
    # 5 ~ px(60),
    6 ~ px(110)
  ) |>
  fmt_markdown(stat_0) |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  # tab_footnote("Number of trials reporting from the 9 included (11 publications).", locations = cells_column_labels(columns = c(n)), placement = "right") |>
  # tab_footnote("Mean, median, or range of the mean/med reported in trials.", locations = cells_column_labels(columns = c(stat_0)), placement = "right") |>
  tab_footnote(paste0("N of the ", length(pt_char_tab_refids_rct(dex_refid)), " studies reporting characteristic allowing description."), locations = cells_column_labels(columns = c(n)), placement = "right") |> 
  as_raw_html()


```

## Nonrandomized Studies

<font size = 4> `r table_ref()` Study and patient characteristics — nonrandomized studies of dexmedetomidine. </font>

```{r dex_nrsi}
#| layout: [[35, 30, 35]]

summary_study_char_tab_nrsi(dex_refid)

summary_surg_tab_nrsi(dex_refid)

## table data ----
pt_char_tab <- study_arm_dat |>
  filter(refid %in% pt_char_tab_refids_nrsi(dex_refid)) |> 
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

## summary table ----
pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, pre_mmse_mean_med, cog_imp, dm, cardiac) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean/med)",
      bmi_mean_med = "BMI (mean/med)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status, N (%)",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      # living_independent = "Lives Independently (%)",
      # living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preop MMSE (mean/med)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)"
      # malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ c(0, 1),
      white ~ 1,
      black ~ 1,
      asian ~ 0,
      # living_independent ~ 1,
      # living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1
      # malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ "{mean} <u>{median}</u> ({min} - {max})",
      bmi_mean_med ~ "{mean} <u>{median}</u> ({min} - {max})",
      female_perc ~ "{mean} <u>{median}</u> ({min} - {max})",
      asa ~ "{n} ({p})",
      white ~ "{mean} ({min} - {max})",
      black ~ "{mean}",
      asian ~ "{mean} <u>{median}</u> ({min} - {max})",
      # living_independent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # living_dependent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_home ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_assisted ~ "{mean} <u>{median}</u> ({min} - {max})",
      pre_mmse_mean_med ~ "{mean} <u>{median}</u> ({min} - {max})",
      cog_imp ~ "all {mean}",
      dm ~ "{mean} <u>{median}</u> ({min} - {max})",
      cardiac ~ "{mean} <u>{median}</u>  ({min} - {max})"
      # malnourish ~ "{mean} <u>{median}</u> ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "continuous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "continuous",
      black ~ "continuous",
      asian ~ "continuous",
      # living_independent ~ "continuous",
      # living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "continuous",
      cog_imp ~ "continuous",
      dm ~ "continuous",
      cardiac ~ "continuous"
      # malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
  missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean<u> Med </u>(Range) <br/> or N (%)**") |>
  modify_footnote(update = stat_0 ~ NA) |>
  as_gt(id = "one") |>
  cols_width(
    3 ~ px(170),
    # 5 ~ px(60),
    6 ~ px(110)
  ) |>
  fmt_markdown(stat_0) |>  
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  tab_footnote(paste0("N of the ", length(pt_char_tab_refids_nrsi(dex_refid)), " studies reporting characteristic allowing description."), locations = cells_column_labels(columns = c(n)), placement = "right") |> 
  as_raw_html()
  # tab_info()

```

# **Melatonin and Ramelteon**

## Randomized Clinical Trials

<font size = 4> `r table_ref()` Study and patient characteristics — randomized clinical trials of melatonin and ramelteon. </font>

```{r met_ram_rct}
#| layout: [[35, 30, 35]]

summary_study_char_tab_rct(mel_ram_refid)

summary_surg_tab_rct(mel_ram_refid)

## table data ----
pt_char_tab <- study_arm_dat |>
  filter(refid %in% pt_char_tab_refids_rct(mel_ram_refid)) |> 
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

## summary table ----
pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, pre_mmse_mean_med, cog_imp, dm, cardiac) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean/med)",
      bmi_mean_med = "BMI (mean/med)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status, N (%)",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      # living_independent = "Lives Independently (%)",
      # living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preop MMSE (mean/med)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)"
      # malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ c(0, 1),
      white ~ 1,
      black ~ 1,
      asian ~ 0,
      # living_independent ~ 1,
      # living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1
      # malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ "{mean} <u>{median}</u> ({min} - {max})",
      bmi_mean_med ~ "{median} ({min} - {max})",
      female_perc ~ "{median} ({min} - {max})",
      asa ~ "{n} ({p})",
      white ~ "{median}",
      black ~ "{median}",
      asian ~ "all {median}",
      # living_independent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # living_dependent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_home ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_assisted ~ "{mean} <u>{median}</u> ({min} - {max})",
      pre_mmse_mean_med ~ "{mean} <u>{median}</u> ({min} - {max})",
      cog_imp ~ "{mean} <u>{median}</u> ({min} - {max})",
      dm ~ "{mean} <u>{median}</u> ({min} - {max})",
      cardiac ~ "{mean} <u>{median}</u> ({min} - {max})"
      # malnourish ~ "{mean} <u>{median}</u> ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "continuous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "continuous",
      black ~ "continuous",
      asian ~ "continuous",
      # living_independent ~ "continuous",
      # living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "continuous",
      cog_imp ~ "continuous",
      dm ~ "continuous",
      cardiac ~ "continuous"
      # malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
  missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean<u> Med </u>(Range) <br/> or N (%)**") |>
  modify_footnote(update = stat_0 ~ NA) |>
  as_gt(id = "one") |>
  cols_width(
    3 ~ px(170),
    # 5 ~ px(60),
    6 ~ px(110)
  ) |>
  fmt_markdown(stat_0) |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  # tab_footnote("Number of trials reporting from the 9 included (11 publications).", locations = cells_column_labels(columns = c(n)), placement = "right") |>
  # tab_footnote("Mean, median, or range of the mean/med reported in trials.", locations = cells_column_labels(columns = c(stat_0)), placement = "right") |>
  tab_footnote(paste0("N of the ", length(pt_char_tab_refids_rct(mel_ram_refid)), " trials reporting characteristic allowing description."), locations = cells_column_labels(columns = c(n)), placement = "right") |> 
  as_raw_html()

```

## Nonrandomized Studies

<font size = 4> `r table_ref()` Study and patient characteristics — nonrandomized studies of melatonin and ramelteon. </font>

```{r mel_ram_nrsi}
#| layout: [[35, 30, 35]]

summary_study_char_tab_nrsi(mel_ram_refid)

summary_surg_tab_nrsi(mel_ram_refid)

## table data ----
pt_char_tab <- study_arm_dat |>
  filter(refid %in% pt_char_tab_refids_nrsi(mel_ram_refid)) |> 
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

## summary table ----
pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, pre_mmse_mean_med, cog_imp, dm, cardiac) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean/med)",
      bmi_mean_med = "BMI (mean/med)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status, N (%)",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      # living_independent = "Lives Independently (%)",
      # living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preop MMSE (mean/med)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)"
      # malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ c(0, 1),
      white ~ 1,
      black ~ 1,
      asian ~ 0,
      # living_independent ~ 1,
      # living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1
      # malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ all_est,
      bmi_mean_med ~ "{mean}",
      female_perc ~ all_est,
      asa ~ "{n} ({p})",
      white ~ "",
      black ~ "",
      asian ~ "all {median}",
      # living_independent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # living_dependent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_home ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_assisted ~ "{mean} <u>{median}</u> ({min} - {max})",
      pre_mmse_mean_med ~ "",
      cog_imp ~ "{mean} ({min} - {max})",
      dm ~ all_est,
      cardiac ~ "{mean} ({min} - {max})"
      # malnourish ~ "{mean} <u>{median}</u> ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "continuous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "dichotomous",
      black ~ "dichotomous",
      asian ~ "continuous",
      # living_independent ~ "continuous",
      # living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "dichotomous",
      cog_imp ~ "continuous",
      dm ~ "continuous",
      cardiac ~ "continuous"
      # malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
  missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean<u> Med </u>(Range) <br/> or N (%)**") |>
  modify_footnote(update = stat_0 ~ NA) |>
  as_gt(id = "one") |>
  cols_width(
    3 ~ px(170),
    # 5 ~ px(60),
    6 ~ px(110)
  ) |>
  fmt_markdown(stat_0) |>  
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  tab_footnote(paste0("N of the ", length(pt_char_tab_refids_nrsi(mel_ram_refid)), " studies reporting characteristic allowing description."), locations = cells_column_labels(columns = c(n)), placement = "right") 
  # tab_info()

```

# **Ketamine**

## Randomized Clinical Trials

<font size = 4> `r table_ref()` Study and patient characteristics — randomized clinical trials of ketamine. </font>
  
```{r study_char_ket_rct}
#| layout: [[35, 30, 35]]

summary_study_char_tab_rct(ket_refid)

summary_surg_tab_rct(ket_refid)

# table data ----
pt_char_tab <- study_arm_dat |>
  filter(refid %in% pt_char_tab_refids_rct(ket_refid)) |> 
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

## summary table ----
pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, pre_mmse_mean_med, cog_imp, dm, cardiac) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean/med)",
      bmi_mean_med = "BMI (mean/med)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status, N (%)",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      # living_independent = "Lives Independently (%)",
      # living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preop MMSE (mean/med)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)"
      # malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ c(0, 1),
      white ~ 1,
      black ~ 1,
      asian ~ 0,
      # living_independent ~ 1,
      # living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1
      # malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ all_est,
      bmi_mean_med ~ all_est,
      female_perc ~ all_est,
      asa ~ "{n} ({p})",
      white ~ "{median}",
      black ~ "",
      asian ~ "all {median}",
      # living_independent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # living_dependent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_home ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_assisted ~ "{mean} <u>{median}</u> ({min} - {max})",
      pre_mmse_mean_med ~ all_est,
      cog_imp ~ "all {mean}",
      dm ~ all_est,
      cardiac ~ "{mean} ({min} - {max})"
      # malnourish ~ "{mean} <u>{median}</u> ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "continuous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "continuous",
      black ~ "dichotomous",
      asian ~ "continuous",
      # living_independent ~ "continuous",
      # living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "continuous",
      cog_imp ~ "continuous",
      dm ~ "continuous",
      cardiac ~ "continuous"
      # malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
    missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean<u> Med </u>(Range) <br/> or N (%)**") |>
  modify_footnote(update = stat_0 ~ NA) |>
  as_gt(id = "one") |>
  cols_width(
    3 ~ px(170),
    # 5 ~ px(60),
    6 ~ px(110)
  ) |>
  fmt_markdown(stat_0) |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  # tab_footnote("Number of trials reporting from the 9 included (11 publications).", locations = cells_column_labels(columns = c(n)), placement = "right") |>
  # tab_footnote("Mean, median, or range of the mean/med reported in trials.", locations = cells_column_labels(columns = c(stat_0)), placement = "right") |>
  tab_footnote(paste0("N of the ", length(pt_char_tab_refids_rct(ket_refid)), " trials reporting characteristic allowing description."), locations = cells_column_labels(columns = c(n)), placement = "right")

```

## Nonrandomized Studies

<font size = 4> `r table_ref()` Study and patient characteristics — nonrandomized studies of ketamine. </font>
  
```{r study_char_ket_nrsi}
#| layout: [[35, 30, 35]]

summary_study_char_tab_nrsi(ket_refid)

summary_surg_tab_nrsi(ket_refid)

## table data ----
pt_char_tab <- study_arm_dat |>
  filter(refid %in% pt_char_tab_refids_nrsi(ket_refid)) |> 
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

## summary table ----
pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, pre_mmse_mean_med, cog_imp, dm, cardiac) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean/med)",
      bmi_mean_med = "BMI (mean/med)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status, N (%)",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      # living_independent = "Lives Independently (%)",
      # living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preop MMSE (mean/med)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)"
      # malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ c(0, 1),
      white ~ 1,
      black ~ 1,
      asian ~ 0,
      # living_independent ~ 1,
      # living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1
      # malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ "{mean} <u>{median}</u> ({min} - {max})",
      bmi_mean_med ~ "",
      female_perc ~ "{median} ({min} - {max})",
      asa ~ "{n} ({p})",
      white ~ "",
      black ~ "{median}",
      asian ~ "",
      # living_independent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # living_dependent ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_home ~ "{mean} <u>{median}</u> ({min} - {max})",
      # housing_assisted ~ "{mean} <u>{median}</u> ({min} - {max})",
      pre_mmse_mean_med ~ "",
      cog_imp ~ "{mean}",
      dm ~ "",
      cardiac ~ ""
      # malnourish ~ "{mean} <u>{median}</u> ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "dichotomous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "dichotomous",
      black ~ "continuous",
      asian ~ "dichotomous",
      # living_independent ~ "continuous",
      # living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "dichotomous",
      cog_imp ~ "continuous",
      dm ~ "dichotomous",
      cardiac ~ "dichotomous"
      # malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
    missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean <u>Med</u> (Range) <br/> or N (%)**") |>
  modify_footnote(update = stat_0 ~ NA) |>
  as_gt(id = "one") |>
  cols_width(
    3 ~ px(170),
    # 5 ~ px(60),
    6 ~ px(110)
  ) |>
  fmt_markdown(stat_0) |>  
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  tab_footnote(paste0("N of the ", length(pt_char_tab_refids_nrsi(ket_refid)), " studies reporting characteristic allowing description."), locations = cells_column_labels(columns = c(n)), placement = "right") |> 
  as_raw_html()


```


