---
title: "Study/Patient Characteristics Expanded Preoperative Evaluation"
date: "`r format(Sys.time(), '%d %B, %Y (%H:%M)')`"
editor: source
toc-title: "**TIVA vs. Inhalation Anesthesia <br/> Summary Study/Patient Characteristics** "
toc-location: "left"
cap-location: "top"
toc-depth: 3
page-layout: full
css: styles.css
tables:
  style: Table
caption:
  pre: "Table "
sep: " -- "
---

```{r read_data}
#| include: false
source("code/load_data.R")

# add arm variable to study_arm_dat
study_arm_dat <- data_kq(study_arm_dat, kq1_refid) |>
  mutate(arm = ifelse(arm_kq1_eval == "eval_expand", "Exp", "Std"))

# fix hempenius 2013/2016 linked to include one study
hempenius_2016_arm <- study_arm_dat |> filter(refid == 1263)
hempenius_2013_arm <- study_arm_dat |> filter(refid == 760)
hempenius_2016_char <- study_char_dat |> filter(refid == 1263)
hempenius_2013_char <- study_char_dat |> filter(refid == 760)
hempenius_2013_arm <- coalesce(hempenius_2013_arm, hempenius_2016_arm)
hempenius_2013_char <- coalesce(hempenius_2013_char, hempenius_2016_char)

# linkded
kq1_refid <- kq1_refid[!kq1_refid %in% c(1263, 17156)]

study_char_dat <- study_char_dat |>
  filter(refid %in% kq1_refid) |>
  filter(refid != 760) |>
  bind_rows(hempenius_2013_char) 

study_arm_dat <- study_arm_dat |>
  filter(refid %in% kq1_refid) |>
  filter(refid != 1263) |>
  bind_rows(hempenius_2013_arm)

```

## Randomized Clinical Trials

### Study Characteristics

<font size = 4> `r table_ref()` Characteristics of included randomized clinical trials. </font>

```{r study_char_rct}
study_char_tab <- study_char_dat |>
  filter(design == "rct") |>
  mutate(
    low_r = if_else(non_vh_hdi == "yes", 1, 0, missing = 0),
    pilot = if_else(pilot == "yes", 1, 0, missing = 0),
    ambulatory = !is.na(ambulatory),
    one_center = centers == 1,
    multi_center = centers > 1,
    general = !is.na(general),
    regional = !is.na(regional),
    sedation = !is.na(sedation),
    non_vh_hdi = ifelse(is.na(non_vh_hdi), 0, 1),
    funding = case_when(
      funding == "industry" ~ "Industry",
      funding == "pub_indus" ~ "Public and industry",
      funding == "public" ~ "Public",
      funding == "NR" ~ "Not reported",
      TRUE ~ "Other"
    ),
    author_coi = author_coi == "author_coi",
    registered = if_else(registered == "yes", TRUE, FALSE, missing = FALSE),
    across(c(ambulatory, one_center, multi_center, general, regional, sedation, registered, author_coi), ~ .x * 1)
  ) |>
  select(refid, study, country, low_r, non_vh_hdi, pilot, ambulatory, centers, funding, registered, n_enroll, arms, author_coi)

study_char_tab |>
  select(n_enroll, arms, pilot, ambulatory, centers, country, non_vh_hdi, funding, author_coi, registered) |>
  tbl_summary(
    label = list(
      n_enroll = "Patients enrolled",
      arms = "Arms",
      pilot = "Pilot study",
      ambulatory = "Ambulatory",
      centers = "Centers",
      country = "Country",
      non_vh_hdi = "Low resource country",
      funding = "Funding",
      author_coi = "Author conflict of interest",
      registered = "Registered"
    ),
    digits = list(
      n_enroll ~ 0
    ),
    type = list(
      n_enroll ~ "continuous",
      arms ~ "categorical"
    ),
    statistic = list(
      # calculate percentages including missing values in the denominator
      n_enroll ~ "{mean} [<u>{median}</u>] ({min} - {max})",
      arms ~ "{n} ({p})"
    ),
    missing_text = "Not reported",
    sort = list(everything() ~ "frequency")
  ) |>
  as_gt(id = "one") |>
  fmt_markdown(stat_0) |>
  gt_theme_mg()

```

### Surgical Procedures

<font size = 4> `r table_ref()` Surgical procedures performed in randomized clinical trials. </font>

```{r surg_rct}
surg_tab <- surgs |>
  filter(refid %in% study_char_tab$refid) |> # only kq4 rcts
  select(refid, surgs) |>
  tabyl(surgs) |> # summarise(total = sum(n))
  arrange(desc(percent)) |>
  rename(per = percent) |>
  mutate(
    per = paste0("(", format(round(100 * per, 1), nsmall = 1), ")"),
    per = str_replace(per, " ", ""),
    n = as.character(n),
    n_per = paste(n, per)
  ) |>
  select(surgs, n_per) |>
  rename(result = n_per, characteristic = surgs)

surgs |>
  filter(refid %in% study_char_tab$refid) |> # only kq4 rcts
  select(surgs) |>
  tbl_summary(
    label = list(
      surgs = "Procedure(s)"
    ),
    statistic = list(
      surgs ~ "{n} ({p})"
    ),
    type = list(
      surgs ~ "categorical"
    ),
    missing_text = "Not reported",
    sort = list(everything() ~ "frequency")
  ) |>
  as_gt(id = "one") |>
  gt_theme_mg() |>
  cols_width(
    5 ~ px(240),
    6 ~ px(100)
  ) |>
  tab_footnote("If reported as various/mixed or included more than 4 types of procedures.",  locations = cells_body(columns = label, rows = label == "Various"), placement = "right")

```

### Patient Charcteristics

<font size = 4> `r table_ref()` Patient characteristics in randomized clinical trials. </font>

```{r pt_rct}
asa_class <- asa_combine |>
  mutate(asa = str_trim(asa_ps_incl)) |>
  select(refid, asa) |>
  slice(1, .by = "refid")

# summaries for individual studies combining arms
pt_char_tab <- study_arm_dat |>
  filter(refid %in% study_char_tab$refid) |> # only kq1 rct
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, living_independent, living_dependent, pre_mmse_mean_med, cog_imp, dm, cardiac, malnourish) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean or median)",
      bmi_mean_med = "BMI (mean or median)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      living_independent = "Lives Independently (%)",
      living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preoperative MMSE (mean or median)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)",
      malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ 1,
      white ~ 1,
      black ~ 1,
      asian ~ 1,
      living_independent ~ 1,
      living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1,
      malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ "{mean} [<u>{median}</u>] ({min} - {max})",
      bmi_mean_med ~ "{median} ({min} - {max})",
      female_perc ~ "{median} ({min} - {max})",
      asa ~ "{n} ({p}%)",
      white ~ "{median} ({min} - {max})",
      black ~ "          — ",
      asian ~ "{median} ({min} - {max})",
      living_independent ~ "{mean} ({min} - {max})",
      living_dependent ~ "{mean} ({min} - {max})",
      # housing_home ~ "{mean} ({min} - {max})",
      # housing_assisted ~ "{mean} ({min} - {max})",
      pre_mmse_mean_med ~ "{mean} ({min} - {max})",
      cog_imp ~ "{mean} ({min} - {max})",
      dm ~ "{mean} ({min} - {max})",
      cardiac ~ "{mean} ({min} - {max})",
      malnourish ~ "{mean} ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "continuous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "continuous",
      black ~ "dichotomous",
      asian ~ "continuous",
      living_independent ~ "continuous",
      living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "continuous",
      cog_imp ~ "continuous",
      dm ~ "continuous",
      cardiac ~ "continuous",
      malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
  missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean<u> Med </u>(Range)**") |>
  modify_footnote(update = stat_0 ~ NA) |> 
  as_gt(id = "one") |>
  fmt_markdown(stat_0) |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  tab_footnote("Number of trials reporting from the 9 included (11 publications).", locations = cells_column_labels(columns = c(n)), placement = "right") |> 
  tab_footnote("Mean, median, or range of the mean or median reported in trials.", locations = cells_column_labels(columns = c(stat_0)), placement = "right") 
  # tab_info()

```

## Nonrandomized Studies

### Study Characteristics

<font size = 4> `r table_ref()` Characteristics of nonrandomized studies. </font>

```{r study_char_nrsi}
study_char_tab <- study_char_dat |>
  filter(refid %in% kq1_refid) |>
  filter(!design == "rct") |>
  mutate(
    low_r = if_else(non_vh_hdi == "yes", 1, 0, missing = 0),
    pilot = if_else(pilot == "yes", 1, 0, missing = 0),
    ambulatory = !is.na(ambulatory),
    one_center = centers == 1,
    multi_center = centers > 1,
    general = !is.na(general),
    regional = !is.na(regional),
    sedation = !is.na(sedation),
    non_vh_hdi = ifelse(is.na(non_vh_hdi), 0, 1),
    funding = case_when(
      funding == "industry" ~ "Industry",
      funding == "pub_indus" ~ "Public and industry",
      funding == "public" ~ "Public",
      funding == "NR" ~ "Not reported",
      TRUE ~ "Other"
    ),
    author_coi = author_coi == "author_coi",
    registered = if_else(registered == "yes", TRUE, FALSE, missing = FALSE),
    across(c(ambulatory, one_center, multi_center, general, regional, sedation, registered, author_coi), ~ .x * 1)
  ) |>
  select(refid, study, design_f_lab, country, low_r, non_vh_hdi, pilot, ambulatory, centers, funding, registered, n_enroll, arms, author_coi)

study_char_tab |>
  mutate(design_f_lab = fct_drop(design_f_lab)) |>
  select(design_f_lab, n_enroll, arms, pilot, ambulatory, centers, country, non_vh_hdi, funding, author_coi, registered) |>
  tbl_summary(
    label = list(
      design_f_lab = "Design",
      n_enroll = "Patients enrolled",
      arms = "Arms",
      pilot = "Pilot study",
      ambulatory = "Ambulatory",
      centers = "Centers",
      country = "Country",
      non_vh_hdi = "Low resource country",
      funding = "Funding",
      author_coi = "Author conflict of interest",
      registered = "Registered"
    ),
    digits = list(
      n_enroll ~ 0
    ),
    type = list(
      n_enroll ~ "continuous",
      arms ~ "categorical"
    ),
    statistic = list(
      # calculate percentages including missing values in the denominator
      n_enroll ~ "{mean} [<u>{median}</u>] ({min} - {max})",
      arms ~ "{n} ({p})"
    ),
    missing_text = "Not reported",
    sort = list(c(design_f_lab, country, funding) ~ "frequency")
  ) |>
  as_gt(id = "one") |>
  fmt_markdown(stat_0) |>
  # cols_width(
  #   study_l          ~ px(165),
  #   arm_n            ~ px(45)
  # ) |>
  gt_theme_mg()

```

### Surgical Procedures

<font size = 4> `r table_ref()` Surgical procedures performed in nonrandomized studies. </font>

```{r surg_nrsi}
surg_tab <- surgs |>
  filter(refid %in% study_char_tab$refid) |> # only kq4 rcts
  select(refid, surgs) |>
  tabyl(surgs) |> # summarise(total = sum(n))
  arrange(desc(percent)) |>
  rename(per = percent) |>
  mutate(
    per = paste0("(", format(round(100 * per, 1), nsmall = 1), ")"),
    per = str_replace(per, " ", ""),
    n = as.character(n),
    n_per = paste(n, per)
  ) |>
  select(surgs, n_per) |>
  rename(result = n_per, characteristic = surgs)

surgs |>
  filter(refid %in% study_char_tab$refid) |> # only kq4 rcts
  select(surgs) |>
  tbl_summary(
    label = list(
      surgs = "Procedure(s)"
    ),
    statistic = list(
      surgs ~ "{n} ({p})"
    ),
    type = list(
      surgs ~ "categorical"
    ),
    missing_text = "Not reported",
    sort = list(everything() ~ "frequency")
  ) |>
  as_gt(id = "one") |>
  gt_theme_mg() |>
  cols_width(
    5 ~ px(240),
    6 ~ px(100)
  ) |>
  tab_footnote("If reported as various/mixed or included more than 4 types of procedures.",  locations = cells_body(columns = label, rows = label == "Various"), placement = "right")

```

### Patient Charcteristics

<font size = 4> `r table_ref()` Patient characteristics in nonrandomized studies. </font>

```{r}
# summaries for individual studies combining arms
pt_char_tab <- study_arm_dat |>
  filter(refid %in% study_char_tab$refid) |> # only kq1 rct
  mutate(
    wgt = arm_n / sum(arm_n, na.rm = TRUE),
    N = sum(arm_n),
    .by = refid
  ) |>
  group_by(refid) |>
  summarize(
    across(
      c(
        age_mean,
        age_med,
        female_perc,
        white,
        black,
        asian,
        bmi_m,
        bmi_med,
        pre_mmse_m,
        pre_mmse_med,
        living_independent,
        living_dependent,
        # housing_home,
        # housing_assisted,
        cog_imp,
        malnourish,
        dm,
        cardiac,
        # cancer,
        # ortho,
        # gi,
        # neuro,
        # pulm,
        # endo,
        # renal,
        # hepatic
      ),
      ~ pt_sum(.x, wgt)
    ),
    N = sum(arm_n)
  ) |>
  mutate(
    age_mean_med = coalesce(age_mean, age_med),
    bmi_mean_med = coalesce(bmi_m, bmi_med),
    pre_mmse_mean_med = coalesce(pre_mmse_m, pre_mmse_med),
  ) |>
  select(-c(bmi_m, bmi_med, pre_mmse_m, pre_mmse_med, age_mean, age_med)) |>
  left_join(asa_class, by = "refid")

pt_char_tab |>
  select(age_mean_med, bmi_mean_med, female_perc, asa, white, black, asian, living_independent, living_dependent, pre_mmse_mean_med, cog_imp, dm, cardiac, malnourish) |>
  mutate(
    # asian = ifelse(asian == 100, "100%", NA),
    asa = ifelse(asa == "NR", NA, asa),
  ) |>
  tbl_summary(
    label = list(
      age_mean_med = "Age (mean or median)",
      bmi_mean_med = "BMI (mean or median)",
      female_perc = "Female (%)",
      asa = "ASA Physical Status",
      white = "White (%)",
      black = "Black (%)",
      asian = "Asian (%)",
      living_independent = "Lives Independently (%)",
      living_dependent = "Lives Dependent (%)",
      # housing_home = "Living at Home (%)",
      # housing_assisted = "Assisted Living (%)",
      cog_imp = "Cognitive Impairment (%)",
      pre_mmse_mean_med = "Preoperative MMSE (mean or median)",
      dm = "Diabetes (%)",
      cardiac = "Cardiac (%)",
      malnourish = "Malnourished (%)"
    ),
    digits = list(
      age_mean_med ~ 1,
      bmi_mean_med ~ 1,
      female_perc ~ 1,
      asa ~ 1,
      white ~ 1,
      black ~ 1,
      asian ~ 1,
      living_independent ~ 1,
      living_dependent ~ 1,
      # housing_home ~ 1,
      # housing_assisted ~ 1,
      pre_mmse_mean_med ~ 1,
      cog_imp ~ 1,
      dm ~ 1,
      cardiac ~ 1,
      malnourish ~ 1
    ),
    statistic = list(
      age_mean_med ~ "{mean} [<u>{median}</u>] ({min} - {max})",
      bmi_mean_med ~ "{median} ({min} - {max})",
      female_perc ~ "{median} ({min} - {max})",
      asa ~ "{n} ({p}%)",
      white ~ "{median} ({min} - {max})",
      black ~ "{median} ({min} - {max})",
      asian ~ "{median} ({min} - {max})",
      living_independent ~ "{mean} ({min} - {max})",
      living_dependent ~ "{mean} ({min} - {max})",
      # housing_home ~ "{mean} ({min} - {max})",
      # housing_assisted ~ "{mean} ({min} - {max})",
      pre_mmse_mean_med ~ "{mean} ({min} - {max})",
      cog_imp ~ "{mean} ({min} - {max})",
      dm ~ "{mean} ({min} - {max})",
      cardiac ~ "{mean} ({min} - {max})",
      malnourish ~ "{mean} ({min} - {max})"
    ),
    type = list(
      age_mean_med ~ "continuous",
      bmi_mean_med ~ "continuous",
      female_perc ~ "continuous",
      asa ~ "categorical",
      white ~ "continuous",
      black ~ "continuous",
      asian ~ "continuous",
      living_independent ~ "continuous",
      living_dependent ~ "continuous",
      # housing_home ~ "continuous",
      # housing_assisted ~ "continuous",
      pre_mmse_mean_med ~ "continuous",
      cog_imp ~ "continuous",
      dm ~ "continuous",
      cardiac ~ "continuous",
      malnourish ~ "continuous"
    ),
    # missing_text = "Not reported"
  missing = "no"
  ) |>
  add_n() |>
  modify_header(stat_0 = "**Mean<u> Med </u>(Range)**") |>
  modify_footnote(update = stat_0 ~ NA) |> 
  as_gt(id = "one") |>
  fmt_markdown(stat_0) |>
  gt_theme_mg() |>
  tab_style(style = cell_text(align = "left"), locations = cells_body(columns = c(stat_0))) |>
  tab_footnote("Number of studies reporting from the 22 included.", locations = cells_column_labels(columns = c(n)), placement = "right") |> 
  tab_footnote("Mean, median, or range of the mean or median reported in trials.", locations = cells_column_labels(columns = c(stat_0)), placement = "right") 
  # tab_info()
```


